---
title: "Garch Prediction Of monthly Gold Price"
author: "Wu Wei"
date: "2017-7-4"
output: html_document
---

## 0. Preparation


```{r Appendix 0.1, echo = FALSE}
suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
suppressMessages(library(rugarch))
suppressMessages(library(tseries))
suppressMessages(library(fBasics))
suppressMessages(library(FinTS))

```

```{r appendix 0.2, echo = TRUE}
rm(list = ls())

setwd("d://MyR//stock//")

monthly.original.data <- read.csv("goldmonthly.csv")

monthly.close.price <- as.ts(monthly.original.data[,5])

monthly.compound.return <- diff(log(monthly.close.price)) * 100

```


```{r Appendix 0.3}
mean(monthly.compound.return)
sd(monthly.compound.return)
skewness(monthly.compound.return)
kurtosis(monthly.compound.return)
jarqueberaTest(monthly.compound.return)

```

## 1 Enfluence on Models of different training set 

```{r Appendix 1.1}
source("CompareGarchAicARMA00.r")
```

```{r Appendix 1.2, echo = TRUE, cache=TRUE}
training.set.420 <- head(monthly.compound.return, 420)
CompareGarchAicARMA00(training.set.420, arg.difference = 0)

```

```{r Appendix 1.3, echo = TRUE, cache=TRUE}
training.set.430 <- head(monthly.compound.return, 430)
CompareGarchAicARMA00(training.set.430, arg.difference = 0)

```


```{r Appendix 1.4, echo = TRUE, cache=TRUE, eval=TRUE}
training.set.440 <- head(monthly.compound.return, 440)
CompareGarchAicARMA00(training.set.440, arg.difference = 0)

```

```{r Appendix 1.5, echo = TRUE, cache=TRUE, eval=TRUE}
training.set.450 <- head(monthly.compound.return, 450)
CompareGarchAicARMA00(training.set.450, arg.difference = 0)

```

```{r Appendix 1.6, echo = TRUE, cache=TRUE, eval=TRUE}
training.set.460 <- head(monthly.compound.return, 460)
CompareGarchAicARMA00(training.set.460, arg.difference = 0)

```




## 2 Comparison of Weekly Models 

```{r appendix 2.1}

source("d://MyR//zhao//CompareObjectAccuracyArimaNolimitation.R")
comparison.period <- 20

forecast.period <- 4

training.set.endpoint <- length(monthly.compound.return) - comparison.period - forecast.period

maxorder <- 5


```


```{r appendix 2.2, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
result.arima <- CompareObjectAccuracyArimaNolimitation(arg.object = monthly.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```



```{r Appendix 2.2(3)}
source("CompareGarchsignbias.r")
```

```{r Appendix 2.2(31), echo = TRUE, cache=TRUE, eval=FALSE}
signbias.sGarchnorm <- CompareGarchsignbias(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "norm")
print(signbias.sGarchnorm)

```

The leverage effect of the standardized residuals is not significant. So eGARCH/apGARCH are not used for modelling.

```{r Appendix 2.2(32)}
source("CompareGarchnyblom.r")
```

```{r Appendix 2.2(321), echo = TRUE, cache=TRUE, eval=FALSE}
nyblom.sGarchnorm <- CompareGarchnyblom(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "norm")

nyblom.sGarchnorm <- round(nyblom.sGarchnorm, digits = 2)
print(nyblom.sGarchnorm)

```


```{r Appendix 2.2(331), echo = TRUE, cache=TRUE, eval=FALSE}
nyblom.sGarchstd <- CompareGarchnyblom(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "std")

nyblom.sGarchstd <- round(nyblom.sGarchstd, digits = 2)
print(nyblom.sGarchstd)

```

```{r Appendix 2.2(34), echo = TRUE, cache=TRUE, eval=FALSE}

nyblom.sGarchged <- CompareGarchnyblom(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "ged")

nyblom.sGarchged <- round(nyblom.sGarchged, digits = 2)
print(nyblom.sGarchged)

```


```{r Appendix 2.2(4)}
source("CompareGarchgof.r")

```


```{r Appendix 2.2(41), echo = TRUE, cache=TRUE, eval=FALSE}

gof.sGarchnorm <- CompareGarchgof(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "norm")
print(gof.sGarchnorm)

```

So, norm distribution assumption can be accepted.


```{r Appendix 2.2(5), echo = TRUE, cache=TRUE, eval=FALSE}
gof.sGarchsnorm <- CompareGarchgof(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "snorm")
print(gof.sGarchsnorm)

```

So, snorm distribution assumption can be accepted.

```{r Appendix 2.2(6), echo = TRUE, cache=TRUE, eval=FALSE}

gof.sGarchstd <- CompareGarchgof(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "std")
print(gof.sGarchstd)

```

So, std distribution assumption can be accepted.

```{r Appendix 2.2(7), echo = TRUE, cache=TRUE, eval=FALSE}

gof.sGarchsstd <- CompareGarchgof(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "sstd")
print(gof.sGarchsstd)

```

So, sstd distribution assumption can be accepted.

```{r Appendix 2.2(8), echo = TRUE, cache=TRUE, eval=FALSE}

gof.sGarchged <- CompareGarchgof(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "ged")
print(gof.sGarchged)

```

So, ged distribution assumption can be accepted.

```{r Appendix 2.2(9), echo = TRUE, cache=TRUE, eval=FALSE}

gof.sGarchsged <- CompareGarchgof(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "sged")
print(gof.sGarchsged)

```

So, sged distribution assumption can be accepted.

## 3 Back test of monthlyly Models 

```{r appendix 3.1}
source("CompareGarchAccuracyARMA00.R")


```


```{r appendix 3.2, echo = TRUE, cache=FALSE, eval=TRUE}


result.iGarchstd <- CompareGarchAccuracyARMA00(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "std")
```


```{r appendix 3.3, echo = TRUE, cache=FALSE, eval=TRUE}


result.iGarchged <- CompareGarchAccuracyARMA00(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "ged")
```



```{r appendix 3.4, eval=TRUE}

rmse.name <- c("iGarchged",
               "iGarchstd")

rmseBT.count <- c(sum(result.iGarchged$RMSE > result.arima$RMSE),
                sum(result.iGarchstd$RMSE > result.arima$RMSE))

rmse.meanvalue <- c(mean(result.iGarchged$RMSE),
                mean(result.iGarchstd$RMSE))

rmse.df <- data.frame(name = rmse.name, CountrmseBTarima = rmseBT.count, meanvalue = round(rmse.meanvalue,digits = 2))


print(rmse.df[order(rmse.df$CountrmseBTarima, rmse.df$meanvalue),])

round(mean(result.arima$RMSE), digits = 2)

```

#### 4 Final comparison of pure Arima model with Garch models for 50 steps

```{r appendix 4.1, echo = TRUE, cache=TRUE, eval=FALSE}

comparison.period <- 50
training.set.endpoint <- length(monthly.compound.return) - comparison.period - forecast.period

result.arima.50 <- CompareObjectZeroDiffAccuracy(arg.object = monthly.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 4.1(2), echo = TRUE, cache=TRUE, eval=FALSE}


result.iGarchged.50 <- CompareGarchAccuracy(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.50,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "ged")
```

```{r appendix 4.1(3), echo = TRUE, cache=TRUE, eval=FALSE}


result.sGarchged.50 <- CompareGarchAccuracy(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.50,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "ged")
```

```{r appendix 4.1(4), echo = TRUE, cache=TRUE, eval=FALSE}


result.iGarchsged.50 <- CompareGarchAccuracy(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.50,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "sged")
```

```{r appendix 4.1(g), echo = TRUE, cache=TRUE, eval=FALSE}


result.gjrGarchnorm.50 <- CompareGarchAccuracy(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.50,
                                                  arg.var.model = "gjrGARCH",
                                                  arg.dist.model = "norm")
```

```{r appendix 4.1(6), eval=FALSE}

rmse.name <- c("iGarchsged",
               "iGarchged",
               "sGarchged",
               "gjrGarchnorm")

rmseBT.count <- c(sum(result.iGarchsged.50$RMSE > result.arima.50$RMSE),
                  sum(result.iGarchged.50$RMSE > result.arima.50$RMSE),
                  sum(result.sGarchged.50$RMSE > result.arima.50$RMSE),
                  sum(result.gjrGarchnorm.50$RMSE > result.arima.50$RMSE))

rmse.meanvalue <- c(mean(result.iGarchsged.50$RMSE),
                    mean(result.iGarchged.50$RMSE),
                    mean(result.sGarchged.50$RMSE),
                    mean(result.gjrGarchnorm.50$RMSE))

rmse.df <- data.frame(name = rmse.name, CountrmseBTarima = rmseBT.count, meanvalue = round(rmse.meanvalue,digits = 2))


print(rmse.df[order(rmse.df$CountrmseBTarima, rmse.df$meanvalue),])

round(mean(result.arima.50$RMSE), digits = 2)

```



```{r appendix 4.2, echo = TRUE, cache=FALSE, eval=FALSE}
t.test(result.iGarchged.50$RMSE - result.arima.50$RMSE)

summary(result.iGarchged.50$RMSE)

summary(result.arima.50$RMSE)

final.result <- cbind(result.arima.50, result.iGarchged.50)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                             "RMSE.iGarchsstd", "Q.p","Q.p^2","LM.p")

print(final.result)

sum(final.result$RMSE.arima > final.result$RMSE.iGarchsstd)

sum(final.result$p.v >= 0.05)


```

```{r appendix 4.2(2), echo = TRUE, cache=FALSE, eval=FALSE}
t.test(result.sGarchged.50$RMSE - result.arima.50$RMSE)

summary(result.sGarchged.50$RMSE)

summary(result.arima.50$RMSE)

final.result <- cbind(result.arima.50, result.sGarchged.50)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                            "RMSE.sGarchsstd", "Q.p","Q.p^2","LM.p")

print(final.result)

sum(final.result$RMSE.arima > final.result$RMSE.sGarchsstd)

sum(final.result$p.v >= 0.05)


```

```{r appendix 4.2(3), echo = TRUE, cache=FALSE, eval=FALSE}
t.test(result.iGarchsged.50$RMSE - result.arima.50$RMSE)

summary(result.iGarchsged.50$RMSE)

summary(result.arima.50$RMSE)

final.result <- cbind(result.arima.50, result.iGarchsged.50)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                            "RMSE.iGarchsged", "Q.p","Q.p^2","LM.p")

print(final.result)

sum(final.result$RMSE.arima > final.result$RMSE.iGarchsged)

sum(final.result$p.v >= 0.05)


```

```{r appendix 4.2(4), echo = TRUE, cache=FALSE, eval=FALSE}
result.gjrGarchnorm.50

t.test(result.gjrGarchnorm.50$RMSE - result.arima.50$RMSE)

summary(result.gjrGarchnorm.50$RMSE)

summary(result.arima.50$RMSE)

final.result <- cbind(result.arima.50, result.gjrGarchnorm.50)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                            "RMSE.gjrGarchnorm", "Q.p","Q.p^2","LM.p")

print(final.result)

sum(final.result$RMSE.arima > final.result$RMSE.gjrGarchnorm)

sum(final.result$p.v >= 0.05)


```

There is no obvious advantage to use Garch model for predicting weekly kdj.k.


#### 5 Final comparison of pure Arima model with Garch models for 40 steps

```{r appendix 5.1, echo = TRUE, cache=TRUE, eval=FALSE}

comparison.period <- 40
training.set.endpoint <- length(monthly.compound.return) - comparison.period - forecast.period

result.arima.40 <- CompareObjectZeroDiffAccuracy(arg.object = monthly.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 5.2, echo = TRUE, cache=TRUE, eval=FALSE}


result.gjrGarchnorm.40 <- CompareGarchAccuracy(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.40,
                                                  arg.var.model = "gjrGARCH",
                                                  arg.dist.model = "norm")
```

```{r appendix 5.3, echo = TRUE, cache=TRUE, eval=FALSE}


result.iGarchged.40 <- CompareGarchAccuracy(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.40,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "ged")
```

```{r appendix 5.4, echo = TRUE, cache=TRUE, eval=FALSE}


result.sGarchged.40 <- CompareGarchAccuracy(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.40,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "ged")
```

```{r appendix 5.5, echo = TRUE, cache=TRUE, eval=FALSE}


result.iGarchsged.40 <- CompareGarchAccuracy(arg.object = monthly.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.40,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "sged")
```

```{r appendix 5.6, eval=FALSE}

rmse.name <- c("iGarchsged",
               "iGarchged",
               "sGarchged",
               "gjrGarchnorm")

rmseBT.count <- c(sum(result.iGarchsged.40$RMSE > result.arima.40$RMSE),
                  sum(result.iGarchged.40$RMSE > result.arima.40$RMSE),
                  sum(result.sGarchged.40$RMSE > result.arima.40$RMSE),
                  sum(result.gjrGarchnorm.40$RMSE > result.arima.40$RMSE))

rmse.meanvalue <- c(mean(result.iGarchsged.40$RMSE),
                    mean(result.iGarchged.40$RMSE),
                    mean(result.sGarchged.40$RMSE),
                    mean(result.gjrGarchnorm.40$RMSE))

rmse.df <- data.frame(name = rmse.name, CountrmseBTarima = rmseBT.count, meanvalue = round(rmse.meanvalue,digits = 2))


print(rmse.df[order(rmse.df$CountrmseBTarima, rmse.df$meanvalue),])

round(mean(result.arima.40$RMSE), digits = 2)

```


```{r appendix 5.7, echo = TRUE, cache=FALSE, eval=FALSE}
result.gjrGarchnorm.40

t.test(result.gjrGarchnorm.40$RMSE - result.arima.40$RMSE)

summary(result.gjrGarchnorm.40$RMSE)

summary(result.arima.40$RMSE)

final.result <- cbind(result.arima.40, result.gjrGarchnorm.40)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                            "RMSE.gjrGarchnorm", "Q.p","Q.p^2","LM.p")

print(final.result)

sum(final.result$RMSE.arima > final.result$RMSE.gjrGarchnorm)

sum(final.result$p.v >= 0.05)


```
