---
title: "ARIMA Prediction Of Gold compound return"
author: "Wu Wei"
date: "2017-7-4"
output: html_document
---



```{r library, echo = FALSE}
suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
suppressMessages(library(rugarch))
suppressMessages(library(lmtest))
suppressMessages(library(tseries))
suppressMessages(library(fBasics))
suppressMessages(library(Rdonlp2))
suppressMessages(library("FinTS"))
```


## 1.Analyse for monthly gold price


```{r appendix 1.1-1, echo = TRUE}
rm(list = ls())

setwd("d://MyR//stock//")
monthly.original.data <- read.csv("goldmonthly.csv")
# View(monthly.original.data)


monthly.close.price <- as.ts(monthly.original.data[,5])

# View(data.frame(monthly.original.data, c(0, diff(log(monthly.close.price)))))

monthly.compound.return <- diff(log(monthly.close.price)) * 100

```


```{r, fig.height=8, fig.width=10}

tsdisplay(monthly.compound.return)
```

```{r, eval=TRUE}

ndiffs(monthly.compound.return)

```

```{r}
mean(monthly.compound.return)
sd(monthly.compound.return)
skewness(monthly.compound.return)
kurtosis(monthly.compound.return)
jarqueberaTest(monthly.compound.return)

```

```{r,eval=TRUE}

(fit.arima.monthly.return <- auto.arima(monthly.compound.return, 
                                                  stepwise = FALSE, approximation = FALSE))

```

### 1.1 White Noise Test


```{r Monthly Verification--White Noise Test, cache=FALSE, eval=TRUE}


Box.test(residuals(fit.arima.monthly.return), 
         lag=10, 
         fitdf=sum(fit.arima.monthly.return$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.monthly.return), 
         lag=20, 
         fitdf=sum(fit.arima.monthly.return$arma[c(1,2)]), type = "Lj")

```

### 1.2  Relationship Between Residuals And Time

```{r main 3.2, fig.height=6, fig.width=10, cache=FALSE, eval=TRUE}

plot(residuals(fit.arima.monthly.return), axes = TRUE)
abline(h = 0, col = "red")

```

### 1.3 Relationship Between Residuals And Fitted Value

```{r main 3.3, fig.height=6, fig.width=10, eval=TRUE}

plot(as.numeric(residuals(fit.arima.monthly.return)) ~ as.numeric(fitted(fit.arima.monthly.return)))
abline(h = 0, col = "red")


```


### 1.4 Normality of Residuals

```{r Monthly Verification--Normality of Residuals, fig.height=6, fig.width=10, eval=TRUE}

qqnorm(residuals(fit.arima.monthly.return))
qqline(residuals(fit.arima.monthly.return))


```

### 1.5 ARCH Effect Test


```{r Monthly Verification 3.5, eval=TRUE}

Box.test((residuals(fit.arima.monthly.return))^2, 
         lag=10, 
         fitdf=sum(fit.arima.monthly.return$arma[c(1,2)]), type = "Lj")

Box.test((residuals(fit.arima.monthly.return))^2, 
         lag=20, 
         fitdf=sum(fit.arima.monthly.return$arma[c(1,2)]), type = "Lj")

ArchTest(residuals(fit.arima.monthly.return))



```

## 2 Comparison of pure Arima model with naive model

```{r appendix 3.6, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
source("d://MyR//stock//CompareObjectNaiveAccuracy.R")
source("d://MyR//stock//CompareObjectAccuracy.R")

comparison.period <- 20

forecast.period <- 4

training.set.endpoint <- length(monthly.compound.return) - comparison.period - forecast.period

maxorder <- 5
```

```{r appendix 3.6(1), fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}
result.naive <- CompareObjectNaiveAccuracy(arg.object = monthly.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 3.6(2), fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}
result.pure <- CompareObjectAccuracy(arg.object = monthly.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 3.6(3), fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.pure$RMSE - result.naive$RMSE)

final.result <- cbind(result.pure,
                      result.naive)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "dr","RMSE", "p.v",
                            "p2","d2","q2", "dr2","RMSE2", "p.v2")

print(final.result)

sum(final.result$RMSE > final.result$RMSE2)

sum(final.result$p.v > 0.05)

sum(final.result$p.v2 > 0.05)

```


## 3 Comparison of pure Arima models

```{r appendix 3.7, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
source("d://MyR//zhao//CompareObjectAccuracyArimaNolimitation.R")


```


```{r appendix 3.7(2), fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}
result.pure.no.limitation <- CompareObjectAccuracyArimaNolimitation(arg.object = monthly.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 3.7(3), fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.pure$RMSE - result.pure.no.limitation$RMSE)

final.result <- cbind(result.pure,
                      result.pure.no.limitation)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "dr","RMSE", "p.v",
                            "p2","d2","q2", "dr2","RMSE2", "p.v2")

print(final.result)

sum(final.result$RMSE > final.result$RMSE2)

sum(final.result$p.v > 0.05)

sum(final.result$p.v2 > 0.05)

```

### 3.1 White Noise Test


```{r , cache=FALSE, eval=TRUE}
(fit.arima.monthly.return.no.limitation <- auto.arima(monthly.compound.return))


Box.test(residuals(fit.arima.monthly.return.no.limitation), 
         lag=10, 
         fitdf=sum(fit.arima.monthly.return.no.limitation$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.monthly.return.no.limitation), 
         lag=20, 
         fitdf=sum(fit.arima.monthly.return.no.limitation$arma[c(1,2)]), type = "Lj")

```

### 3.2  Relationship Between Residuals And Time

```{r , fig.height=6, fig.width=10, cache=FALSE, eval=TRUE}

plot(residuals(fit.arima.monthly.return.no.limitation), axes = TRUE)
abline(h = 0, col = "red")

```

### 3.3 Relationship Between Residuals And Fitted Value

```{r , fig.height=6, fig.width=10, eval=TRUE}

# plot(as.numeric(residuals(fit.arima.monthly.return.no.limitation)) ~ as.numeric(fitted(fit.arima.monthly.return.no.limitation)))
# abline(h = 0, col = "red")


plot(as.numeric(residuals(fit.arima.monthly.return.no.limitation)) )

```


### 3.4 Normality of Residuals

```{r , fig.height=6, fig.width=10, eval=TRUE}

qqnorm(residuals(fit.arima.monthly.return.no.limitation))
qqline(residuals(fit.arima.monthly.return.no.limitation))


```

### 3.5 ARCH Effect Test


```{r , eval=TRUE}

Box.test((residuals(fit.arima.monthly.return.no.limitation))^2, 
         lag=10, 
         fitdf=sum(fit.arima.monthly.return.no.limitation$arma[c(1,2)]), type = "Lj")

Box.test((residuals(fit.arima.monthly.return.no.limitation))^2, 
         lag=20, 
         fitdf=sum(fit.arima.monthly.return.no.limitation$arma[c(1,2)]), type = "Lj")

ArchTest(residuals(fit.arima.monthly.return.no.limitation))



```



## 4 Forecast using Arima model
```{r, eval=TRUE}
forecast(fit.arima.monthly.return.no.limitation, h = 1, 
                              level = c(80,95))
```

```{r, eval=TRUE}
tail(monthly.compound.return)
```




