---
title: "ARIMA Prediction Of Stock 600550"
author: "Wu Wei"
date: "2015-12-13"
output: html_document
---

## Synopsis

 Index data of stock 600550 was analyzed using Arima model  

* Arima model for data begining from 2015-12 is better, which can be used as a prediction tool right now


## Library input & Data Input
```{r}
suppressMessages(library(forecast))

setwd("d://MyR//stock//")
original.data <- read.csv("600550.csv")
# (original.data)
close.price <- as.ts(original.data[,5])

training.set.start260 <- window(close.price, start = 260, end = 277)
test.set <- window(close.price, start = 278)

training.set.start235 <- window(close.price, start = 235, end = 277)
```

## Analysis for data between 2016-6 and 2016-9

### Exploratory Data Analysis for data between 2016-6 and 2016-9
```{r}
# dev.off()
par(mfrow = c(1,1))

# plot(training.set.start260)
plot(training.set.start260, axes = FALSE, main = "stock index of 600550")
axis(1, 
     at = seq(tsp(training.set.start260)[1], tsp(training.set.start260)[2], 3), 
     labels = original.data[seq(tsp(training.set.start260)[1], 
                                tsp(training.set.start260)[2], 3), 1])
axis(2)
box()

abline(v = seq(tsp(training.set.start260)[1], tsp(training.set.start260)[2], 3), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(min(training.set.start260) - 0.2, 
               max(training.set.start260) + 0.2, 0.2), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))


```

It seems that there is no season pattern, but trend exists.

### Modelling for data between 2016-6 and 2016-9

```{r, fig.height=9, fig.width=10}

tsdisplay(training.set.start260)
```

```{r, fig.height=7, fig.width=10}

par(mfrow = c(2,1))
plot(training.set.start260)
plot(diff(training.set.start260))
abline(h = 0, col = "red")
```

```{r, fig.height=7, fig.width=10}

tsdisplay(diff(training.set.start260))
```

```{r}

##nsdiffs(training.set.start260)
ndiffs(training.set.start260)

```

```{r, fig.height=7, fig.width=10}

(fit.010.start260 <- Arima(training.set.start260, order = c(0,1,0)))

tsdisplay(residuals(fit.010.start260))
```

```{r}

Box.test(residuals(fit.010.start260), lag=3, fitdf=0)
Box.test(residuals(fit.010.start260), lag=3, fitdf=0, type = "Lj")

```



```{r}
name.aicc <- c("Arima(training.set.start260, order = c(0,1,0))$aicc",
               "Arima(training.set.start260, order = c(0,1,1))$aicc",
               "Arima(training.set.start260, order = c(0,1,2))$aicc",
               "Arima(training.set.start260, order = c(1,1,0))$aicc",
               "Arima(training.set.start260, order = c(1,1,1))$aicc",
               "Arima(training.set.start260, order = c(1,1,2))$aicc",
               "Arima(training.set.start260, order = c(2,1,0))$aicc",
               "Arima(training.set.start260, order = c(2,1,1))$aicc",
               "Arima(training.set.start260, order = c(2,1,2))$aicc",
               
               "Arima(training.set.start260, order = c(0,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.start260, order = c(0,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.start260, order = c(0,1,2), include.drift = TRUE)$aicc",
               "Arima(training.set.start260, order = c(1,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.start260, order = c(1,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.start260, order = c(1,1,2), include.drift = TRUE)$aicc",
               "Arima(training.set.start260, order = c(2,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.start260, order = c(2,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.start260, order = c(2,1,2), include.drift = TRUE)$aicc"
               
)

aicc <- unlist(lapply(lapply(name.aicc, parse, file = "", n = NULL), eval))

name <-  substr(name.aicc, 1, nchar(name.aicc) - 5)

df <- data.frame(name = sub("training.set","",name), 
                 aicc = round(aicc, digits = 3))

(df[order(df$aicc),])

```

Arima(0,1,0) is preferred.


```{r}

auto.arima(training.set.start260, stepwise = FALSE, approximation = FALSE)
```

Arima(0,1,0) is also selected by auto method.

#### Relationship Between Residuals And Time(for data between 2016-6 and 2016-9)

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.010.start260), axes = FALSE, main = "Arima(0,1,0)")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(training.set.start260)[1], tsp(training.set.start260)[2], 3), 
     labels = original.data[seq(tsp(training.set.start260)[1], 
                                tsp(training.set.start260)[2], 3), 1])
axis(2)
box()
```

#### Relationship Between Residuals And Fitted Value(for data between 2016-6 and 2016-9)

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.010.start260)) ~ as.numeric(fitted(fit.010.start260)), 
     main = "Arima(0,1,0)")
abline(h = 0, col = "red")



```

There is no obvious heteroscedasticity.


#### Normality of  Residuals(for data between 2016-6 and 2016-9)

```{r}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.010.start260), main = "Arima(0,1,0)")
qqline(residuals(fit.010.start260))

```

Residuals conform to normality.

#### Comparison between actual value and forecast result (for data between 2016-6 and 2016-9)

```{r}
# dev.off()

par(mfrow = c(1,1))


fc.arima.start260 <- forecast(fit.010.start260, h = length(test.set), level = 60)

ylim.upper <- max(c(fc.arima.start260$upper, 
                    fc.arima.start260$x)) + 0.2

ylim.lower <- min(c(fc.arima.start260$lower, 
                    fc.arima.start260$x)) - 0.2


plot(fc.arima.start260, ylim = c(ylim.lower, ylim.upper),
     type = "o", plot.conf = TRUE, shaded = FALSE, pi.col = "purple",
     axes = FALSE, main = "Arima(0,1,0)")
lines(test.set, type = "o",col = "red")

axis(1, at = seq(tsp(training.set.start260)[1], tsp(close.price)[2], 3), 
     labels = original.data[seq(tsp(training.set.start260)[1], tsp(close.price)[2], 3), 1])
axis(2)
box()

abline(v = seq(tsp(training.set.start260)[1], tsp(close.price)[2], 3), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower, ylim.upper, 0.2), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


```

Comparing with actual value of test set, forecast result of Arima(0,1,0) model is reasonable.



## Analysis for data between 2015-12 and 2016-9

### Exploratory Data Analysis for data between 2015-12 and 2016-9
```{r}
# dev.off()
par(mfrow = c(1,1))


# plot(training.set.start260)
plot(training.set.start235, axes = FALSE, main = "stock index of 600550")
axis(1, at = seq(tsp(training.set.start235)[1], tsp(training.set.start235)[2], 5), 
     labels = original.data[seq(tsp(training.set.start235)[1], tsp(training.set.start235)[2], 5), 1])
axis(2)
box()

abline(v = seq(tsp(training.set.start235)[1], tsp(training.set.start235)[2], 5), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(min(training.set.start235) - 0.1, 
               max(training.set.start235) + 0.1, 0.3), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))


```


### Modelling for data between 2015-12 and 2016-9

```{r, fig.height=7, fig.width=10}
tsdisplay(training.set.start235)
```

```{r, fig.height=7, fig.width=10}
par(mfrow = c(2,1))
plot(training.set.start235)
plot(diff(training.set.start235))
abline(h = 0, col = "red")
```

```{r, fig.height=7, fig.width=10}
tsdisplay(diff(training.set.start235))
```

```{r}
##nsdiffs(training.set.start235)
ndiffs(training.set.start235)

```



```{r, fig.height=7, fig.width=10}

(fit.010.start235 <- Arima(training.set.start235, order = c(0,1,0)))

tsdisplay(residuals(fit.010.start235))
```



```{r, fig.height=7, fig.width=10}

Box.test(residuals(fit.010.start235), lag=8, fitdf=0)
Box.test(residuals(fit.010.start235), lag=8, fitdf=0, type = "Lj")

```



```{r}
name.aicc <- c("Arima(training.set.start235, order = c(0,1,0))$aicc",
               "Arima(training.set.start235, order = c(0,1,1))$aicc",
               "Arima(training.set.start235, order = c(0,1,2))$aicc",
               
               "Arima(training.set.start235, order = c(1,1,0))$aicc",
               "Arima(training.set.start235, order = c(1,1,1))$aicc",
               "Arima(training.set.start235, order = c(1,1,2))$aicc",
               
               "Arima(training.set.start235, order = c(2,1,0))$aicc",
               "Arima(training.set.start235, order = c(2,1,1))$aicc",
               "Arima(training.set.start235, order = c(2,1,2))$aicc",
               
               "Arima(training.set.start235, order = c(0,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.start235, order = c(0,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.start235, order = c(0,1,2), include.drift = TRUE)$aicc",
               
               "Arima(training.set.start235, order = c(1,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.start235, order = c(1,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.start235, order = c(1,1,2), include.drift = TRUE)$aicc",
               
               "Arima(training.set.start235, order = c(2,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.start235, order = c(2,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.start235, order = c(2,1,2), include.drift = TRUE)$aicc"
               
)

aicc <- unlist(lapply(lapply(name.aicc, parse, file = "", n = NULL), eval))

name <-  substr(name.aicc, 1, nchar(name.aicc) - 5)

df <- data.frame(name = sub("training.set","",name), 
                 aicc = round(aicc, digits = 3))

(df[order(df$aicc),])

```

Arima(0,1,1) is preferred.


```{r}

auto.arima(training.set.start235,  stepwise = FALSE, approximation = FALSE)

```

Arima(0,1,1) is also selected by auto method.

```{r, fig.height=7, fig.width=10}

(fit.011.start235 <- Arima(training.set.start235, order = c(0,1,1)))

tsdisplay(residuals(fit.011.start235))
```


```{r, fig.height=7, fig.width=10}

Box.test(residuals(fit.011.start235), lag=8, fitdf=1)
Box.test(residuals(fit.011.start235), lag=8, fitdf=1, type = "Lj")

```


#### Relationship Between Residuals And Time(for data between 2015-12 and 2016-9)

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.011.start235), axes = FALSE, main = "Arima(0,1,1)")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(training.set.start235)[1], tsp(training.set.start235)[2], 5), 
     labels = original.data[seq(tsp(training.set.start235)[1], 
                                tsp(training.set.start235)[2], 5), 1])
axis(2)
box()
```

#### Relationship Between Residuals And Fitted Value(for data between 2015-12 and 2016-9)

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.011.start235)) ~ as.numeric(fitted(fit.011.start235)), 
     main = "Arima(0,1,1)")
abline(h = 0, col = "red")



```

There is no obvious heteroscedasticity.


#### Normality of  Residuals(for data between 2015-12 and 2016-9)

```{r}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.011.start235), main = "Arima(0,1,1)")
qqline(residuals(fit.011.start235))

```


#### Comparison between actual value and forecast result (for data between 2015-12 and 2016-9)

```{r}
# dev.off()

par(mfrow = c(1,1))


fc.arima.start235 <- forecast(fit.011.start235, h = length(test.set), level = 60)

ylim.upper <- max(c(fc.arima.start235$upper, 
                    fc.arima.start235$x)) + 0.1

ylim.lower <- min(c(fc.arima.start235$lower, 
                    fc.arima.start235$x)) - 0.1

plot(fc.arima.start235, ylim = c(ylim.lower, ylim.upper),
     type = "o", plot.conf = TRUE, shaded = FALSE, pi.col = "purple",
     axes = FALSE, main = "Arima(0,1,1)")
lines(test.set, type = "o",col = "red")

axis(1, at = seq(tsp(training.set.start235)[1], tsp(close.price)[2], 5), 
     labels = original.data[seq(tsp(training.set.start235)[1], tsp(close.price)[2], 5), 1])
axis(2)
box()

abline(v = seq(tsp(training.set.start235)[1], tsp(close.price)[2], 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower, ylim.upper, 0.3), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


```

Comparing with actual value of test set, forecast result of Arima(0,1,1) model is reasonable for a long time.


## Comparison between Arima(0,1,0) model (for data between 2016-6 and 2016-9) and Arima(0,1,1) model (for data between 2015-12 and 2016-9) and SES model (for data between 2015-12 and 2016-9)

### Accuracy Of Training Set

```{r}
# fit.holt.start260 <- holt(training.set.start260, 
#                           h = length(test.set),  
#                           level = 60)

fit.ses.ets.start235 <- ets(training.set.start235, model = "ANN", lambda = -1)

df.training.set.comparison <- rbind(accuracy(fit.010.start260),
            accuracy(fit.011.start235),
            accuracy(fit.ses.ets.start235))

row.names(df.training.set.comparison) <- c("Arima(0,1,0) 2016-6", 
                                           "Arima(0,1,1) 2015-12",
                                           "SES model 2015-12")
print(round(df.training.set.comparison, 3))


```

SES model for data begining from 2015-12 is the best.

### White noise test

```{r}

Box.test(residuals(fit.010.start260), lag=3, fitdf=0)
Box.test(residuals(fit.010.start260), lag=3, fitdf=0, type = "Lj")

Box.test(residuals(fit.011.start235), lag=8, fitdf=1)
Box.test(residuals(fit.011.start235), lag=8, fitdf=1, type = "Lj")

Box.test(residuals(fit.ses.ets.start235), lag=8, fitdf=1)
Box.test(residuals(fit.ses.ets.start235), lag=8, fitdf=1, type = "Lj")
```


### Relationship Between Residuals And Fitted Value

```{r, fig.height=7, fig.width=14}
# dev.off()
par(mfrow = c(1,3))

plot(as.numeric(residuals(fit.010.start260)) ~ as.numeric(fitted(fit.010.start260)), 
     main = "Arima(0,1,0) model for data between 2016-6 and 2016-9")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.011.start235)) ~ as.numeric(fitted(fit.011.start235)), 
     main = "Arima(0,1,1) model for data between 2015-12 and 2016-9")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.ses.ets.start235)) ~ as.numeric(fitted(fit.ses.ets.start235)), 
     main = "SES model for data between 2015-12 and 2016-9")
abline(h = 0, col = "red")

```


### Normality of  Residuals

```{r, fig.height=7, fig.width=14}
# dev.off()
par(mfrow = c(1,3))

qqnorm(residuals(fit.010.start260), main = "Arima(0,1,0) model for data between 2016-6 and 2016-9")
qqline(residuals(fit.010.start260))

qqnorm(residuals(fit.011.start235), main = "Arima(0,1,1) model for data between 2015-12 and 2016-9")
qqline(residuals(fit.011.start235))

qqnorm(residuals(fit.ses.ets.start235), main = "SES model for data between 2015-12 and 2016-9")
qqline(residuals(fit.ses.ets.start235))

```



### Accuracy Of Test Set

```{r}
df.test.set.comparison <- rbind(
        accuracy(forecast(fit.010.start260, h = length(test.set)), test.set)[2,],
        accuracy(forecast(fit.011.start235, h = length(test.set)), test.set)[2,],
        accuracy(forecast(fit.ses.ets.start235, h = length(test.set)), test.set)[2,])

row.names(df.test.set.comparison) <- c("Arima(0,1,0) 2016-6", 
                                       "Arima(0,1,1) 2015-12",
                                       "SES model 2015-12")
print(round(df.test.set.comparison, 3))


```


#### Comparison between actual value and forecast result (for data between 2015-12 and 2016-9)

```{r, fig.height=7, fig.width=14}
# dev.off()

fc.ses.ets.start235 <- forecast(fit.ses.ets.start235, h = length(test.set), level = 60)

ylim.upper.comparison <- max(c(fc.arima.start235$upper, 
                    fc.arima.start235$x,
                    fc.arima.start260$upper,
                    fc.ses.ets.start235$upper)) + 0.1

ylim.lower.comparison <- min(c(fc.arima.start235$lower, 
                    fc.arima.start235$x,
                    fc.arima.start260$lower,
                    fc.ses.ets.start235$lower)) - 0.1


par(mfrow = c(1,3))


plot(fc.arima.start260, 
     ylim = c(ylim.lower.comparison, ylim.upper.comparison),
     type = "o", plot.conf = TRUE, shaded = FALSE, pi.col = "purple",
     axes = FALSE, main = "Arima(0,1,0) model for data between 2016-6 and 2016-9")
lines(test.set, col = "red")

axis(1, at = seq(tsp(training.set.start260)[1], length(close.price), 5), 
     labels = FALSE)

text(seq(tsp(training.set.start260)[1], length(close.price), 5), 
     par("usr")[3] - 0.1, 
     labels = original.data[seq(tsp(training.set.start260)[1], length(close.price), 5), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2)
box()

abline(v = seq(tsp(training.set.start260)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower.comparison, ylim.upper.comparison, 0.5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))



###"Arima(0,1,1) model for data between 2015-12 and 2016-9"
plot(fc.arima.start235, 
     ylim = c(ylim.lower.comparison, ylim.upper.comparison),
     type = "o", plot.conf = TRUE, shaded = FALSE, pi.col = "purple",
     axes = FALSE, main = "Arima(0,1,1) model for data between 2015-12 and 2016-9")
lines(test.set, col = "red")
axis(1, at = seq(tsp(training.set.start235)[1], length(close.price), 5), 
     labels = FALSE)

text(seq(tsp(training.set.start235)[1], length(close.price), 5), 
     par("usr")[3] - 0.1, 
     labels = original.data[seq(tsp(training.set.start235)[1], length(close.price), 5), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)


axis(2)
box()

abline(v = seq(tsp(training.set.start235)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower.comparison, ylim.upper.comparison, 0.5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

###"Holt model for data between 2016-6 and 2016-9"

plot(fc.ses.ets.start235, 
     ylim = c(ylim.lower.comparison, ylim.upper.comparison),
     type = "o", plot.conf = TRUE, shaded = FALSE, pi.col = "purple",
     axes = FALSE, main = "SES model for data between 2015-12 and 2016-9")
lines(test.set, col = "red")

axis(1, at = seq(tsp(training.set.start235)[1], length(close.price), 5), 
     labels = FALSE)

text(seq(tsp(training.set.start235)[1], length(close.price), 5), 
     par("usr")[3] - 0.1, 
     labels = original.data[seq(tsp(training.set.start235)[1], length(close.price), 5), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2)
box()

abline(v = seq(tsp(training.set.start235)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower.comparison, ylim.upper.comparison, 0.5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


```

SES model for data begining from 2015-12 is better .

## Conclusion

* Arima(0,1,0) model for data begining from 2016-6 is better in Arima family, which can be used as a prediction tool


## Review of the prediction of the last 5 weeks 
```{r, fig.height=7, fig.width=14}

review.length <- 5

refined.training.set.last5weeks <- 
        window(close.price, start = 260, end = length(close.price) - review.length)

refined.test.set.last5weeks <- 
        window(close.price, start = length(close.price) - review.length + 1)

```

```{r, fig.height=7, fig.width=10}
tsdisplay(refined.training.set.last5weeks)
```

```{r, fig.height=7, fig.width=10}

par(mfrow = c(2,1))
plot(refined.training.set.last5weeks)
plot(diff(refined.training.set.last5weeks))
abline(h = 0, col = "red")
```

```{r, fig.height=7, fig.width=10}

tsdisplay(diff(refined.training.set.last5weeks))
```

```{r}

##nsdiffs(refined.training.set.last5weeks)
ndiffs(refined.training.set.last5weeks)

```

```{r, fig.height=7, fig.width=10}

(fit.010.last5weeks <- Arima(refined.training.set.last5weeks, order = c(0,1,0)))

tsdisplay(residuals(fit.010.last5weeks))

```

```{r}

Box.test(residuals(fit.010.last5weeks), lag=4, fitdf=0)
Box.test(residuals(fit.010.last5weeks), lag=4, fitdf=0, type = "Lj")

```

```{r}
name.aicc <- c("Arima(refined.training.set.last5weeks, order = c(0,1,0))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(0,1,1))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(0,1,2))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(0,1,3))$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(1,1,0))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(1,1,1))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(1,1,2))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(1,1,3))$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(2,1,0))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(2,1,1))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(2,1,2))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(2,1,3))$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(3,1,0))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(3,1,1))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(3,1,2))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(3,1,3))$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(0,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(0,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(0,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(0,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(1,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(1,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(1,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(1,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(2,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(2,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(2,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(2,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(3,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(3,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(3,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(3,1,3), include.drift = TRUE)$aicc"
)

aicc <- unlist(lapply(lapply(name.aicc, parse, file = "", n = NULL), eval))

name <-  substr(name.aicc, 1, nchar(name.aicc) - 5)

df <- data.frame(name = sub("refined.training.set","",name), 
                 aicc = round(aicc, digits = 3))

(df[order(df$aicc),])

```

```{r}

(fit.211.drift.last5weeks <- Arima(refined.training.set.last5weeks, order = c(2,1,1), include.drift = TRUE))
                       
Box.test(residuals(fit.211.drift.last5weeks), lag=4, fitdf=3)
Box.test(residuals(fit.211.drift.last5weeks), lag=4, fitdf=3, type = "Lj")
```

The absolute value of ma1 is equal to 1, which does not fulfil the invertibility constraints.

```{r}

(fit.012.drift.last5weeks <- Arima(refined.training.set.last5weeks, order = c(0,1,2), include.drift = TRUE))
                       
Box.test(residuals(fit.012.drift.last5weeks), lag=4, fitdf=2)
Box.test(residuals(fit.012.drift.last5weeks), lag=4, fitdf=2, type = "Lj")
```

The sum of ma1 and ma2 is less than -1, which does not fulfil the invertibility constraints.

```{r}

auto.arima(refined.training.set.last5weeks, stepwise = FALSE, approximation = FALSE)
                       
```


#### Relationship Between Residuals And Time

```{r, fig.height=7, fig.width=14}
# dev.off()
par(mfrow = c(1,3))

plot(residuals(fit.211.drift.last5weeks), axes = FALSE, main = "Arima(2,1,1)")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(refined.training.set.last5weeks)[1], tsp(refined.training.set.last5weeks)[2], 5), 
     labels = original.data[seq(tsp(refined.training.set.last5weeks)[1], 
                                tsp(refined.training.set.last5weeks)[2], 5), 1])
axis(2)
box()

plot(residuals(fit.012.drift.last5weeks), axes = FALSE, main = "Arima(0,1,2)")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(refined.training.set.last5weeks)[1], tsp(refined.training.set.last5weeks)[2], 5), 
     labels = original.data[seq(tsp(refined.training.set.last5weeks)[1], 
                                tsp(refined.training.set.last5weeks)[2], 5), 1])
axis(2)
box()


plot(residuals(fit.010.last5weeks), axes = FALSE, main = "Arima(0,1,0)")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(refined.training.set.last5weeks)[1], tsp(refined.training.set.last5weeks)[2], 5), 
     labels = original.data[seq(tsp(refined.training.set.last5weeks)[1], 
                                tsp(refined.training.set.last5weeks)[2], 5), 1])
axis(2)
box()
```

#### Relationship Between Residuals And Fitted Value

```{r, fig.height=7, fig.width=14}
# dev.off()
par(mfrow = c(1,3))

plot(as.numeric(residuals(fit.211.drift.last5weeks)) ~ as.numeric(fitted(fit.211.drift.last5weeks)), 
     main = "Arima(2,1,1)")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.012.drift.last5weeks)) ~ as.numeric(fitted(fit.012.drift.last5weeks)), 
     main = "Arima(0,1,2)")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.010.last5weeks)) ~ as.numeric(fitted(fit.010.last5weeks)), 
     main = "Arima(0,1,0)")
abline(h = 0, col = "red")



```

There is no obvious heteroscedasticity.


#### Normality of  Residuals

```{r, fig.height=7, fig.width=14}
# dev.off()
par(mfrow = c(1,3))

qqnorm(residuals(fit.211.drift.last5weeks), main = "Arima(2,1,1)")
qqline(residuals(fit.211.drift.last5weeks))

qqnorm(residuals(fit.012.drift.last5weeks), main = "Arima(0,1,2)")
qqline(residuals(fit.012.drift.last5weeks))

qqnorm(residuals(fit.010.last5weeks), main = "Arima(0,1,0)")
qqline(residuals(fit.010.last5weeks))

```


```{r, fig.height=7, fig.width=14}
par(mfrow = c(1,3))

refined.fc.arima211.last5weeks <- forecast(fit.211.drift.last5weeks, #h = 70, 
                          h = review.length,  
                          level = c(80,95))

refined.fc.arima012.last5weeks <- forecast(fit.012.drift.last5weeks, #h = 70, 
                          h = review.length,  
                          level = c(80,95))

refined.fc.arima010.last5weeks <- forecast(fit.010.last5weeks, #h = 70, 
                          h = review.length,  
                          level = c(80,95))

ylim.upper.last5weeks <- max(c(refined.fc.arima211.last5weeks$upper,
                               refined.fc.arima012.last5weeks$upper,
        refined.fc.arima010.last5weeks$upper, 
                    refined.fc.arima010.last5weeks$x)) + 0.1


ylim.lower.last5weeks <- min(c(refined.fc.arima211.last5weeks$lower,
                               refined.fc.arima012.last5weeks$lower,
        refined.fc.arima010.last5weeks$lower, 
                    refined.fc.arima010.last5weeks$x)) - 0.1

plot(refined.fc.arima211.last5weeks, 
     ylim = c(ylim.lower.last5weeks, ylim.upper.last5weeks),
     type = "o", plot.conf = TRUE, shaded = TRUE, 
     fcol = "red", pi.col = "red",
     axes = FALSE, main = "Forecast for the last 5 weeks using Arima(2,1,1) model")

lines(fitted(refined.fc.arima211.last5weeks), col = "red")

lines(window(close.price, start = tsp(refined.training.set.last5weeks)[1]), 
      type = "o")

axis(1, at = seq(tsp(refined.training.set.last5weeks)[1], length(close.price), 5), 
     labels = original.data[seq(tsp(refined.training.set.last5weeks)[1], length(close.price), 5), 1])
axis(2)
box()

abline(v = seq(tsp(refined.fc.arima211.last5weeks$x)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower.last5weeks, ylim.upper.last5weeks, 0.3), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

plot(refined.fc.arima012.last5weeks, 
     ylim = c(ylim.lower.last5weeks, ylim.upper.last5weeks),
     type = "o", plot.conf = TRUE, shaded = TRUE, 
     fcol = "red", pi.col = "red",
     axes = FALSE, main = "Forecast for the last 5 weeks using Arima(0,1,2) model")

lines(fitted(refined.fc.arima012.last5weeks), col = "red")

lines(window(close.price, start = tsp(refined.training.set.last5weeks)[1]), 
      type = "o")

axis(1, at = seq(tsp(refined.training.set.last5weeks)[1], length(close.price), 5), 
     labels = original.data[seq(tsp(refined.training.set.last5weeks)[1], length(close.price), 5), 1])
axis(2)
box()

abline(v = seq(tsp(refined.fc.arima012.last5weeks$x)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower.last5weeks, ylim.upper.last5weeks, 0.3), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


plot(refined.fc.arima010.last5weeks, 
     ylim = c(ylim.lower.last5weeks, ylim.upper.last5weeks),
     type = "o", plot.conf = TRUE, shaded = TRUE, 
     fcol = "red", pi.col = "red",
     axes = FALSE, main = "Forecast for the last 5 weeks using Arima(0,1,0) model")

lines(fitted(refined.fc.arima010.last5weeks), col = "red")

lines(window(close.price, start = tsp(refined.training.set.last5weeks)[1]), 
      type = "o")

axis(1, at = seq(tsp(refined.training.set.last5weeks)[1], length(close.price), 5), 
     labels = original.data[seq(tsp(refined.training.set.last5weeks)[1], length(close.price), 5), 1])
axis(2)
box()

abline(v = seq(tsp(refined.fc.arima010.last5weeks$x)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower.last5weeks, ylim.upper.last5weeks, 0.3), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


summary(refined.fc.arima010.last5weeks)

```



## Review of the prediction of the last week
```{r, fig.height=7, fig.width=14}

refined.dataset.last.week <- window(close.price, start = 260, end = length(close.price) - 1)

```

```{r, fig.height=7, fig.width=10}

tsdisplay(refined.dataset.last.week)
```

```{r, fig.height=7, fig.width=10}

par(mfrow = c(2,1))
plot(refined.dataset.last.week)
plot(diff(refined.dataset.last.week))
abline(h = 0, col = "red")
```

```{r, fig.height=7, fig.width=10}

tsdisplay(diff(refined.dataset.last.week))
```

```{r}

##nsdiffs(refined.dataset.last.week)
ndiffs(refined.dataset.last.week)

```



```{r, fig.height=7, fig.width=10}

(fit.010.start260.last.week <- Arima(refined.dataset.last.week, order = c(0,1,0)))

tsdisplay(residuals(fit.010.start260.last.week))
```

```{r}

Box.test(residuals(fit.010.start260.last.week), lag=4, fitdf=0)
Box.test(residuals(fit.010.start260.last.week), lag=4, fitdf=0, type = "Lj")

```



```{r}
name.aicc <- c("Arima(refined.dataset.last.week, order = c(0,1,0))$aicc",
               "Arima(refined.dataset.last.week, order = c(0,1,1))$aicc",
               "Arima(refined.dataset.last.week, order = c(0,1,2))$aicc",
               "Arima(refined.dataset.last.week, order = c(0,1,3))$aicc",
               
               "Arima(refined.dataset.last.week, order = c(1,1,0))$aicc",
               "Arima(refined.dataset.last.week, order = c(1,1,1))$aicc",
               "Arima(refined.dataset.last.week, order = c(1,1,2))$aicc",
               "Arima(refined.dataset.last.week, order = c(1,1,3))$aicc",
               
               "Arima(refined.dataset.last.week, order = c(2,1,0))$aicc",
               "Arima(refined.dataset.last.week, order = c(2,1,1))$aicc",
               "Arima(refined.dataset.last.week, order = c(2,1,2))$aicc",
               "Arima(refined.dataset.last.week, order = c(2,1,3))$aicc",
               
               "Arima(refined.dataset.last.week, order = c(3,1,0))$aicc",
               "Arima(refined.dataset.last.week, order = c(3,1,1))$aicc",
               "Arima(refined.dataset.last.week, order = c(3,1,2))$aicc",
               "Arima(refined.dataset.last.week, order = c(3,1,3))$aicc",
               
               "Arima(refined.dataset.last.week, order = c(0,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(0,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(0,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(0,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.dataset.last.week, order = c(1,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(1,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(1,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(1,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.dataset.last.week, order = c(2,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(2,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(2,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(2,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.dataset.last.week, order = c(3,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(3,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(3,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(3,1,3), include.drift = TRUE)$aicc"
               
)

aicc <- unlist(lapply(lapply(name.aicc, parse, file = "", n = NULL), eval))

name <-  substr(name.aicc, 1, nchar(name.aicc) - 5)

df <- data.frame(name = sub("refined.dataset","",name), 
                 aicc = round(aicc, digits = 3))

(df[order(df$aicc),])

```



```{r}

auto.arima(refined.dataset.last.week, stepwise = FALSE, approximation = FALSE)
```

Arima(0,1,0) is selected by auto method.

```{r, fig.height=7, fig.width=10}

# (fit.211.start260.last.week <- 
#          Arima(refined.dataset.last.week, order = c(2,1,1), include.drift = TRUE))
# 
# tsdisplay(residuals(fit.211.start260.last.week))

```



```{r}

# Box.test(residuals(fit.211.start260.last.week), lag=4, fitdf=3)
# Box.test(residuals(fit.211.start260.last.week), lag=4, fitdf=3, type = "Lj")

```



#### Relationship Between Residuals And Time

```{r, fig.height=7, fig.width=10}
# dev.off()
# par(mfrow = c(1,2))

# plot(residuals(fit.211.start260.last.week), axes = FALSE, main = "Arima(2,1,1)")
# abline(h = 0, col = "red")
# axis(1, 
#      at = seq(tsp(refined.dataset.last.week)[1], tsp(refined.dataset.last.week)[2], 5), 
#      labels = original.data[seq(tsp(refined.dataset.last.week)[1], 
#                                 tsp(refined.dataset.last.week)[2], 5), 1])
# axis(2)
# box()

plot(residuals(fit.010.start260.last.week), axes = FALSE, main = "Arima(0,1,0)")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(refined.dataset.last.week)[1], tsp(refined.dataset.last.week)[2], 5), 
     labels = original.data[seq(tsp(refined.dataset.last.week)[1], 
                                tsp(refined.dataset.last.week)[2], 5), 1])
axis(2)
box()
```

#### Relationship Between Residuals And Fitted Value

```{r, fig.height=7, fig.width=10}
# dev.off()
# par(mfrow = c(1,2))
# 
# plot(as.numeric(residuals(fit.211.start260.last.week)) ~ as.numeric(fitted(fit.211.start260.last.week)), 
#      main = "Arima(2,1,1)")
# abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.010.start260.last.week)) ~ as.numeric(fitted(fit.010.start260.last.week)), 
     main = "Arima(0,1,0)")
abline(h = 0, col = "red")


```

There is no obvious heteroscedasticity.


#### Normality of  Residuals

```{r, fig.height=7, fig.width=10}
# dev.off()
# par(mfrow = c(1,2))
# 
# qqnorm(residuals(fit.211.start260.last.week), main = "Arima(2,1,1)")
# qqline(residuals(fit.211.start260.last.week))

qqnorm(residuals(fit.010.start260.last.week), main = "Arima(0,1,0)")
qqline(residuals(fit.010.start260.last.week))

```


```{r, fig.height=7, fig.width=14}
# refined.fc.arima.211.last.week <- forecast(fit.211.start260.last.week, 
#                           h = 1,  
#                           level = 80)

refined.fc.arima.010.last.week <- forecast(fit.010.start260.last.week, 
                          h = 1,  
                          level = 80)

ylim.upper <- max(c(#refined.fc.arima.211.last.week$upper, 
        #refined.fc.arima.211.last.week$x,
        refined.fc.arima.010.last.week$x,
        refined.fc.arima.010.last.week$upper)) + 0.1


ylim.lower <- min(c(#refined.fc.arima.211.last.week$lower, 
        #refined.fc.arima.211.last.week$x,
        refined.fc.arima.010.last.week$x,
        refined.fc.arima.010.last.week$lower)) - 0.1

# par(mfrow = c(1,2))
# 
# plot(refined.fc.arima.211.last.week, ylim = c(ylim.lower, ylim.upper),
#      type = "o", plot.conf = TRUE, shaded = FALSE, 
#      fcol = "red", pi.col = "red",
#      axes = FALSE, main = "Forecast for last week using Arima(2,1,1) model")
# 
# lines(fitted(refined.fc.arima.211.last.week), col = "red")
# 
# lines(window(close.price, start = tsp(refined.dataset.last.week)[1]), 
#       type = "o")
# 
# axis(1, at = seq(tsp(refined.fc.arima.211.last.week$x)[1], length(close.price), 5), 
#      labels = original.data[seq(tsp(refined.fc.arima.211.last.week$x)[1], length(close.price), 5), 1])
# axis(2)
# box()
# 
# abline(v = seq(tsp(refined.fc.arima.211.last.week$x)[1], length(close.price), 5), 
#        col = "springgreen4", 
#        lty = "dotted",
#        lwd = par("lwd"))
# 
# abline(h = seq(ylim.lower, ylim.upper, 0.3), 
#        col = "springgreen4", 
#        lty = "dotted",
#        lwd = par("lwd"))
# 
# 
# summary(refined.fc.arima.211.last.week)

plot(refined.fc.arima.010.last.week, ylim = c(ylim.lower, ylim.upper),
     type = "o", plot.conf = TRUE, shaded = FALSE, 
     fcol = "red", pi.col = "red",
     axes = FALSE, main = "Forecast for last week using Arima(0,1,0) model")

lines(fitted(refined.fc.arima.010.last.week), col = "red")

lines(window(close.price, start = tsp(refined.dataset.last.week)[1]), 
      type = "o")

axis(1, at = seq(tsp(refined.fc.arima.010.last.week$x)[1], length(close.price), 5), 
     labels = original.data[seq(tsp(refined.fc.arima.010.last.week$x)[1], length(close.price), 5), 1])
axis(2)
box()

abline(v = seq(tsp(refined.fc.arima.010.last.week$x)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower, ylim.upper, 0.3), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


summary(refined.fc.arima.010.last.week)


```


The actual value of the last week is in the 80% prediction interval. 

## Predict the index of the next 3 weeks

Before next prediction, training data and testing data are all used to refine the Arima model.
```{r, fig.height=7, fig.width=10}

refined.dataset <- window(close.price, start = 260) 

tsdisplay(refined.dataset)
```

```{r, fig.height=7, fig.width=10}

par(mfrow = c(2,1))
plot(refined.dataset)
plot(diff(refined.dataset))
abline(h = 0, col = "red")
```

```{r, fig.height=7, fig.width=10}

tsdisplay(diff(refined.dataset))
```

```{r}

##nsdiffs(refined.dataset)
ndiffs(refined.dataset)

```

```{r, fig.height=7, fig.width=10}

(fit.012.start260.endfinal <- Arima(refined.dataset, order = c(0,1,2)))

tsdisplay(residuals(fit.012.start260.endfinal))
```

```{r}

Box.test(residuals(fit.012.start260.endfinal), lag=4, fitdf=2)
Box.test(residuals(fit.012.start260.endfinal), lag=4, fitdf=2, type = "Lj")

```



```{r}
name.aicc <- c("Arima(refined.dataset, order = c(0,1,0))$aicc",
               "Arima(refined.dataset, order = c(0,1,1))$aicc",
               "Arima(refined.dataset, order = c(0,1,2))$aicc",
               "Arima(refined.dataset, order = c(0,1,3))$aicc",
               
               "Arima(refined.dataset, order = c(1,1,0))$aicc",
               "Arima(refined.dataset, order = c(1,1,1))$aicc",
               "Arima(refined.dataset, order = c(1,1,2))$aicc",
               "Arima(refined.dataset, order = c(1,1,3))$aicc",
               
               "Arima(refined.dataset, order = c(2,1,0))$aicc",
               "Arima(refined.dataset, order = c(2,1,1))$aicc",
               "Arima(refined.dataset, order = c(2,1,2))$aicc",
               "Arima(refined.dataset, order = c(2,1,3))$aicc",
               
               "Arima(refined.dataset, order = c(3,1,0))$aicc",
               "Arima(refined.dataset, order = c(3,1,1))$aicc",
               "Arima(refined.dataset, order = c(3,1,2))$aicc",
               "Arima(refined.dataset, order = c(3,1,3))$aicc",
               
               "Arima(refined.dataset, order = c(0,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset, order = c(0,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset, order = c(0,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset, order = c(0,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.dataset, order = c(1,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset, order = c(1,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset, order = c(1,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset, order = c(1,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.dataset, order = c(2,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset, order = c(2,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset, order = c(2,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset, order = c(2,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.dataset, order = c(3,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset, order = c(3,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset, order = c(3,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset, order = c(3,1,3), include.drift = TRUE)$aicc"
               
)

aicc <- unlist(lapply(lapply(name.aicc, parse, file = "", n = NULL), eval))

name <-  substr(name.aicc, 1, nchar(name.aicc) - 5)

df <- data.frame(name = sub("refined.dataset","",name), 
                 aicc = round(aicc, digits = 3))

(df[order(df$aicc),])

```

Arima(0,1,0) is preferred.


```{r}

auto.arima(refined.dataset, stepwise = FALSE, approximation = FALSE)

```

Arima(0,1,0) is selected by auto method.


```{r, fig.height=7, fig.width=10}

(fit.010.start260.endfinal <- Arima(refined.dataset, order = c(0,1,0)))

tsdisplay(residuals(fit.010.start260.endfinal))
```

```{r, fig.height=7, fig.width=10}

(fit.010.start260.endfinal <- Arima(refined.dataset, order = c(0,1,0)))

tsdisplay(residuals(fit.010.start260.endfinal))
```


```{r}

Box.test(residuals(fit.010.start260.endfinal), lag=4, fitdf=0)
Box.test(residuals(fit.010.start260.endfinal), lag=4, fitdf=0, type = "Lj")

```


#### Relationship Between Residuals And Time

```{r, fig.height=7, fig.width=10}
# dev.off()
par(mfrow = c(1,1))


plot(residuals(fit.010.start260.endfinal), axes = FALSE, main = "Arima(0,1,0)")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(refined.dataset)[1], tsp(refined.dataset)[2], 5), 
     labels = original.data[seq(tsp(refined.dataset)[1], 
                                tsp(refined.dataset)[2], 5), 1])
axis(2)
box()
```

#### Relationship Between Residuals And Fitted Value

```{r, fig.height=7, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.010.start260.endfinal)) ~ as.numeric(fitted(fit.010.start260.endfinal)), 
     main = "Arima(0,1,0)")
abline(h = 0, col = "red")


```

There is no obvious heteroscedasticity.


#### Normality of  Residuals

```{r, fig.height=7, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.010.start260.endfinal), main = "Arima(0,1,0)")
qqline(residuals(fit.010.start260.endfinal))
```

```{r, fig.height=7, fig.width=14}

prediction.length <- 3


refined.fc.arima.010.next3weeks <- forecast(fit.010.start260.endfinal, 
                          h = prediction.length,  
                          level = 80)

ylim.upper.next3weeks <- max(c(refined.fc.arima.010.next3weeks$x,
                    refined.fc.arima.010.next3weeks$upper)) + 0.1


ylim.lower.next3weeks <- min(c(refined.fc.arima.010.next3weeks$x,
                    refined.fc.arima.010.next3weeks$lower)) - 0.1

par(mfrow = c(1,1))
plot(refined.fc.arima.010.next3weeks, 
     ylim = c(ylim.lower.next3weeks, ylim.upper.next3weeks),
     type = "o", plot.conf = TRUE, shaded = FALSE, 
     fcol = "red", pi.col = "red",
     axes = FALSE, main = "Forecast for the next 3 weeks using Arima(0,1,0) model")

lines(fitted(refined.fc.arima.010.next3weeks), col = "red")

axis(1, at = seq(tsp(refined.fc.arima.010.next3weeks$x)[1], length(close.price), 5), 
     labels = original.data[seq(tsp(refined.fc.arima.010.next3weeks$x)[1], length(close.price), 5), 1])
axis(2)
box()

abline(v = seq(tsp(refined.fc.arima.010.next3weeks$x)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower.next3weeks, ylim.upper.next3weeks, 0.3), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


summary(refined.fc.arima.010.next3weeks)

```

The 80% prediction interval of stock index of the next week is []. So the possibility of the event that stock index is larger than  is 90% and the possibility of the event that stock index is larger than  is 10%, which can be treated as one type of condition of buying and selling.  
