---
title: "ARIMA Prediction Of Stock 999999"
author: "Wu Wei"
date: "2016-12-12"
output: html_document
---

## Synopsis

 Index data of stock 999999 was analyzed using Arima model  

* Arima model for data begining from 2015-12 is better, which can be used as a prediction tool right now


## Library input & Data Input
```{r}
suppressMessages(library(forecast))

setwd("d://MyR//stock//")
original.data <- read.csv("999999.csv")
# (original.data)
close.price <- as.ts(original.data[,5])

training.set.start250 <- window(close.price, start = 250, end = 280)
test.set <- window(close.price, start = 281)

training.set.start240 <- window(close.price, start = 240, end = 280)
```

## Analysis for data between 2016-3 and 2016-9

### Exploratory Data Analysis for data between 2016-3 and 2016-9
```{r}
# dev.off()
par(mfrow = c(1,1))

# plot(training.set.start250)
plot(training.set.start250, axes = FALSE, main = "stock index of 999999")
axis(1, 
     at = seq(tsp(training.set.start250)[1], tsp(training.set.start250)[2], 5), 
     labels = original.data[seq(tsp(training.set.start250)[1], 
                                tsp(training.set.start250)[2], 5), 1])
axis(2)
box()

abline(v = seq(tsp(training.set.start250)[1], tsp(training.set.start250)[2], 5), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(min(training.set.start250) - 50, 
               max(training.set.start250) + 50, 50), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))


```


### Modelling for data between 2016-3 and 2016-9

```{r, fig.height=9, fig.width=10}

tsdisplay(training.set.start250)
```

```{r, fig.height=8, fig.width=10}

par(mfrow = c(2,1))
plot(training.set.start250)
plot(diff(training.set.start250))
abline(h = 0, col = "red")
```

```{r, fig.height=8, fig.width=10}

tsdisplay(diff(training.set.start250))
```

```{r}

##nsdiffs(training.set.start250)
ndiffs(training.set.start250)

```

```{r, fig.height=8, fig.width=10}

(fit.010.start250 <- Arima(training.set.start250, order = c(0,1,0)))

tsdisplay(residuals(fit.010.start250))
```

```{r}

Box.test(residuals(fit.010.start250), lag=6, fitdf=0)
Box.test(residuals(fit.010.start250), lag=6, fitdf=0, type = "Lj")

```



```{r}
name.aicc <- c("Arima(training.set.start250, order = c(0,1,0))$aicc",
               "Arima(training.set.start250, order = c(0,1,1))$aicc",
               "Arima(training.set.start250, order = c(0,1,2))$aicc",
               
               "Arima(training.set.start250, order = c(1,1,0))$aicc",
               "Arima(training.set.start250, order = c(1,1,1))$aicc",
               "Arima(training.set.start250, order = c(1,1,2))$aicc",
               
               "Arima(training.set.start250, order = c(2,1,0))$aicc",
               "Arima(training.set.start250, order = c(2,1,1))$aicc",
               "Arima(training.set.start250, order = c(2,1,2))$aicc",

               "Arima(training.set.start250, order = c(0,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.start250, order = c(0,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.start250, order = c(0,1,2), include.drift = TRUE)$aicc",
               
               "Arima(training.set.start250, order = c(1,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.start250, order = c(1,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.start250, order = c(1,1,2), include.drift = TRUE)$aicc",
               
               "Arima(training.set.start250, order = c(2,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.start250, order = c(2,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.start250, order = c(2,1,2), include.drift = TRUE)$aicc"
)

aicc <- unlist(lapply(lapply(name.aicc, parse, file = "", n = NULL), eval))

name <-  substr(name.aicc, 1, nchar(name.aicc) - 5)

df <- data.frame(name = sub("training.set","",name), 
                 aicc = round(aicc, digits = 3))

(df[order(df$aicc),])

```

Arima(0,1,0) is preferred.


```{r}

auto.arima(training.set.start250, stepwise = FALSE, approximation = FALSE)

```

Arima(0,1,0) is also selected by auto method.

#### Relationship Between Residuals And Time(for data between 2016-3 and 2016-9)

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.010.start250), axes = FALSE, main = "Arima(0,1,0)")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(training.set.start250)[1], tsp(training.set.start250)[2], 5), 
     labels = original.data[seq(tsp(training.set.start250)[1], 
                                tsp(training.set.start250)[2], 5), 1])
axis(2)
box()
```

#### Relationship Between Residuals And Fitted Value(for data between 2016-3 and 2016-9)

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.010.start250)) ~ as.numeric(fitted(fit.010.start250)), 
     main = "Arima(0,1,0)")
abline(h = 0, col = "red")



```

There is no obvious heteroscedasticity.


#### Normality of  Residuals(for data between 2016-3 and 2016-9)

```{r}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.010.start250), main = "Arima(0,1,0)")
qqline(residuals(fit.010.start250))

```

Residuals conform to normality.

#### Comparison between actual value and forecast result (for data between 2016-3 and 2016-9)

```{r}
par(mfrow = c(1,1))
fc.arima.start250 <- forecast(fit.010.start250, h = length(test.set), 
                              level = c(80,95))

ylim.upper <- max(c(test.set,
                    fc.arima.start250$upper, 
                    fc.arima.start250$x)) + 30

ylim.lower <- min(c(test.set,
                    fc.arima.start250$lower, 
                    fc.arima.start250$x)) - 30


plot(fc.arima.start250, ylim = c(ylim.lower, ylim.upper),
     type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
     axes = FALSE, main = "Arima(0,1,0)")
lines(test.set, type = "o",col = "red")


axis(1, at = seq(tsp(training.set.start250)[1], tsp(close.price)[2], 5), 
     labels = original.data[seq(tsp(training.set.start250)[1], tsp(close.price)[2], 5), 1])
axis(2)
box()

abline(v = seq(tsp(training.set.start250)[1], tsp(close.price)[2], 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower, ylim.upper, 50), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


```


## Analysis for data between 2015-12 and 2016-9

### Exploratory Data Analysis for data between 2016-12 and 2016-9
```{r}
par(mfrow = c(1,1))

# plot(training.set.start250)
plot(training.set.start240, axes = FALSE, main = "stock index of 999999")
axis(1, at = seq(tsp(training.set.start240)[1], tsp(training.set.start240)[2], 5), 
     labels = original.data[seq(tsp(training.set.start240)[1], tsp(training.set.start240)[2], 5), 1])
axis(2)
box()

abline(v = seq(tsp(training.set.start240)[1], tsp(training.set.start240)[2], 5), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(min(training.set.start240) - 50, 
               max(training.set.start240) + 50, 100), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))


```

It seems that there is no season pattern, but we can assume there is trend pattern.

### Modelling for data between 2015-12 and 2016-9

```{r, fig.height=8, fig.width=10}
tsdisplay(training.set.start240)
```

```{r, fig.height=8, fig.width=10}
par(mfrow = c(2,1))
plot(training.set.start240)
plot(diff(training.set.start240))
abline(h = 0, col = "red")
```

```{r, fig.height=8, fig.width=10}
tsdisplay(diff(training.set.start240))
```

```{r}
##nsdiffs(training.set.start240)
ndiffs(training.set.start240)

```



```{r, fig.height=8, fig.width=10}

(fit.100.start240 <- Arima(training.set.start240, order = c(1,0,0)))

tsdisplay(residuals(fit.100.start240))
```



```{r, fig.height=8, fig.width=10}

Box.test(residuals(fit.100.start240), lag=8, fitdf=1)
Box.test(residuals(fit.100.start240), lag=8, fitdf=1, type = "Lj")

```

```{r}
name.aicc <- c("Arima(training.set.start240, order = c(1,0,0))$aicc",
               "Arima(training.set.start240, order = c(2,0,0))$aicc",
               "Arima(training.set.start240, order = c(3,0,0))$aicc",
               
               "Arima(training.set.start240, order = c(0,0,1))$aicc",
               "Arima(training.set.start240, order = c(1,0,1))$aicc",
               "Arima(training.set.start240, order = c(2,0,1))$aicc",
               "Arima(training.set.start240, order = c(3,0,1))$aicc",
               
               "Arima(training.set.start240, order = c(0,0,2))$aicc",
               "Arima(training.set.start240, order = c(1,0,2))$aicc",
               "Arima(training.set.start240, order = c(2,0,2))$aicc",
               "Arima(training.set.start240, order = c(3,0,2))$aicc"
               
)

aicc <- unlist(lapply(lapply(name.aicc, parse, file = "", n = NULL), eval))

df <- data.frame(name = name.aicc, aicc = aicc)

(df[order(df$aicc),])

```

Arima(2,0,1) is preferred.


```{r}

auto.arima(training.set.start240, stepwise = FALSE, approximation = FALSE)

```

Arima(2,0,1) is also selected by auto method.

```{r, fig.height=8, fig.width=10}

(fit.201.start240 <- Arima(training.set.start240, order = c(2,0,1)))

tsdisplay(residuals(fit.201.start240))
```


```{r, fig.height=8, fig.width=10}

Box.test(residuals(fit.201.start240), lag=8, fitdf=3)
Box.test(residuals(fit.201.start240), lag=8, fitdf=3, type = "Lj")

```


#### Relationship Between Residuals And Time(for data between 2015-12 and 2016-9)

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.201.start240), axes = FALSE, main = "Arima(2,0,1)")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(training.set.start240)[1], tsp(training.set.start240)[2], 5), 
     labels = original.data[seq(tsp(training.set.start240)[1], 
                                tsp(training.set.start240)[2], 5), 1])
axis(2)
box()
```

#### Relationship Between Residuals And Fitted Value(for data between 2015-12 and 2016-9)

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.201.start240)) ~ as.numeric(fitted(fit.201.start240)), 
     main = "Arima(2,0,1)")
abline(h = 0, col = "red")

```

There is no obvious heteroscedasticity.

#### Normality of  Residuals(for data between 2015-12 and 2016-9)

```{r}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.201.start240), main = "Arima(2,0,1)")
qqline(residuals(fit.201.start240))

```


#### Comparison between actual value and forecast result (for data between 2015-12 and 2016-9)

```{r}
par(mfrow = c(1,1))


fc.arima.start240 <- forecast(fit.201.start240, h = length(test.set), 
                              level = c(80,95))

ylim.upper <- max(c(fc.arima.start240$upper, 
                    fc.arima.start240$x)) + 30

ylim.lower <- min(c(fc.arima.start240$lower, 
                    fc.arima.start240$x)) - 30

plot(fc.arima.start240, ylim = c(ylim.lower, ylim.upper),
     type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
     axes = FALSE, main = "Arima(2,0,1)")
lines(test.set, type = "o",col = "red")

axis(1, at = seq(tsp(training.set.start240)[1], tsp(close.price)[2], 5), 
     labels = original.data[seq(tsp(training.set.start240)[1], tsp(close.price)[2], 5), 1])
axis(2)
box()

abline(v = seq(tsp(training.set.start240)[1], tsp(close.price)[2], 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower, ylim.upper, 50), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


```

Comparing with actual value of test set, forecast result of Arima(2,0,1) model is reasonable for a long time.


## Comparison between Arima(0,1,0) model (for data between 2016-3 and 2016-9) and Arima(2,0,1) model (for data between 2015-12 and 2016-9) and Holt model (for data between 2016-3 and 2016-9)



### Accuracy Of Training Set
```{r}
fit.holt.start250 <- holt(training.set.start250, 
                          h = length(test.set),  
                          damped = TRUE,
                          level = c(80,95))

df.training.set.comparison <- rbind(accuracy(fit.010.start250),
            accuracy(fit.201.start240),
            accuracy(fit.holt.start250))

row.names(df.training.set.comparison) <- c("Arima(0,1,0) 2016-3", 
                                           "Arima(2,0,1) 2015-12",
                                           "Holt model 2016-3")
print(round(df.training.set.comparison, 3))


```

Arima(0,1,0) model for data begining from 2016-3 is better.

### White Noise Test
```{r}
Box.test(residuals(fit.010.start250), lag=6, fitdf=0)
Box.test(residuals(fit.010.start250), lag=6, fitdf=0, type = "Lj")

Box.test(residuals(fit.201.start240), lag=8, fitdf=3)
Box.test(residuals(fit.201.start240), lag=8, fitdf=3, type = "Lj")

Box.test(residuals(fit.holt.start250), lag=6, fitdf=3)
Box.test(residuals(fit.holt.start250), lag=6, fitdf=3, type = "Lj")
```


### Relationship Between Residuals And Fitted Value

```{r, fig.height=7, fig.width=14}
# dev.off()
par(mfrow = c(1,3))

plot(as.numeric(residuals(fit.010.start250)) ~ as.numeric(fitted(fit.010.start250)), 
     main = "Arima(0,1,0) model for data between 2016-3 and 2016-9")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.201.start240)) ~ as.numeric(fitted(fit.201.start240)), 
     main = "Arima(2,0,1) model for data between 2015-12 and 2016-9")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.holt.start250)) ~ as.numeric(fitted(fit.holt.start250)), 
     main = "Holt model for data between 2016-3 and 2016-9")
abline(h = 0, col = "red")

```


### Normality of  Residuals

```{r, fig.height=7, fig.width=14}
# dev.off()
par(mfrow = c(1,3))

qqnorm(residuals(fit.010.start250), main = "Arima(0,1,0) model for data between 2016-3 and 2016-9")
qqline(residuals(fit.010.start250))

qqnorm(residuals(fit.201.start240), main = "Arima(2,0,1) model for data between 2015-12 and 2016-9")
qqline(residuals(fit.201.start240))

qqnorm(residuals(fit.holt.start250), main = "Holt model for data between 2016-3 and 2016-9")
qqline(residuals(fit.holt.start250))

```

### Accuracy Of Test Set

```{r}
df.test.set.comparison <- rbind(
        accuracy(forecast(fit.010.start250, h = length(test.set)), test.set)[2,],
        accuracy(forecast(fit.201.start240, h = length(test.set)), test.set)[2,],
        accuracy(forecast(fit.holt.start250, h = length(test.set)), test.set)[2,])

row.names(df.test.set.comparison) <- c("Arima010 16/3", 
                                       "Arima201 15/12",
                                       "Holt 16/3")
print(round(df.test.set.comparison, 3))

```

Holt model from 2016-3 is better.

#### Comparison between actual value and forecast result (for data between 2015-12 and 2016-9)

```{r, fig.height=7, fig.width=14}
# dev.off()

ylim.upper.comparison <- max(c(fc.arima.start240$upper, 
                    fc.arima.start240$x,
                    fc.arima.start250$upper,
                    fit.holt.start250$upper)) + 30

ylim.lower.comparison <- min(c(fc.arima.start240$lower, 
                    fc.arima.start240$x,
                    fc.arima.start250$lower,
                    fit.holt.start250$lower)) - 30


par(mfrow = c(1,3))


plot(fc.arima.start250, 
     ylim = c(ylim.lower.comparison, ylim.upper.comparison),
     type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
     axes = FALSE, main = "Arima(0,1,0) model for data between 2016-3 and 2016-9")
lines(test.set, col = "red")

axis(1, at = seq(tsp(training.set.start250)[1], length(close.price), 5), 
     labels = FALSE)

text(seq(tsp(training.set.start250)[1], length(close.price), 5), 
     par("usr")[3] - 50, 
     labels = original.data[seq(tsp(training.set.start250)[1], length(close.price), 5), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2)
box()

abline(v = seq(tsp(training.set.start250)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower.comparison, ylim.upper.comparison, 50), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))



###"Arima(2,0,1) model for data between 2015-12 and 2016-9"
plot(fc.arima.start240, 
     ylim = c(ylim.lower.comparison, ylim.upper.comparison),
     type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
     axes = FALSE, main = "Arima(2,0,1) model for data between 2015-12 and 2016-9")
lines(test.set, col = "red")
axis(1, at = seq(tsp(training.set.start240)[1], length(close.price), 5), 
     labels = FALSE)

text(seq(240, length(close.price), 5), 
     par("usr")[3] - 50, 
     labels = original.data[seq(tsp(training.set.start240)[1], length(close.price), 5), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)


axis(2)
box()

abline(v = seq(tsp(training.set.start240)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower.comparison, ylim.upper.comparison, 50), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

###"Holt model for data between 2016-3 and 2016-9"

plot(fit.holt.start250, 
     ylim = c(ylim.lower.comparison, ylim.upper.comparison),
     type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
     axes = FALSE, main = "Holt model for data between 2016-3 and 2016-9")
lines(test.set, col = "red")

axis(1, at = seq(tsp(training.set.start250)[1], length(close.price), 5), 
     labels = FALSE)

text(seq(tsp(training.set.start250)[1], length(close.price), 5), 
     par("usr")[3] - 50, 
     labels = original.data[seq(tsp(training.set.start250)[1], length(close.price), 5), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2)
box()

abline(v = seq(tsp(training.set.start250)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower.comparison, ylim.upper.comparison, 50), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


```

Holt model for data begining from 2016-3 is better .

## Conclusion

* Arima(0,1,0) model for data begining from 2016-3 is better in Arima family, which can be used as a prediction tool


## Review of the prediction of the last 5 weeks
```{r, fig.height=8, fig.width=10}
review.length <- 5

refined.training.set.last5weeks <- 
        window(close.price, start = 250, end = length(close.price) - review.length)

refined.test.set.last5weeks <- 
        window(close.price, start = length(close.price) - review.length + 1)


tsdisplay(refined.training.set.last5weeks, lag.max = 40)
```

```{r, fig.height=8, fig.width=10}

par(mfrow = c(2,1))
plot(refined.training.set.last5weeks)
plot(diff(refined.training.set.last5weeks))
abline(h = 0, col = "red")
```

```{r, fig.height=8, fig.width=10}

tsdisplay(diff(refined.training.set.last5weeks))
```

```{r}

##nsdiffs(refined.training.set.last5weeks)
ndiffs(refined.training.set.last5weeks)

```

```{r, fig.height=8, fig.width=10}

(fit.010.last5weeks <- Arima(refined.training.set.last5weeks, order = c(0,1,0)))

tsdisplay(residuals(fit.010.last5weeks))

```

```{r}

Box.test(residuals(fit.010.last5weeks), lag=7, fitdf=0)
Box.test(residuals(fit.010.last5weeks), lag=7, fitdf=0, type = "Lj")

```



```{r}
name.aicc <- c("Arima(refined.training.set.last5weeks, order = c(0,1,0))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(0,1,1))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(0,1,2))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(0,1,3))$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(1,1,0))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(1,1,1))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(1,1,2))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(1,1,3))$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(2,1,0))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(2,1,1))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(2,1,2))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(2,1,3))$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(3,1,0))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(3,1,1))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(3,1,2))$aicc",
               "Arima(refined.training.set.last5weeks, order = c(3,1,3))$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(0,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(0,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(0,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(0,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(1,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(1,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(1,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(1,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(2,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(2,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(2,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(2,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.training.set.last5weeks, order = c(3,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(3,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(3,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.training.set.last5weeks, order = c(3,1,3), include.drift = TRUE)$aicc"
               
)

aicc <- unlist(lapply(lapply(name.aicc, parse, file = "", n = NULL), eval))

name <-  substr(name.aicc, 1, nchar(name.aicc) - 5)

df <- data.frame(name = sub("refined.training.set","",name), 
                 aicc = round(aicc, digits = 3))

(df[order(df$aicc),])

```

Arima(0,1,0) is preferred.


```{r}

auto.arima(refined.training.set.last5weeks, stepwise = FALSE, approximation = FALSE)
                       

```

Arima(0,1,0) is also selected by auto method.



#### Relationship Between Residuals And Time

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.010.last5weeks), axes = FALSE, main = "Arima(0,1,0)")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(refined.training.set.last5weeks)[1], tsp(refined.training.set.last5weeks)[2], 5), 
     labels = original.data[seq(tsp(refined.training.set.last5weeks)[1], 
                                tsp(refined.training.set.last5weeks)[2], 5), 1])
axis(2)
box()
```

#### Relationship Between Residuals And Fitted Value

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.010.last5weeks)) ~ as.numeric(fitted(fit.010.last5weeks)), 
     main = "Arima(0,1,0)")
abline(h = 0, col = "red")



```

There is no obvious heteroscedasticity.


#### Normality of  Residuals

```{r}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.010.last5weeks), main = "Arima(0,1,0)")
qqline(residuals(fit.010.last5weeks))

```


#### Predict the index of the last 5 weeks

```{r, fig.height=7, fig.width=14}
refined.fc.arima.last5weeks <- forecast(fit.010.last5weeks, #h = 70, 
                          h = review.length,  
                          level = c(80,95))


ylim.upper.last5weeks <- max(c(refined.fc.arima.last5weeks$upper, 
                    refined.fc.arima.last5weeks$x)) + 30


ylim.lower.last5weeks <- min(c(refined.fc.arima.last5weeks$lower, 
                    refined.fc.arima.last5weeks$x)) - 30

plot(refined.fc.arima.last5weeks, 
     ylim = c(ylim.lower.last5weeks, ylim.upper.last5weeks),
     type = "o", plot.conf = TRUE, shaded = TRUE, 
     fcol = "red", pi.col = "red",
     axes = FALSE, main = "Forecast for the last 5 weeks using Arima(0,1,0) model")

lines(fitted(refined.fc.arima.last5weeks), col = "red")

lines(window(close.price, start = tsp(refined.training.set.last5weeks)[1]), 
      type = "o")

axis(1, at = seq(tsp(refined.training.set.last5weeks)[1], length(close.price), 5), 
     labels = original.data[seq(tsp(refined.training.set.last5weeks)[1], length(close.price), 5), 1])
axis(2)
box()

abline(v = seq(tsp(refined.fc.arima.last5weeks$x)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower, ylim.upper, 50), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


summary(refined.fc.arima.last5weeks)

```


The actual values of the last 5 weeks are in the 80% prediction interval of the prediction. 

## Review of the prediction of the last week
```{r, fig.height=8, fig.width=10}

refined.dataset.last.week <- window(close.price, start = 250, end = length(close.price) - 1)

tsdisplay(refined.dataset.last.week)
```

```{r, fig.height=8, fig.width=10}

par(mfrow = c(2,1))
plot(refined.dataset.last.week)
plot(diff(refined.dataset.last.week))
abline(h = 0, col = "red")
```

```{r, fig.height=8, fig.width=10}

tsdisplay(diff(refined.dataset.last.week))
```

```{r}

##nsdiffs(refined.dataset.last.week)
ndiffs(refined.dataset.last.week)

```

```{r, fig.height=8, fig.width=10}

(fit.010.last.week <- Arima(refined.dataset.last.week, order = c(0,1,0)))

tsdisplay(residuals(fit.010.last.week))
```

```{r}

Box.test(residuals(fit.010.last.week), lag=8, fitdf=0)
Box.test(residuals(fit.010.last.week), lag=8, fitdf=0, type = "Lj")

```



```{r}
name.aicc <- c("Arima(refined.dataset.last.week, order = c(0,1,0))$aicc",
               "Arima(refined.dataset.last.week, order = c(0,1,1))$aicc",
               "Arima(refined.dataset.last.week, order = c(0,1,2))$aicc",
               "Arima(refined.dataset.last.week, order = c(0,1,3))$aicc",
               
               "Arima(refined.dataset.last.week, order = c(1,1,0))$aicc",
               "Arima(refined.dataset.last.week, order = c(1,1,1))$aicc",
               "Arima(refined.dataset.last.week, order = c(1,1,2))$aicc",
               "Arima(refined.dataset.last.week, order = c(1,1,3))$aicc",
               
               "Arima(refined.dataset.last.week, order = c(2,1,0))$aicc",
               "Arima(refined.dataset.last.week, order = c(2,1,1))$aicc",
               "Arima(refined.dataset.last.week, order = c(2,1,2))$aicc",
               "Arima(refined.dataset.last.week, order = c(2,1,3))$aicc",
               
               "Arima(refined.dataset.last.week, order = c(3,1,0))$aicc",
               "Arima(refined.dataset.last.week, order = c(3,1,1))$aicc",
               "Arima(refined.dataset.last.week, order = c(3,1,2))$aicc",
               "Arima(refined.dataset.last.week, order = c(3,1,3))$aicc",
               
               "Arima(refined.dataset.last.week, order = c(0,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(0,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(0,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(0,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.dataset.last.week, order = c(1,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(1,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(1,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(1,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.dataset.last.week, order = c(2,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(2,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(2,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(2,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.dataset.last.week, order = c(3,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(3,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(3,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.last.week, order = c(3,1,3), include.drift = TRUE)$aicc"
)

aicc <- unlist(lapply(lapply(name.aicc, parse, file = "", n = NULL), eval))

name <-  substr(name.aicc, 1, nchar(name.aicc) - 5)

df <- data.frame(name = sub("refined.dataset","",name), 
                 aicc = round(aicc, digits = 3))

(df[order(df$aicc),])

```

Arima(0,1,0) is preferred.


```{r}

auto.arima(refined.dataset.last.week, stepwise = FALSE, approximation = FALSE)

```

Arima(0,1,0) is also selected by auto method.



#### Relationship Between Residuals And Time

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.010.last.week), axes = FALSE, main = "Arima(0,1,0)")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(refined.dataset.last.week)[1], tsp(refined.dataset.last.week)[2], 5), 
     labels = original.data[seq(tsp(refined.dataset.last.week)[1], 
                                tsp(refined.dataset.last.week)[2], 5), 1])
axis(2)
box()
```

#### Relationship Between Residuals And Fitted Value

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.010.last.week)) ~ as.numeric(fitted(fit.010.last.week)), 
     main = "Arima(0,1,0)")
abline(h = 0, col = "red")



```

There is no obvious heteroscedasticity.


#### Normality of  Residuals

```{r}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.010.last.week), main = "Arima(0,1,0)")
qqline(residuals(fit.010.last.week))

```


#### Predict the index of last week

```{r, fig.height=7, fig.width=14}
refined.fc.arima.last.week <- forecast(fit.010.last.week, 
                          h = 1,  
                          level = 80)


ylim.upper <- max(c(refined.fc.arima.last.week$upper, 
                    refined.fc.arima.last.week$x)) + 30


ylim.lower <- min(c(refined.fc.arima.last.week$lower, 
                    refined.fc.arima.last.week$x)) - 30

plot(refined.fc.arima.last.week, ylim = c(ylim.lower, ylim.upper),
     type = "o", plot.conf = TRUE, shaded = FALSE, 
     fcol = "red", pi.col = "red",
     axes = FALSE, main = "Forecast for last week using Arima(0,1,0) model")

lines(fitted(refined.fc.arima.last.week), col = "red")

lines(window(close.price, start = tsp(refined.dataset.last.week)[1]), 
      type = "o")

axis(1, at = seq(tsp(refined.fc.arima.last.week$x)[1], length(close.price), 5), 
     labels = original.data[seq(tsp(refined.fc.arima.last.week$x)[1], length(close.price), 5), 1])
axis(2)
box()

abline(v = seq(tsp(refined.fc.arima.last.week$x)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower, ylim.upper, 50), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


summary(refined.fc.arima.last.week)

```


The actual value of the last week is outside the 80% prediction interval. 

## Predict the index of the next 3 weeks

Before prediction, training data and testing data are all used to refine the Arima model.
```{r, fig.height=10, fig.width=10}

refined.dataset.next3weeks <- window(close.price, start = 250) 

tsdisplay(refined.dataset.next3weeks)
```

```{r, fig.height=8, fig.width=10}

par(mfrow = c(2,1))
plot(refined.dataset.next3weeks)
plot(diff(refined.dataset.next3weeks))
abline(h = 0, col = "red")
```

```{r, fig.height=8, fig.width=10}

tsdisplay(diff(refined.dataset.next3weeks))
```

```{r}

##nsdiffs(refined.dataset.next3weeks)
ndiffs(refined.dataset.next3weeks)

```

```{r, fig.height=8, fig.width=10}

(fit.010.endfinal <- Arima(refined.dataset.next3weeks, order = c(0,1,0)))

tsdisplay(residuals(fit.010.endfinal))
```

```{r}

Box.test(residuals(fit.010.endfinal), lag=8, fitdf=0)
Box.test(residuals(fit.010.endfinal), lag=8, fitdf=0, type = "Lj")

```

```{r}
name.aicc <- c("Arima(refined.dataset.next3weeks, order = c(0,1,0))$aicc",
               "Arima(refined.dataset.next3weeks, order = c(0,1,1))$aicc",
               "Arima(refined.dataset.next3weeks, order = c(0,1,2))$aicc",
               "Arima(refined.dataset.next3weeks, order = c(0,1,3))$aicc",
               
               "Arima(refined.dataset.next3weeks, order = c(1,1,0))$aicc",
               "Arima(refined.dataset.next3weeks, order = c(1,1,1))$aicc",
               "Arima(refined.dataset.next3weeks, order = c(1,1,2))$aicc",
               "Arima(refined.dataset.next3weeks, order = c(1,1,3))$aicc",
               
               "Arima(refined.dataset.next3weeks, order = c(2,1,0))$aicc",
               "Arima(refined.dataset.next3weeks, order = c(2,1,1))$aicc",
               "Arima(refined.dataset.next3weeks, order = c(2,1,2))$aicc",
               "Arima(refined.dataset.next3weeks, order = c(2,1,3))$aicc",
               
               "Arima(refined.dataset.next3weeks, order = c(3,1,0))$aicc",
               "Arima(refined.dataset.next3weeks, order = c(3,1,1))$aicc",
               "Arima(refined.dataset.next3weeks, order = c(3,1,2))$aicc",
               "Arima(refined.dataset.next3weeks, order = c(3,1,3))$aicc",
               
               "Arima(refined.dataset.next3weeks, order = c(0,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.next3weeks, order = c(0,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.next3weeks, order = c(0,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.next3weeks, order = c(0,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.dataset.next3weeks, order = c(1,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.next3weeks, order = c(1,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.next3weeks, order = c(1,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.next3weeks, order = c(1,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.dataset.next3weeks, order = c(2,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.next3weeks, order = c(2,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.next3weeks, order = c(2,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.next3weeks, order = c(2,1,3), include.drift = TRUE)$aicc",
               
               "Arima(refined.dataset.next3weeks, order = c(3,1,0), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.next3weeks, order = c(3,1,1), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.next3weeks, order = c(3,1,2), include.drift = TRUE)$aicc",
               "Arima(refined.dataset.next3weeks, order = c(3,1,3), include.drift = TRUE)$aicc"
               
)

aicc <- unlist(lapply(lapply(name.aicc, parse, file = "", n = NULL), eval))

name <-  substr(name.aicc, 1, nchar(name.aicc) - 5)

df <- data.frame(name = sub("refined.dataset","",name), 
                 aicc = round(aicc, digits = 3))

(df[order(df$aicc),])

```

Arima(0,1,0) is preferred.


```{r}

auto.arima(refined.dataset.next3weeks, stepwise = FALSE, approximation = FALSE)

```

Arima(0,1,0) is also selected by auto method.



#### Relationship Between Residuals And Time

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.010.endfinal), axes = FALSE, main = "Arima(0,1,0)")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(refined.dataset.next3weeks)[1], tsp(refined.dataset.next3weeks)[2], 5), 
     labels = original.data[seq(tsp(refined.dataset.next3weeks)[1], 
                                tsp(refined.dataset.next3weeks)[2], 5), 1])
axis(2)
box()
```

#### Relationship Between Residuals And Fitted Value

```{r}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.010.endfinal)) ~ as.numeric(fitted(fit.010.endfinal)), 
     main = "Arima(0,1,0)")
abline(h = 0, col = "red")



```

There is no obvious heteroscedasticity.

#### Normality of  Residuals

```{r}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.010.endfinal), main = "Arima(0,1,0)")
qqline(residuals(fit.010.endfinal))

```

#### Predict the next 3 weeks

```{r, fig.height=7}
prediction.length <- 3

refined.fc.arima.next3weeks <- forecast(fit.010.endfinal, 
                          h = prediction.length,  
                          level = 80)


ylim.upper.next3weeks <- max(c(refined.fc.arima.next3weeks$upper, 
                    refined.fc.arima.next3weeks$x)) + 30


ylim.lower.next3weeks <- min(c(refined.fc.arima.next3weeks$lower, 
                    refined.fc.arima.next3weeks$x)) - 30

plot(refined.fc.arima.next3weeks, 
     ylim = c(ylim.lower.next3weeks, ylim.upper.next3weeks),
     type = "o", plot.conf = TRUE, shaded = FALSE, 
     fcol = "red", pi.col = "red",
     axes = FALSE, main = "Forecast for next 3 weeks using Arima(0,1,0) model")

lines(fitted(refined.fc.arima.next3weeks), col = "red")

axis(1, at = seq(tsp(refined.fc.arima.next3weeks$x)[1], length(close.price), 5), 
     labels = original.data[seq(tsp(refined.fc.arima.next3weeks$x)[1], length(close.price), 5), 1])
axis(2)
box()

abline(v = seq(tsp(refined.fc.arima.next3weeks$x)[1], length(close.price), 5), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))

abline(h = seq(ylim.lower.next3weeks, ylim.upper.next3weeks, 50), 
       col = "springgreen4", 
       lty = "dotted",
       lwd = par("lwd"))


summary(refined.fc.arima.next3weeks)

```

The 80% prediction interval of stock index of the next week is []. So the possibility of the event that stock index is larger than xxx is 90% and the possibility of the event that stock index is larger than xxx is 10%, which can be treated as one type of condition of buying and selling.  
