---
title: "ARIMA Prediction Of Gold compound return"
author: "Wu Wei"
date: "2017-8-19"
output: html_document
---



```{r library, echo = FALSE}
rm(list = ls())

suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
suppressMessages(library(rugarch))
suppressMessages(library(lmtest))
suppressMessages(library(tseries))
suppressMessages(library(fBasics))
suppressMessages(library(Rdonlp2))
suppressMessages(library("FinTS"))
suppressMessages(library("vars"))
```

```{r source, echo = FALSE}
source("d://MyR//stock//CompareObjectGoldDollarVARAccuracy.r")
source("d://MyR//stock//CompareObjectNNARAccuracy.r")
source("d://MyR//stock//CompareObjectAccuracy.R")
source("d://MyR//stock//CompareObjectNaiveAccuracy.R")
source("d://MyR//stock//CompareObjectArfimaAccuracy.r")

source("d://MyR//zhao//CompareObjectAccuracyArimaNolimitation.R")
```


## 1.Analyse for monthly gold price


```{r appendix 1-1, echo = TRUE}


setwd("d://MyR//stock//")
monthly.original.data <- read.csv("goldmonthly.csv")
# View(monthly.original.data)

monthly.close.price <- monthly.original.data$Close
monthly.dollar.index <- monthly.original.data$dollarindex

## The last month has not passed completely. So it is cancelled.
monthly.close.price <- monthly.close.price[-length(monthly.close.price)]
monthly.dollar.index <- monthly.dollar.index[-length(monthly.dollar.index)]


## 19900101 ~ 20170630

monthly.gold.compound.return <- diff(log(monthly.close.price)) * 100
names(monthly.gold.compound.return) <- monthly.original.data$Time[-c(1,length(monthly.original.data$Time))]
monthly.gold.compound.return <- ts(monthly.gold.compound.return, start = c(1990, 2), frequency = 12)


monthly.dollar.compound.return <- diff(log(monthly.dollar.index)) * 100
names(monthly.dollar.compound.return) <- monthly.original.data$Time[-c(1,length(monthly.original.data$Time))]
monthly.dollar.compound.return <- ts(monthly.dollar.compound.return, start = c(1990, 2), frequency = 12)
```


```{r appendix 1-2, fig.height=8, fig.width=10}

tsdisplay(monthly.gold.compound.return)
```

```{r appendix 1-3, eval=TRUE}

ndiffs(monthly.gold.compound.return)

```


```{r Appendix 1-4}
summary(monthly.gold.compound.return)

monthly.gold.compound.return[monthly.gold.compound.return == max(monthly.gold.compound.return)]

monthly.gold.compound.return[monthly.gold.compound.return == min(monthly.gold.compound.return)]
```

```{r appendix 1-5}
mean(monthly.gold.compound.return)
sd(monthly.gold.compound.return)
skewness(monthly.gold.compound.return)
kurtosis(monthly.gold.compound.return)
jarqueberaTest(monthly.gold.compound.return)

```

```{r appendix 1-6, cache=TRUE, eval=TRUE}
(fit.arima.monthly.return <- auto.arima(monthly.gold.compound.return, seasonal = FALSE,
                                                  stepwise = FALSE, approximation = FALSE))

```

### 1.1 White Noise Test


```{r  appendix 1.1-1, cache=FALSE, eval=TRUE}


Box.test(residuals(fit.arima.monthly.return), 
         lag=10, 
         fitdf=sum(fit.arima.monthly.return$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.monthly.return), 
         lag=20, 
         fitdf=sum(fit.arima.monthly.return$arma[c(1,2)]), type = "Lj")

```

### 1.2  Relationship Between Residuals And Time

```{r appendix 1.2-1, fig.height=6, fig.width=10, cache=FALSE, eval=TRUE}

plot(residuals(fit.arima.monthly.return), axes = TRUE)
abline(h = 0, col = "red")

```

### 1.3 Relationship Between Residuals And Fitted Value

```{r appendix 1.3-1, fig.height=6, fig.width=10, eval=TRUE}

plot(as.numeric(residuals(fit.arima.monthly.return)) ~ as.numeric(fitted(fit.arima.monthly.return)))
abline(h = 0, col = "red")


```


### 1.4 Normality of Residuals

```{r appendix 1.4-1, fig.height=6, fig.width=10, eval=TRUE}

qqnorm(residuals(fit.arima.monthly.return))
qqline(residuals(fit.arima.monthly.return))


```

### 1.5 ARCH Effect Test


```{r appendix 1.5-1, eval=TRUE}

Box.test((residuals(fit.arima.monthly.return))^2, 
         lag=10, 
         fitdf=sum(fit.arima.monthly.return$arma[c(1,2)]), type = "Lj")

Box.test((residuals(fit.arima.monthly.return))^2, 
         lag=20, 
         fitdf=sum(fit.arima.monthly.return$arma[c(1,2)]), type = "Lj")

ArchTest(residuals(fit.arima.monthly.return))



```

## 2 Comparison of pure Arima model with naive model

```{r appendix 2-1, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}



comparison.period <- 20

forecast.period <- 4

training.set.endpoint <- length(monthly.gold.compound.return) - comparison.period - forecast.period

maxorder <- 5
```

```{r appendix 2-2, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}

result.naive <- CompareObjectNaiveAccuracy(arg.object = monthly.gold.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 2-3, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}


result.pure <- CompareObjectAccuracy(arg.object = monthly.gold.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 2-4, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.pure$RMSE - result.naive$RMSE)

final.result <- cbind(result.pure,
                      result.naive)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "sigma","RMSE", "p.v",
                            "p2","d2","q2", "dr2","RMSE2", "p.v2")

print(final.result)

sum(final.result$RMSE > final.result$RMSE2)

sum(final.result$p.v > 0.05)

sum(final.result$p.v2 > 0.05)

```

Arima model should not be replaced by naive model.


## 3 Comparison of pure Arima models



```{r appendix 3-2, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}
result.pure.no.limitation <- CompareObjectAccuracyArimaNolimitation(arg.object = monthly.gold.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 3-3, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.pure$RMSE - result.pure.no.limitation$RMSE)

final.result <- cbind(result.pure,
                      result.pure.no.limitation)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "sigma","RMSE", "p.v",
                            "p2","d2","q2", "dr2","RMSE2", "p.v2")

print(final.result)

sum(final.result$RMSE > final.result$RMSE2)

sum(final.result$p.v > 0.05)

sum(final.result$p.v2 > 0.05)

```

### 3.1 White Noise Test


```{r appendix 3.1-1 , cache=FALSE, eval=TRUE}
(fit.arima.monthly.return.no.limitation <- auto.arima(monthly.gold.compound.return, seasonal = FALSE))


Box.test(residuals(fit.arima.monthly.return.no.limitation), 
         lag=10, 
         fitdf=sum(fit.arima.monthly.return.no.limitation$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.monthly.return.no.limitation), 
         lag=20, 
         fitdf=sum(fit.arima.monthly.return.no.limitation$arma[c(1,2)]), type = "Lj")

```

### 3.2  Relationship Between Residuals And Time

```{r appendix 3.2-1 , fig.height=6, fig.width=10, cache=FALSE, eval=TRUE}

plot(residuals(fit.arima.monthly.return.no.limitation), axes = TRUE)
abline(h = 0, col = "red")

```

### 3.3 Relationship Between Residuals And Fitted Value

```{r appendix 3.3-1 , fig.height=6, fig.width=10, eval=TRUE}

plot(as.numeric(residuals(fit.arima.monthly.return.no.limitation)) ~ as.numeric(fitted(fit.arima.monthly.return.no.limitation)))
abline(h = 0, col = "red")


# plot(as.numeric(residuals(fit.arima.monthly.return.no.limitation)) )

```


### 3.4 Normality of Residuals

```{r appendix 3.4-1 , fig.height=6, fig.width=10, eval=TRUE}

qqnorm(residuals(fit.arima.monthly.return.no.limitation))
qqline(residuals(fit.arima.monthly.return.no.limitation))


```

### 3.5 ARCH Effect Test


```{r appendix 3.5-1 , eval=TRUE}

Box.test((residuals(fit.arima.monthly.return.no.limitation))^2, 
         lag=10, 
         fitdf=sum(fit.arima.monthly.return.no.limitation$arma[c(1,2)]), type = "Lj")

Box.test((residuals(fit.arima.monthly.return.no.limitation))^2, 
         lag=20, 
         fitdf=sum(fit.arima.monthly.return.no.limitation$arma[c(1,2)]), type = "Lj")

ArchTest(residuals(fit.arima.monthly.return.no.limitation))



```


## 4 Comparison of pure Arima model with arfima model

### 4.1 ARFIMA Model With Norm Distribution Assumption

```{r appendix 4.1.1, cache=TRUE, eval=TRUE}

result.arfima.norm <- CompareObjectArfimaAccuracy(arg.object = monthly.gold.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.dist = "norm")

```

```{r appendix 4.1.2, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.pure$RMSE - result.arfima.norm$RMSE)

final.result <- cbind(result.pure,
                      result.arfima.norm)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "sigma","RMSE", "p.v",
                            "p2","q2", "RMSE2", "p.v2")

print(final.result)

sum(final.result$RMSE > final.result$RMSE2)

sum(final.result$p.v > 0.05)

sum(final.result$p.v2 > 0.05)

```

### 4.2 ARFIMA Model With Std Distribution Assumption

```{r appendix 4.2.1, cache=TRUE, eval=TRUE}
result.arfima.std <- CompareObjectArfimaAccuracy(arg.object = monthly.gold.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.dist = "std")

```

```{r appendix 4.2.2, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.pure$RMSE - result.arfima.std$RMSE)

final.result <- cbind(result.pure,
                      result.arfima.std)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "sigma","RMSE", "p.v",
                            "p2","q2", "RMSE2", "p.v2")

print(final.result)

sum(final.result$RMSE > final.result$RMSE2)

sum(final.result$p.v > 0.05)

sum(final.result$p.v2 > 0.05)

```

```{r appendix 4.2.3, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.arfima.norm$RMSE - result.arfima.std$RMSE)

final.result <- cbind(result.arfima.norm,
                      result.arfima.std)


final.result <- final.result[, -c(6)]

colnames(final.result) <- c("seq", "p","q", "RMSE", "p.v",
                            "p2","q2", "RMSE2", "p.v2")

print(final.result)

sum(final.result$RMSE > final.result$RMSE2)

sum(final.result$p.v > 0.05)

sum(final.result$p.v2 > 0.05)

```

```{r appendix 4.2.4, cache=TRUE, eval=TRUE}
autoarfima(data = monthly.gold.compound.return, ar.max = 3, ma.max = 2, 
                                criterion = "AIC", method = "full", distribution.model = "std")
```

## 5 Comparison of pure Arima model with VAR model of Gold & dollar

### 5.1 forecast.period = 4

```{r appendix 5.1.1, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}

comparison.period <- 20

forecast.period <- 4

training.set.endpoint <- length(monthly.gold.compound.return) - comparison.period - forecast.period

maxorder <- 5
```

```{r appendix 5.1.2, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}


result.pure <- CompareObjectAccuracy(arg.object = monthly.gold.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 5.1.3, cache=TRUE, eval=TRUE}

gold.dollar <- cbind(monthly.gold.compound.return, monthly.dollar.compound.return)

gold.dollar <- ts(gold.dollar, start = c(1990, 2), frequency = 12)
```

```{r appendix 5.1.4, cache=TRUE, eval=TRUE}
result.GoldDollarVAR <- CompareObjectGoldDollarVARAccuracy(arg.object = gold.dollar,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period)

```


```{r appendix 5.1.5, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.pure$RMSE - result.GoldDollarVAR$RMSE)

final.result <- cbind(result.pure,
                      result.GoldDollarVAR)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "sigma","RMSE", "p.v",
                            "RMSE2", "p.v2", "sigma2")

print(final.result)

sum(final.result$RMSE >= final.result$RMSE2)

sum(final.result$p.v > 0.05)

sum(final.result$p.v2 > 0.05)

```

### 5.2 forecast.period = 1

```{r appendix 5.2.1, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}

comparison.period <- 30

forecast.period <- 1

training.set.endpoint <- length(monthly.gold.compound.return) - comparison.period - forecast.period

maxorder <- 5
```

```{r appendix 5.2.2, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}

result.pure <- CompareObjectAccuracy(arg.object = monthly.gold.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 5.2.3, cache=TRUE, eval=TRUE}
gold.dollar <- cbind(monthly.gold.compound.return, monthly.dollar.compound.return)
gold.dollar <- ts(gold.dollar, start = c(1990, 2), frequency = 12)
```

```{r appendix 5.2.4, cache=TRUE, eval=TRUE}
result.GoldDollarVAR <- CompareObjectGoldDollarVARAccuracy(arg.object = gold.dollar,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period)

```


```{r appendix 5.2.5, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.pure$RMSE - result.GoldDollarVAR$RMSE)

final.result <- cbind(result.pure,
                      result.GoldDollarVAR)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "sigma","RMSE", "p.v",
                            "RMSE2", "p.v2", "sigma2")

print(final.result)

sum(final.result$RMSE >= final.result$RMSE2)

sum(final.result$p.v > 0.05)

sum(final.result$p.v2 > 0.05)

```

```{r appendix 5.2.6, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
final.result.diff <- final.result[final.result$d > 0, ]

t.test(final.result.diff$RMSE - final.result.diff$RMSE2)

```

```{r appendix 5.2.7, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
final.result.no.diff <- final.result[final.result$d == 0, ]

t.test(final.result.no.diff$RMSE - final.result.no.diff$RMSE2)

```



## 6 Comparison of pure Arima model with NNAR model

### 6.1 forecast.period = 4

```{r appendix 6.1.1, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}



comparison.period <- 20

forecast.period <- 4

training.set.endpoint <- length(monthly.gold.compound.return) - comparison.period - forecast.period

maxorder <- 5
```

```{r appendix 6.1.2, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}


result.pure <- CompareObjectAccuracy(arg.object = monthly.gold.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```


```{r appendix 6.1.4, cache=TRUE, eval=TRUE}


result.nnar <- CompareObjectNNARAccuracy(arg.object = monthly.gold.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period)

```


```{r appendix 6.1.5, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.pure$RMSE - result.nnar$RMSE)

final.result <- cbind(result.pure,
                      result.nnar)


final.result <- final.result[, -c(8)]

# colnames(final.result) <- c("seq", "p","d","q", "sigma","RMSE", "p.v",
#                             "RMSE2", "p.v2", "sigma2")

colnames(final.result) <- c("seq", "p","d","q", "sigma","RMSE", "p.v",
                            "p","size","RMSE2")

print(final.result)

sum(final.result$RMSE >= final.result$RMSE2)

sum(final.result$p.v > 0.05)

# sum(final.result$p.v2 > 0.05)

```

### 6.2 forecast.period = 1

```{r appendix 6.2.1, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}

comparison.period <- 30

forecast.period <- 1

training.set.endpoint <- length(monthly.gold.compound.return) - comparison.period - forecast.period

maxorder <- 5
```

```{r appendix 6.2.2, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}

result.pure <- CompareObjectAccuracy(arg.object = monthly.gold.compound.return,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)

result.nnar <- CompareObjectNNARAccuracy(arg.object = monthly.gold.compound.return,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period)

```


```{r appendix 6.2.5, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
t.test(result.pure$RMSE - result.nnar$RMSE)

final.result <- cbind(result.pure,
                      result.nnar)


final.result <- final.result[, -c(8)]

colnames(final.result) <- c("seq", "p","d","q", "sigma","RMSE", "p.v",
                            "p","size","RMSE2")

print(final.result)

sum(final.result$RMSE >= final.result$RMSE2)

sum(final.result$p.v > 0.05)

# sum(final.result$p.v2 > 0.05)

```

```{r appendix 6.2.6, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
final.result.diff <- final.result[final.result$d > 0, ]

t.test(final.result.diff$RMSE - final.result.diff$RMSE2)

```

```{r appendix 6.2.7, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
final.result.no.diff <- final.result[final.result$d == 0, ]

t.test(final.result.no.diff$RMSE - final.result.no.diff$RMSE2)

```

## 7 Forecast using Arima model
```{r appendix 7-1, eval=TRUE}
forecast(fit.arima.monthly.return.no.limitation, h = 1, 
                              level = c(80,95))
```

```{r appendix 7-2, eval=TRUE}
tail(monthly.gold.compound.return)
```




