---
title: "Prediction Of Gold monthly KDJ.K"
author: "Wu Wei"
date: "2017-11-30"
output: html_document
---

```{r library, echo = FALSE}
rm(list = ls())

suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
suppressMessages(library(rugarch))
suppressMessages(library(vars))
suppressMessages(library(urca))
```

```{r source file, echo = FALSE}
setwd("d://MyR//stock//")

source("CompareObjectAccuracy.R")
source("CompareObjectXregAccuracy.R")

source("CompareObjectEstimated2layersXregAccuracy.R")
source("CompareObjectEstimated4layersXregAccuracy.R")

source("CompareObjectNaiveAccuracy.R")
source("CompareObjectZeroDiffAccuracy.R")
source("CompareKDJDEstimatedKDJKXregAccuracy.R")

source("CompareObjectArfimaAccuracy.r")

```



### 3.Analyse for predicting monthly KDJ.K

#### 3.1 Forecast relationship between monthly KDJ.K and other variables
```{r appendix 3.1-1, echo = FALSE, cache=FALSE}
monthly.original.data <- read.csv("goldmonthly.csv")

monthly.close.price <- as.ts(monthly.original.data[,5])
monthly.kdj.k <- as.ts(monthly.original.data[,7])
monthly.kdj.d <- as.ts(monthly.original.data[,8])

###The last 20 values are left as the test set. 

training.monthly.close.price <- head(monthly.close.price, 
                                     length(monthly.close.price) - 20)

training.monthly.kdj.k <- head(monthly.kdj.k, 
                               length(monthly.kdj.k) - 20)

training.monthly.kdj.d <- head(monthly.kdj.d, 
                               length(monthly.kdj.d) - 20)

```


```{r appendix 3.1-2, echo = TRUE, cache=FALSE, eval=TRUE}

reg.lagged.df <- cbind(as.numeric(training.monthly.kdj.d),
                as.numeric(training.monthly.kdj.k - training.monthly.kdj.d),
                as.numeric(training.monthly.close.price),

                ts(c(NA, training.monthly.kdj.d[-length(training.monthly.kdj.d)])),
                ts(c(NA, training.monthly.kdj.k[-length(training.monthly.kdj.k)] -
                             training.monthly.kdj.d[-length(training.monthly.kdj.d)])),
                ts(c(NA, training.monthly.close.price[-length(training.monthly.close.price)])),
                
                
                ts(c(NA, NA, head(training.monthly.kdj.d, length(training.monthly.kdj.d) - 2))),
                ts(c(NA, NA, head(training.monthly.kdj.k, length(training.monthly.kdj.k) - 2) -
                             head(training.monthly.kdj.d, length(training.monthly.kdj.d) - 2))),
                ts(c(NA, NA, head(training.monthly.close.price, length(training.monthly.close.price) - 2))),
                
                ts(c(NA, NA, NA, head(training.monthly.kdj.d, length(training.monthly.kdj.d) - 3))),
                ts(c(NA, NA, NA, head(training.monthly.kdj.k, length(training.monthly.kdj.k) - 3) -
                             head(training.monthly.kdj.d, length(training.monthly.kdj.d) - 3))),
                ts(c(NA, NA, NA, head(training.monthly.close.price, length(training.monthly.close.price) - 3))))
```

```{r appendix 3.1-3, echo = TRUE, cache=TRUE, eval=TRUE}
fit.pure.arima <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                             stepwise = FALSE,
                              approximation = FALSE, max.order = 9)
```

```{r appendix 3.1-4, echo = TRUE, cache=TRUE, eval=TRUE}
fit.2 <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 2],
                    max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.2.5 <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(2,5)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.2.5.8 <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(2,5,8)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.2.5.8.11 <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(2,5,8,11)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)
```

```{r appendix 3.1-5, echo = TRUE, cache=TRUE, eval=TRUE}
fit.1 <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1],
                    max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.1.4 <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(1,4)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.1.4.7 <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(1,4,7)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.1.4.7.10 <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(1,4,7,10)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)
```

```{r appendix 3.1-6, echo = TRUE, cache=TRUE, eval=TRUE}
fit.3 <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 3],
                    max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.3.6 <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(3,6)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.3.6.9 <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(3,6,9)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.3.6.9.12 <- auto.arima(training.monthly.kdj.k[4:length(training.monthly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(3,6,9,12)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

```

```{r appendix 3.1-7, echo = FALSE, cache=FALSE, eval=TRUE}

aicc.name <- c("fit.pure.arima$aicc",
               "fit.2$aicc",
               "fit.2.5$aicc",
               "fit.2.5.8$aicc",
               "fit.2.5.8.11$aicc",
               "fit.1$aicc",
               "fit.1.4$aicc",
               "fit.1.4.7$aicc",
               "fit.1.4.7.10$aicc",
               "fit.3$aicc",
               "fit.3.6$aicc",
               "fit.3.6.9$aicc",
               "fit.3.6.9.12$aicc")

aicc.value <- c(fit.pure.arima$aicc,
                fit.2$aicc,
                fit.2.5$aicc,
                fit.2.5.8$aicc,
                fit.2.5.8.11$aicc,
                fit.1$aicc,
                fit.1.4$aicc,
                fit.1.4.7$aicc,
                fit.1.4.7.10$aicc,
                fit.3$aicc,
                fit.3.6$aicc,
                fit.3.6.9$aicc,
                fit.3.6.9.12$aicc)

aicc.df <- data.frame(name = aicc.name, aicc = aicc.value)

cat("Forecast relationship between monthly KDJ.K and other variables:\n")
print(aicc.df[order(aicc.df$aicc),])

```

#### 3.2 Comparison of forecast accuracy of monthly KDJ.K by monthly KDJ.D

```{r appendix 3.2-2, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}

comparison.period <- 20

forecast.period <- 5

training.set.endpoint <- length(monthly.kdj.k) - comparison.period - forecast.period

maxorder <- 5

result.pure.kdj.k <- CompareObjectAccuracy(arg.object = monthly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)

```

```{r appendix 3.2-3(2), fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}
result.pure.kdj.k.maxorder9 <- CompareObjectAccuracy(arg.object = monthly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = 9)

```


```{r appendix 3.2-3(3), fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
# summary(result.pure.kdj.k.maxorder9$RMSE - result.pure.kdj.k$RMSE)

t.test(result.pure.kdj.k.maxorder9$RMSE - result.pure.kdj.k$RMSE)

sum(result.pure.kdj.k$p.v >= 0.05)

sum(result.pure.kdj.k.maxorder9$p.v >= 0.05)

```


For predicting kdj.k using pure Arima model, the effect of setting max.order to 9 is the same with that of setting max.order to 5.


```{r appendix 3.2-4, fig.height=12, fig.width=10, echo = FALSE, cache=TRUE, eval=TRUE}

reg.lagged.df <- cbind(monthly.kdj.d,
                                  ts(c(NA, monthly.kdj.d[-length(monthly.kdj.d)])))

result.actual.xreg.kdj.k <-
        CompareObjectXregAccuracy(arg.object = monthly.kdj.k,
                                  arg.forecast.period = forecast.period,
                                  arg.training.set.endpoint = training.set.endpoint,
                                  arg.comparison.period = comparison.period,
                                  arg.maxorder = maxorder,
                                  arg.xreg = reg.lagged.df)
```


```{r appendix 3.2-5, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}

result.predicted.2layers.xreg.kdj.k <-
        CompareObjectEstimated2layersXregAccuracy(arg.object = monthly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.maxorder = maxorder,
                                                  arg.reg.variable = monthly.kdj.d)
```

```{r appendix 3.2-5(2), fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}

result.predicted.2layers.xreg.kdj.k.maxorder9 <-
        CompareObjectEstimated2layersXregAccuracy(arg.object = monthly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.maxorder = 9,
                                                  arg.reg.variable = monthly.kdj.d)
```

```{r appendix 3.2-5(3), fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
# summary(result.predicted.2layers.xreg.kdj.k.maxorder9$RMSE - result.predicted.2layers.xreg.kdj.k$RMSE)

t.test(result.predicted.2layers.xreg.kdj.k.maxorder9$RMSE - result.predicted.2layers.xreg.kdj.k$RMSE,
       conf.level = 0.95)

sum(result.predicted.2layers.xreg.kdj.k.maxorder9$p.v >= 0.05)

sum(result.predicted.2layers.xreg.kdj.k$p.v >= 0.05)

```

For predicting kdj.k using dynamic Arima model with estimated kdj.d, the difference between the effect of setting max.order to 9 and that of setting max.order to 5 is not significant.

```{r appendix 3.2-6, fig.height=12, fig.width=10, echo = FALSE, cache=FALSE, eval=TRUE}
final.result.kdj.d <- cbind(result.pure.kdj.k,
                      result.actual.xreg.kdj.k,
                      result.predicted.2layers.xreg.kdj.k)

final.result.kdj.d <- final.result.kdj.d[, -c(5, 8,12, 15,19)]

colnames(final.result.kdj.d) <- c("seq", "p","d","q", "RMSE", "p.v",
                            "p2","d2","q2", "RMSE2", "p.v2",
                            "p3","d3","q3", "RMSE3", "p.v3")

print(final.result.kdj.d)
```

```{r appendix 3.2-7, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
model.name <- c("Accuracy of pure kdj.k Arima",
                   "Accuracy of Arima with actual KDJ.D",
                   "Accuracy of Arima with predicted KDJ.D")

average.rmse <- c(mean(final.result.kdj.d$RMSE),
                    mean(final.result.kdj.d$RMSE2),
                    mean(final.result.kdj.d$RMSE3))

pv.up.0.05 <- c(sum(final.result.kdj.d$p.v >= 0.05),
                sum(final.result.kdj.d$p.v2 >= 0.05),
                sum(final.result.kdj.d$p.v3 >= 0.05))


df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)
```

```{r appendix 3.2-8, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
mean(final.result.kdj.d$RMSE >= final.result.kdj.d$RMSE3)
t.test(final.result.kdj.d$RMSE - final.result.kdj.d$RMSE3)

```

For predicting kdj.k using dynamic Arima model with estimated kdj.d, some chosen ARIMA models is (0,0,0), which means that there is only linear relationship between kdj.k and estimated kdj.d. 


#### 3.3 Comparison of forecast accuracy of monthly KDJ.K by difference of monthly KDJ.K and monthly KDJ.D

```{r appendix 3.3-2, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}

monthly.kdj.kd.diff <- monthly.kdj.k - monthly.kdj.d
reg.lagged.df <- 
        data.frame(cbind(monthly.kdj.kd.diff,
                         ts(c(NA, monthly.kdj.kd.diff[-length(monthly.kdj.kd.diff)])),
                         ts(c(NA, NA, head(monthly.kdj.kd.diff, length(monthly.kdj.kd.diff) - 2))),
                         ts(c(NA, NA, NA, head(monthly.kdj.kd.diff, length(monthly.kdj.kd.diff) - 3)))))
```

```{r appendix 3.3-3, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}
result.actual.xreg.kdj.k <-
        CompareObjectXregAccuracy(arg.object = monthly.kdj.k,
                                  arg.forecast.period = forecast.period,
                                  arg.training.set.endpoint = training.set.endpoint,
                                  arg.comparison.period = comparison.period,
                                  arg.maxorder = maxorder,
                                  arg.xreg = reg.lagged.df)

```

```{r appendix 3.3-4, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}
result.predicted.4layers.xreg.kdj.k <-
        CompareObjectEstimated4layersXregAccuracy(arg.object = monthly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.maxorder = maxorder,
                                                  arg.reg.variable = monthly.kdj.kd.diff)

```

```{r appendix 3.3-4(2), fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}
result.predicted.4layers.xreg.kdj.k.maxorder9 <-
        CompareObjectEstimated4layersXregAccuracy(arg.object = monthly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.maxorder = 9,
                                                  arg.reg.variable = monthly.kdj.kd.diff)

```

```{r appendix 3.3-4(3), fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
# summary(result.predicted.4layers.xreg.kdj.k.maxorder9$RMSE - result.predicted.4layers.xreg.kdj.k$RMSE)

t.test(result.predicted.4layers.xreg.kdj.k.maxorder9$RMSE - result.predicted.4layers.xreg.kdj.k$RMSE)

sum(result.predicted.4layers.xreg.kdj.k.maxorder9$p.v >= 0.05)

sum(result.predicted.4layers.xreg.kdj.k$p.v >= 0.05)

```

For predicting kdj.k using dynamic Arima model with estimated kdj.kd.diff, the difference between the effect of setting max.order to 9 and that of setting max.order to 5 is not significant. 
P value of both models is less than 5% in most situations, which seems that Arima model with estimated kdj.kd.diff is not a good way.


```{r appendix 3.3-5, fig.height=12, fig.width=10, echo = FALSE, cache=FALSE, eval=TRUE}

final.result.kdj.kd.diff <- cbind(result.pure.kdj.k,
                                  result.actual.xreg.kdj.k,
                                  result.predicted.4layers.xreg.kdj.k)



final.result.kdj.kd.diff <- final.result.kdj.kd.diff[, -c(5, 8,12, 15,19)]

colnames(final.result.kdj.kd.diff) <- c("seq", "p","d","q", "RMSE", "p.v",
                                        "p2","d2","q2", "RMSE2", "p.v2",
                                        "p3","d3","q3", "RMSE3", "p.v3")


print(final.result.kdj.kd.diff)

model.name <- c("pure kdj.k Arima",
                   "Arima with actual kdj.kd.diff",
                   "Arima with predicted kdj.kd.diff")

average.rmse <- c(mean(final.result.kdj.kd.diff$RMSE),
                  mean(final.result.kdj.kd.diff$RMSE2),
                  mean(final.result.kdj.kd.diff$RMSE3))

pv.up.0.05 <- c(sum(final.result.kdj.kd.diff$p.v >= 0.05),
                sum(final.result.kdj.kd.diff$p.v2 >= 0.05),
                sum(final.result.kdj.kd.diff$p.v3 >= 0.05))

df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)
```

```{r appendix 3.3-6, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
mean(final.result.kdj.kd.diff$RMSE >= final.result.kdj.kd.diff$RMSE3) 
t.test(final.result.kdj.kd.diff$RMSE - final.result.kdj.kd.diff$RMSE3) 
```

#### 3.4 Comparison of forecast accuracy of monthly KDJ.K by monthly gold price

```{r appendix 3.4-2, fig.height=12, fig.width=10, echo = FALSE, cache=FALSE, eval=TRUE}
reg.lagged.df <- 
        data.frame(cbind(monthly.close.price,
                         ts(c(NA, monthly.close.price[-length(monthly.close.price)]))))
```

```{r appendix 3.4-3, fig.height=12, fig.width=10, echo = FALSE, cache=TRUE, eval=TRUE}
result.actual.xreg.kdj.k <-
        CompareObjectXregAccuracy(arg.object = monthly.kdj.k,
                                  arg.forecast.period = forecast.period,
                                  arg.training.set.endpoint = training.set.endpoint,
                                  arg.comparison.period = comparison.period,
                                  arg.maxorder = maxorder,
                                  arg.xreg = reg.lagged.df)

```

```{r appendix 3.4-4, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}
result.predicted.2layers.xreg.kdj.k <-
        CompareObjectEstimated2layersXregAccuracy(arg.object = monthly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.maxorder = maxorder,
                                                  arg.reg.variable = monthly.close.price)

```

```{r appendix 3.4-4(2), fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}
result.predicted.2layers.xreg.kdj.k.maxorder9 <-
        CompareObjectEstimated2layersXregAccuracy(arg.object = monthly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.maxorder = 9,
                                                  arg.reg.variable = monthly.close.price)

```

```{r appendix 3.4-4(3), fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
# summary(result.predicted.2layers.xreg.kdj.k.maxorder9$RMSE - result.predicted.2layers.xreg.kdj.k$RMSE)

t.test(result.predicted.2layers.xreg.kdj.k.maxorder9$RMSE - result.predicted.2layers.xreg.kdj.k$RMSE)

sum(result.predicted.2layers.xreg.kdj.k.maxorder9$p.v >= 0.05)

sum(result.predicted.2layers.xreg.kdj.k$p.v >= 0.05)

```

For predicting kdj.k using dynamic Arima model with gold price, the difference between the effect of setting max.order to 9 and that of setting max.order to 5 is not significant. 

```{r appendix 3.4-5, fig.height=12, fig.width=10, echo = FALSE, cache=FALSE, eval=TRUE}

final.result.close.price <- cbind(result.pure.kdj.k,
                                  result.actual.xreg.kdj.k,
                                  result.predicted.2layers.xreg.kdj.k)



final.result.close.price <- final.result.close.price[, -c(5, 8,12, 15,19)]

colnames(final.result.close.price) <- c("seq", "p","d","q", "RMSE", "p.v",
                                        "p2","d2","q2", "RMSE2", "p.v2",
                                        "p3","d3","q3", "RMSE3", "p.v3")


print(final.result.close.price)

model.name <- c("pure kdj.k Arima",
                   "Arima with actual close.price",
                   "Arima with predicted close.price")

average.rmse <- c(mean(final.result.close.price$RMSE),
                  mean(final.result.close.price$RMSE2),
                  mean(final.result.close.price$RMSE3))

pv.up.0.05 <- c(sum(final.result.close.price$p.v >= 0.05),
                sum(final.result.close.price$p.v2 >= 0.05),
                sum(final.result.close.price$p.v3 >= 0.05))

df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)
```

```{r appendix 3.4-6, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
mean(final.result.close.price$RMSE >= final.result.close.price$RMSE3) 

t.test(final.result.close.price$RMSE - final.result.close.price$RMSE3) 
```

#### 3.5 Comparison of forecast accuracy of monthly KDJ.K by different factors using predicted value

```{r appendix 3.5, fig.height=5, fig.width=7, echo = FALSE, cache=FALSE, eval=TRUE}

ggplot(,aes(x=factor(c(rep("Pure Arima", length(final.result.kdj.d$RMSE)),
                       rep("KDJ.K", length(final.result.kdj.d$RMSE3)),
                      rep("KDJ.KD.difference", length(final.result.kdj.kd.diff$RMSE3)),
                      rep("gold price", length(final.result.close.price$RMSE3))),
                     levels = c("Pure Arima", 
                                "KDJ.K", 
                                "KDJ.KD.difference", 
                                "gold price")),
           y=c(final.result.kdj.d$RMSE, 
               final.result.kdj.d$RMSE3, 
               final.result.kdj.kd.diff$RMSE3, 
               final.result.close.price$RMSE3))) +
        geom_boxplot() +
        xlab("") +
        ylab("RMSE") +
        ylim(0, 50)

ggplot(,aes(x=factor(c(rep("Pure Arima - KDJ.D", length(final.result.kdj.d$RMSE3)),
                      rep("Pure Arima - KDJ.KD.difference", length(final.result.kdj.kd.diff$RMSE3)),
                      rep("Pure Arima - gold price", length(final.result.close.price$RMSE3))),
                     levels = c("Pure Arima - KDJ.D",
                                "Pure Arima - KDJ.KD.difference",
                                "Pure Arima - gold price")),
           y=c(final.result.kdj.d$RMSE - final.result.kdj.d$RMSE3,
               final.result.kdj.d$RMSE - final.result.kdj.kd.diff$RMSE3,
               final.result.kdj.d$RMSE - final.result.close.price$RMSE3))) +
        geom_boxplot() +
        xlab("") +
        ylab("RMSE difference")+
        ylim(-30, 30)

t.test(final.result.kdj.d$RMSE - final.result.kdj.d$RMSE3)
t.test(final.result.kdj.d$RMSE - final.result.kdj.kd.diff$RMSE3)
t.test(final.result.kdj.d$RMSE - final.result.close.price$RMSE3)


```

It can be concluded that pure Arima model with max.order set to 5 is well for predicting monthly kdj.k.

#### 3.6 Comparison of pure Arima model of monthly kdj.k with naive model

```{r appendix 3.6, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}

result.naive.kdj.k <- CompareObjectNaiveAccuracy(arg.object = monthly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)

t.test(result.pure.kdj.k.maxorder9$RMSE - result.naive.kdj.k$RMSE)

t.test(result.pure.kdj.k$RMSE - result.naive.kdj.k$RMSE)

```

```{r appendix 3.6(2), fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}


final.result.kdj.k <- cbind(result.pure.kdj.k,
                      result.naive.kdj.k)

final.result.kdj.k <- final.result.kdj.k[, -c(5,8,12)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "RMSE", "p.v",
                            "p2","d2","q2", "RMSE2", "p.v2")

print(final.result.kdj.k)

sum(final.result.kdj.k$RMSE > final.result.kdj.k$RMSE2)

sum(final.result.kdj.k$p.v > 0.05)
sum(final.result.kdj.k$p.v2 > 0.05)

```

It can be concluded that hybrid model with Arima model and naive model is not needed for predicting monthly kdj.k.


#### 3.7 Comparison of pure Arima model of monthly kdj.k with Zero Difference model

```{r appendix 3.7, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}

training.set.endpoint.50 <- length(monthly.kdj.d) - 50 - forecast.period

result.zero.diff.kdj.k.50 <- CompareObjectZeroDiffAccuracy(arg.object = monthly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint.50,
                                                 arg.comparison.period = 50,
                                                 arg.maxorder = maxorder)
```


```{r appendix 3.7(1), fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}
result.pure.kdj.k.50 <- CompareObjectAccuracy(arg.object = monthly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint.50,
                                                 arg.comparison.period = 50,
                                                 arg.maxorder = maxorder)


```

```{r appendix 3.7(2), fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}

t.test(result.pure.kdj.k.50$RMSE - result.zero.diff.kdj.k.50$RMSE)


final.result.kdj.k <- cbind(result.pure.kdj.k.50, result.zero.diff.kdj.k.50)

final.result.kdj.k <- final.result.kdj.k[, -c(5,8,12)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "RMSE", "p.v",
                            "p2","d2","q2", "RMSE2", "p.v2")

print(final.result.kdj.k)

mean(final.result.kdj.k$RMSE > final.result.kdj.k$RMSE2)

sum(final.result.kdj.k$p.v >= 0.05)

sum(final.result.kdj.k$p.v2 >= 0.05)

```

It can be concluded that pure Arima model with max.order set to 5 and d set to 0 is well for predicting monthly kdj.k.

#### 3.8 Comparison of pure Arima model of monthly kdj.k with VAR model

```{r appendix 3.8.1, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
source("CompareVARAccuracy.r")
monthly.kdj <- cbind(monthly.kdj.k, monthly.kdj.d)

monthly.kdj <- ts(monthly.kdj, start = c(1990, 1), frequency = 12)
```

```{r appendix 3.8.2, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
result.var.kdj.k <- CompareVARAccuracy(arg.object = monthly.kdj,
                                       arg.forecast.period = forecast.period,
                                       arg.training.set.endpoint = training.set.endpoint,
                                       arg.comparison.period = comparison.period,
                                       arg.comparison.colname = "monthly.kdj.k")
```

```{r appendix 3.8.3, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
t.test(result.pure.kdj.k$RMSE - result.var.kdj.k$RMSE)
mean(result.pure.kdj.k$RMSE > result.var.kdj.k$RMSE)
```

```{r appendix 3.8.4, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
final.result.kdj.k <- cbind(result.pure.kdj.k,
                      result.var.kdj.k)


# final.result <- final.result[, -c(8)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "sigma","RMSE", "p.v","seq2",
                            "RMSE2", "p.v2", "sigma2","max.root","p.order")

print(final.result.kdj.k)
```


```{r appendix 3.8.5, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
model.name <- c("Accuracy of pure kdj.d Arima",
                   "Accuracy of VAR model")

average.rmse <- c(mean(final.result.kdj.k$RMSE),
                    mean(final.result.kdj.k$RMSE2))

pv.up.0.05 <- c(sum(final.result.kdj.k$p.v >= 0.05),
                sum(final.result.kdj.k$p.v2 >= 0.05))


df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)



```


#### 3.9 Comparison of pure Arima model of monthly kdj.K with VECM model

```{r appendix 3.9.1, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
source("CompareVECMAccuracy.r")

result.vecm.kdj.k <- CompareVECMAccuracy(arg.object = monthly.kdj,
                                       arg.forecast.period = forecast.period,
                                       arg.training.set.endpoint = training.set.endpoint,
                                       arg.comparison.period = comparison.period,
                                       arg.comparison.colname = "monthly.kdj.k")
```

```{r appendix 3.9.2, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
t.test(result.pure.kdj.k$RMSE - result.vecm.kdj.k$RMSE)
mean(result.pure.kdj.k$RMSE > result.vecm.kdj.k$RMSE)
```


```{r appendix 3.9.3, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
final.result.kdj.k <- cbind(result.pure.kdj.k,
                      result.vecm.kdj.k)


# final.result <- final.result[, -c(8)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "sigma","RMSE", "p.v","seq2",
                            "RMSE2", "p.v2", "sigma2","max.root","p.order","flag")

print(final.result.kdj.k)
```

```{r appendix 3.9.4, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
model.name <- c("Accuracy of pure kdj.d Arima",
                   "Accuracy of VECM model")

average.rmse <- c(mean(final.result.kdj.k$RMSE),
                    mean(final.result.kdj.k$RMSE2))

pv.up.0.05 <- c(sum(final.result.kdj.k$p.v >= 0.05),
                sum(final.result.kdj.k$p.v2 >= 0.05))


df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)



```


#### 3.10 Comparison of pure Arima model of monthly kdj.K with VAR model and VAR in difference By root

```{r appendix 3.10.1, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
source("CompareVARinDiffByRootAccuracy.r")

result.varindiffbyroot.kdj.k <- CompareVARinDiffByRootAccuracy(arg.object = monthly.kdj,
                                       arg.forecast.period = forecast.period,
                                       arg.training.set.endpoint = training.set.endpoint,
                                       arg.comparison.period = comparison.period,
                                       arg.comparison.colname = "monthly.kdj.k")
```

```{r appendix 3.10.2, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
t.test(result.pure.kdj.k$RMSE - result.varindiffbyroot.kdj.k$RMSE)
mean(result.pure.kdj.k$RMSE > result.varindiffbyroot.kdj.k$RMSE)
```


```{r appendix 3.10.3, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
final.result.kdj.k <- cbind(result.pure.kdj.k,
                      result.varindiffbyroot.kdj.k)


# final.result <- final.result[, -c(8)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "sigma","RMSE", "p.v","seq2",
                            "RMSE2", "p.v2", "sigma2","max.root","p.order","flag")

print(final.result.kdj.k)
```

```{r appendix 3.10.4, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
model.name <- c("pure kdj.d Arima",
                   "VAR/VAR in difference model by root ")

average.rmse <- c(mean(final.result.kdj.k$RMSE),
                    mean(final.result.kdj.k$RMSE2))

pv.up.0.05 <- c(sum(final.result.kdj.k$p.v >= 0.05),
                sum(final.result.kdj.k$p.v2 >= 0.05))


df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)



```

#### 3.11 Comparison of pure Arima model of monthly kdj.K with VAR model and Univariate ARIMA By root

```{r appendix 3.11.1, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
source("CompareVARUARByRootAccuracy.r")

result.varuarbyroot.kdj.k <- CompareVARUARByRootAccuracy(arg.object = monthly.kdj,
                                       arg.forecast.period = forecast.period,
                                       arg.training.set.endpoint = training.set.endpoint,
                                       arg.comparison.period = comparison.period,
                                       arg.comparison.colname = "monthly.kdj.k")
```

```{r appendix 3.11.2, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
t.test(result.pure.kdj.k$RMSE - result.varuarbyroot.kdj.k$RMSE)
mean(result.pure.kdj.k$RMSE > result.varuarbyroot.kdj.k$RMSE)
```


```{r appendix 3.11.3, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
final.result.kdj.k <- cbind(result.pure.kdj.k,
                      result.varuarbyroot.kdj.k)


# final.result <- final.result[, -c(8)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "sigma","RMSE", "p.v","seq2",
                            "RMSE2", "p.v2", "sigma2","max.root","p.order","flag")

print(final.result.kdj.k)
```

```{r appendix 3.11.4, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
model.name <- c("pure kdj.d Arima",
                   "VAR/UAR model by root ")

average.rmse <- c(mean(final.result.kdj.k$RMSE),
                    mean(final.result.kdj.k$RMSE2))

pv.up.0.05 <- c(sum(final.result.kdj.k$p.v >= 0.05),
                sum(final.result.kdj.k$p.v2 >= 0.05))


df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)



```

#### 3.12 Comparison of pure Arima model of monthly kdj.d with VAR in difference model
```{r appendix 3.12.2, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
source("CompareVARInDiffAccuracy.r")

result.varindiff.kdj.k <- CompareVARInDiffAccuracy(arg.object = monthly.kdj,
                                       arg.forecast.period = forecast.period,
                                       arg.training.set.endpoint = training.set.endpoint,
                                       arg.comparison.period = comparison.period,
                                       arg.comparison.colname = "monthly.kdj.k")
```

```{r appendix 3.12.3, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
t.test(result.pure.kdj.k$RMSE - result.varindiff.kdj.k$RMSE)
mean(result.pure.kdj.k$RMSE > result.varindiff.kdj.k$RMSE)
```


```{r appendix 3.12.4, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
final.result.kdj.k <- cbind(result.pure.kdj.k,
                      result.varindiff.kdj.k)



colnames(final.result.kdj.k) <- c("seq", "p","d","q", "sigma","RMSE", "p.v","seq2", 
                            "RMSE2", "p.v2", "sigma2","max.root","p.order")

print(final.result.kdj.k)
```


#### 3.13 Comparison of VAR model and VAR in difference By root model with Zero Difference model

```{r appendix 3.13, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}

result.varindiffbyroot.kdj.k.50 <- CompareVARinDiffByRootAccuracy(arg.object = monthly.kdj,
                                       arg.forecast.period = forecast.period,
                                       arg.training.set.endpoint = training.set.endpoint.50,
                                       arg.comparison.period = 50,
                                       arg.comparison.colname = "monthly.kdj.k")

```



```{r appendix 3.13(2), fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}

t.test(result.varindiffbyroot.kdj.k.50$RMSE - result.zero.diff.kdj.k.50$RMSE)
mean(result.varindiffbyroot.kdj.k.50$RMSE > result.zero.diff.kdj.k.50$RMSE)

final.result.kdj.k <- cbind(result.varindiffbyroot.kdj.k.50, result.zero.diff.kdj.k.50)

final.result.kdj.k <- final.result.kdj.k[, -c(4:6,12)]

colnames(final.result.kdj.k) <- c("seq", "RMSE", "p.v","flag","seq2",
                            "p2","d2","q2", "RMSE2", "p.v2")

print(final.result.kdj.k)


```

```{r appendix 3.13.3, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
model.name <- c("VAR/VAR in difference model by root ",
                   "zero diff Arima")

average.rmse <- c(mean(final.result.kdj.k$RMSE),
                    mean(final.result.kdj.k$RMSE2))

pv.up.0.05 <- c(sum(final.result.kdj.k$p.v >= 0.05),
                sum(final.result.kdj.k$p.v2 >= 0.05))


df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)



```

#### 3.14 Comparison of VECM model with Zero Difference model

```{r appendix 3.14, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}
source("CompareVECMAccuracy.r")
result.vecm.kdj.k.50 <- CompareVECMAccuracy(arg.object = monthly.kdj,
                                       arg.forecast.period = forecast.period,
                                       arg.training.set.endpoint = training.set.endpoint.50,
                                       arg.comparison.period = 50,
                                       arg.comparison.colname = "monthly.kdj.k")
```



```{r appendix 3.14(2), fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}

t.test(result.vecm.kdj.k.50$RMSE - result.zero.diff.kdj.k.50$RMSE)
mean(result.vecm.kdj.k.50$RMSE > result.zero.diff.kdj.k.50$RMSE)

final.result.kdj.k <- cbind(result.vecm.kdj.k.50, result.zero.diff.kdj.k.50)

final.result.kdj.k <- final.result.kdj.k[, -c(4:6,12)]

colnames(final.result.kdj.k) <- c("seq", "RMSE", "p.v","flag","seq2",
                            "p2","d2","q2", "RMSE2", "p.v2")

print(final.result.kdj.k)


```

```{r appendix 3.14.3, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
model.name <- c("VECM",
                   "zero diff Arima")

average.rmse <- c(mean(final.result.kdj.k$RMSE),
                    mean(final.result.kdj.k$RMSE2))

pv.up.0.05 <- c(sum(final.result.kdj.k$p.v >= 0.05),
                sum(final.result.kdj.k$p.v2 >= 0.05))


df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)



```
