---
title: "Prediction Of Gold weekly KDJ.K"
author: "Wu Wei"
date: "2017-12-25"
output: html_document
---

#### 3.0 Data Preparation

```{r library}
rm(list = ls())

suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
suppressMessages(library(vars))
suppressMessages(library(urca))
```

```{r source files}
setwd("d://MyR//stock//")

source("CompareObjectAccuracy.R")
source("CompareObjectXregAccuracy.R")
source("CompareObjectEstimated4layersXregAccuracy.R")
source("CompareObjectEstimated3layersXregAccuracy.R")

source("CompareObjectNaiveAccuracy.R")
source("CompareObjectZeroDiffAccuracy.R")

```


#### 3.1 Forecast relationship between weekly KDJ.K and other variables
```{r appendix 3.1-1, echo = FALSE, cache=FALSE, eval = TRUE}
weekly.original.data <- read.csv("goldweekly.csv")

weekly.close.price <- as.ts(tail(weekly.original.data[,5], 490))
weekly.kdj.k <- as.ts(tail(weekly.original.data[,7], 490))
weekly.kdj.d <- as.ts(tail(weekly.original.data[,8], 490))

weekly.mlcadd <- as.ts(tail(weekly.original.data[,9], 490))
weekly.mlcdec <- as.ts(tail(weekly.original.data[,10], 490))


training.weekly.close.price <- head(weekly.close.price, 470)
training.weekly.kdj.k <- head(weekly.kdj.k, 470)
training.weekly.kdj.d <- head(weekly.kdj.d, 470)

training.weekly.mlcadd <- head(weekly.mlcadd, 470)

training.weekly.mlcdec <- head(weekly.mlcdec, 470)

comparison.period <- 20

forecast.period <- 5

maxorder <- 5
```

```{r appendix 3.2-2, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}
### For lessening caculation, use old value of training.set.endpoint to use old result of some models


training.set.endpoint <- length(weekly.kdj.k) - comparison.period - forecast.period
training.set.endpoint.50 <- length(weekly.kdj.k) - 50 - forecast.period

```



```{r appendix 3.1-2, echo = TRUE, cache=FALSE, eval=TRUE}

reg.lagged.df <- cbind(as.numeric(training.weekly.kdj.d),
                as.numeric(training.weekly.kdj.k - training.weekly.kdj.d),
                as.numeric(training.weekly.close.price),

                ts(c(NA, training.weekly.kdj.d[-length(training.weekly.kdj.d)])),
                ts(c(NA, training.weekly.kdj.k[-length(training.weekly.kdj.k)] -
                             training.weekly.kdj.d[-length(training.weekly.kdj.d)])),
                ts(c(NA, training.weekly.close.price[-length(training.weekly.close.price)])),
                
                
                ts(c(NA, NA, head(training.weekly.kdj.d, length(training.weekly.kdj.d) - 2))),
                ts(c(NA, NA, head(training.weekly.kdj.k, length(training.weekly.kdj.k) - 2) -
                             head(training.weekly.kdj.d, length(training.weekly.kdj.d) - 2))),
                ts(c(NA, NA, head(training.weekly.close.price, length(training.weekly.close.price) - 2))),
                
                ts(c(NA, NA, NA, head(training.weekly.kdj.d, length(training.weekly.kdj.d) - 3))),
                ts(c(NA, NA, NA, head(training.weekly.kdj.k, length(training.weekly.kdj.k) - 3) -
                             head(training.weekly.kdj.d, length(training.weekly.kdj.d) - 3))),
                ts(c(NA, NA, NA, head(training.weekly.close.price, length(training.weekly.close.price) - 3))))
```

```{r appendix 3.1-3, echo = TRUE, cache=TRUE, eval=TRUE}
fit.pure.arima <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                             stepwise = FALSE,
                              approximation = FALSE, max.order = 9)
```

```{r appendix 3.1-4, echo = TRUE, cache=TRUE, eval=TRUE}
fit.2 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 2],
                    max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.2.5 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(2,5)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.2.5.8 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(2,5,8)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.2.5.8.11 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(2,5,8,11)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)
```

```{r appendix 3.1-5, echo = TRUE, cache=TRUE, eval=TRUE}
fit.1 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1],
                    max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.1.4 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(1,4)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.1.4.7 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(1,4,7)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.1.4.7.10 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(1,4,7,10)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)
```

```{r appendix 3.1-6, echo = TRUE, cache=TRUE, eval=TRUE}
fit.3 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 3],
                    max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.3.6 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(3,6)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.3.6.9 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(3,6,9)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.3.6.9.12 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(3,6,9,12)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

```

```{r appendix 3.1-7, echo = FALSE, cache=FALSE, eval=TRUE}

aicc.name <- c("fit.pure.arima$aicc",
               "fit.2$aicc",
               "fit.2.5$aicc",
               "fit.2.5.8$aicc",
               "fit.2.5.8.11$aicc",
               "fit.1$aicc",
               "fit.1.4$aicc",
               "fit.1.4.7$aicc",
               "fit.1.4.7.10$aicc",
               "fit.3$aicc",
               "fit.3.6$aicc",
               "fit.3.6.9$aicc",
               "fit.3.6.9.12$aicc")

aicc.value <- c(fit.pure.arima$aicc,
                fit.2$aicc,
                fit.2.5$aicc,
                fit.2.5.8$aicc,
                fit.2.5.8.11$aicc,
                fit.1$aicc,
                fit.1.4$aicc,
                fit.1.4.7$aicc,
                fit.1.4.7.10$aicc,
                fit.3$aicc,
                fit.3.6$aicc,
                fit.3.6.9$aicc,
                fit.3.6.9.12$aicc)

aicc.df <- data.frame(name = aicc.name, aicc = aicc.value)

cat("Forecast relationship between weekly KDJ.K and other variables:\n")
print(aicc.df[order(aicc.df$aicc),])

```

#### 3.2 Comparison of forecast accuracy of weekly KDJ.K by weekly KDJ.D


```{r appendix 3.2-3, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}
result.pure.kdj.k <- CompareObjectAccuracy(arg.object = weekly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)

```

```{r appendix 3.2-4, fig.height=12, fig.width=10, echo = FALSE, cache=TRUE, eval=TRUE}

reg.lagged.df <- data.frame(cbind(weekly.kdj.d,
                                  ts(c(NA, weekly.kdj.d[-length(weekly.kdj.d)])),
                                  ts(c(NA, NA, head(weekly.kdj.d, length(weekly.kdj.d) - 2))),
                                  ts(c(NA, NA, NA, head(weekly.kdj.d, length(weekly.kdj.d) - 3)))))

result.actual.xreg.kdj.k <-
        CompareObjectXregAccuracy(arg.object = weekly.kdj.k,
                                  arg.forecast.period = forecast.period,
                                  arg.training.set.endpoint = training.set.endpoint,
                                  arg.comparison.period = comparison.period,
                                  arg.maxorder = maxorder,
                                  arg.xreg = reg.lagged.df)
```


```{r appendix 3.2-5, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}

result.predicted.4layers.xreg.kdj.k <-
        CompareObjectEstimated4layersXregAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.maxorder = maxorder,
                                                  arg.reg.variable = weekly.kdj.d)
```


```{r appendix 3.2-6, fig.height=12, fig.width=10, echo = FALSE, cache=FALSE, eval=TRUE}
final.result.kdj.d <- cbind(result.pure.kdj.k,
                      result.actual.xreg.kdj.k,
                      result.predicted.4layers.xreg.kdj.k)[, -c(5, 7, 12, 14, 19,21)]


colnames(final.result.kdj.d) <- c("seq", "p","d","q", "RMSE",
                                  "seq2","p2","d2","q2", "RMSE2",
                                  "seq3","p3","d3","q3", "RMSE3")

print(final.result.kdj.d)
```

```{r appendix 3.2-7, fig.height=12, fig.width=10, echo = FALSE, cache=FALSE, eval=TRUE}
model.name <- c("Accuracy of pure kdj.k Arima",
                   "Accuracy of Arima with actual KDJ.D",
                   "Accuracy of Arima with predicted KDJ.D")

average.rmse <- c(mean(final.result.kdj.d$RMSE),
                    mean(final.result.kdj.d$RMSE2),
                    mean(final.result.kdj.d$RMSE3))

sd.rmse <- c(sd(final.result.kdj.d$RMSE),
                    sd(final.result.kdj.d$RMSE2),
                    sd(final.result.kdj.d$RMSE3))

pv.up.0.05 <- c(sum(result.pure.kdj.k$p.v >= 0.05),
                sum(result.actual.xreg.kdj.k$p.v >= 0.05),
                sum(result.predicted.4layers.xreg.kdj.k$p.v >= 0.05))


df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          sd.rmse = sd.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)

mean(final.result.kdj.d$RMSE > final.result.kdj.d$RMSE3)


```

#### 3.3 Comparison of forecast accuracy of weekly KDJ.K by difference of weekly KDJ.K and weekly KDJ.D

```{r appendix 3.3-2, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}

weekly.kdj.kd.diff <- weekly.kdj.k - weekly.kdj.d

```

```{r appendix 3.3-3, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}

reg.lagged.df <- 
        data.frame(cbind(weekly.kdj.kd.diff,
                         ts(c(NA, weekly.kdj.kd.diff[-length(weekly.kdj.kd.diff)])),
                         ts(c(NA, NA, head(weekly.kdj.kd.diff, length(weekly.kdj.kd.diff) - 2))),
                         ts(c(NA, NA, NA, head(weekly.kdj.kd.diff, length(weekly.kdj.kd.diff) - 3)))))

result.actual.xreg.kdj.k <-
        CompareObjectXregAccuracy(arg.object = weekly.kdj.k,
                                  arg.forecast.period = forecast.period,
                                  arg.training.set.endpoint = training.set.endpoint,
                                  arg.comparison.period = comparison.period,
                                  arg.maxorder = maxorder,
                                  arg.xreg = reg.lagged.df)

```

```{r appendix 3.3-4, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}
result.predicted.4layers.xreg.kdj.k <-
        CompareObjectEstimated4layersXregAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.maxorder = maxorder,
                                                  arg.reg.variable = weekly.kdj.kd.diff)

```


```{r appendix 3.3-5, fig.height=12, fig.width=10, echo = FALSE, cache=FALSE, eval=TRUE}

final.result.kdj.kd.diff <- cbind(result.pure.kdj.k,
                                  result.actual.xreg.kdj.k,
                                  result.predicted.4layers.xreg.kdj.k)[, -c(5, 7, 12, 14, 19,21)]


colnames(final.result.kdj.kd.diff) <- c("seq", "p","d","q", "RMSE",
                                        "seq2","p2","d2","q2", "RMSE2",
                                        "seq3","p3","d3","q3", "RMSE3")

print(final.result.kdj.kd.diff)

model.name <- c("pure kdj.k Arima",
                   "Arima with actual kdj.kd.diff",
                   "Arima with predicted kdj.kd.diff")

average.rmse <- c(mean(final.result.kdj.kd.diff$RMSE),
                  mean(final.result.kdj.kd.diff$RMSE2),
                  mean(final.result.kdj.kd.diff$RMSE3))

sd.rmse <- c(sd(final.result.kdj.kd.diff$RMSE),
               sd(final.result.kdj.kd.diff$RMSE2),
                 sd(final.result.kdj.kd.diff$RMSE3))

pv.up.0.05 <- c(sum(final.result.kdj.kd.diff$p.v >= 0.05),
                sum(final.result.kdj.kd.diff$p.v2 >= 0.05),
                sum(final.result.kdj.kd.diff$p.v3 >= 0.05))

df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          sd.rmse = sd.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)

mean(final.result.kdj.kd.diff$RMSE > final.result.kdj.kd.diff$RMSE3) 

```

#### 3.4 Comparison of forecast accuracy of weekly KDJ.K by weekly gold price

```{r appendix 3.4-2, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}

reg.lagged.df <- 
        data.frame(cbind(weekly.close.price,
                         ts(c(NA, weekly.close.price[-length(weekly.close.price)])),
                         ts(c(NA, NA, head(weekly.close.price, length(weekly.close.price) - 2)))))

```

```{r appendix 3.4-3, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}
result.actual.xreg.kdj.k <-
        CompareObjectXregAccuracy(arg.object = weekly.kdj.k,
                                  arg.forecast.period = forecast.period,
                                  arg.training.set.endpoint = training.set.endpoint,
                                  arg.comparison.period = comparison.period,
                                  arg.maxorder = maxorder,
                                  arg.xreg = reg.lagged.df)

```

```{r appendix 3.4-4, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}
result.predicted.3layers.xreg.kdj.k <-
        CompareObjectEstimated3layersXregAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.maxorder = maxorder,
                                                  arg.reg.variable = weekly.close.price)

```


```{r appendix 3.4-5, fig.height=12, fig.width=10, echo = FALSE, cache=FALSE, eval=TRUE}

final.result.close.price <- cbind(result.pure.kdj.k,
                                  result.actual.xreg.kdj.k,
                                  result.predicted.3layers.xreg.kdj.k)[, -c(5, 7, 12, 14, 19,21)]


colnames(final.result.close.price) <- c("seq", "p","d","q", "RMSE",
                                        "seq2","p2","d2","q2", "RMSE2",
                                        "seq3","p3","d3","q3", "RMSE3")


print(final.result.close.price)

model.name <- c("pure kdj.k Arima",
                   "Arima with actual close.price",
                   "Arima with predicted close.price")

average.rmse <- c(mean(final.result.close.price$RMSE),
                  mean(final.result.close.price$RMSE2),
                  mean(final.result.close.price$RMSE3))

sd.rmse <- c(sd(final.result.close.price$RMSE),
               sd(final.result.close.price$RMSE2),
                 sd(final.result.close.price$RMSE3))


pv.up.0.05 <- c(sum(final.result.close.price$p.v >= 0.05),
                sum(final.result.close.price$p.v2 >= 0.05),
                sum(final.result.close.price$p.v3 >= 0.05))

df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          sd.rmse = sd.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)

mean(final.result.close.price$RMSE > final.result.close.price$RMSE3) 


```


#### 3.6 Comparison of pure Arima model of weekly kdj.k with naive model

```{r appendix 3.6, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}
result.naive.kdj.k <- CompareObjectNaiveAccuracy(arg.object = weekly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)


t.test(result.pure.kdj.k$RMSE - result.naive.kdj.k$RMSE)

```

```{r appendix 3.6(2), fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
final.result.kdj.k <- cbind(result.pure.kdj.k,
                      result.naive.kdj.k)

final.result.kdj.k <- final.result.kdj.k[, -c(5,12)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "RMSE", "p.v",
                                  "seq2","p2","d2","q2", "RMSE2", "p.v2")

print(final.result.kdj.k)

sum(final.result.kdj.k$RMSE > final.result.kdj.k$RMSE2)


```

```{r}
model.name <- c("pure kdj.k Arima",
                   "naive model")

average.rmse <- c(mean(final.result.kdj.k$RMSE),
                  mean(final.result.kdj.k$RMSE2))

sd.rmse <- c(sd(final.result.kdj.k$RMSE),
               sd(final.result.kdj.k$RMSE2))


pv.up.0.05 <- c(sum(final.result.kdj.k$p.v >= 0.05),
                sum(final.result.kdj.k$p.v2 >= 0.05))

df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          sd.rmse = sd.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)

mean(final.result.kdj.k$RMSE > final.result.kdj.k$RMSE2) 
```


It can be concluded that hybrid model with Arima model and naive model is not needed for predicting weekly kdj.d.

#### 3.7 Comparison of pure Arima model of weekly kdj.k with Zero Difference model

```{r appendix 3.7, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}

result.zero.diff.kdj.k.50 <- CompareObjectZeroDiffAccuracy(arg.object = weekly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint.50,
                                                 arg.comparison.period = 50,
                                                 arg.maxorder = maxorder)
```


```{r appendix 3.7(1), fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}
result.pure.kdj.k.50 <- CompareObjectAccuracy(arg.object = weekly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint.50,
                                                 arg.comparison.period = 50,
                                                 arg.maxorder = maxorder)


```

```{r appendix 3.7(2), fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
t.test(result.pure.kdj.k.50$RMSE - result.zero.diff.kdj.k.50$RMSE)

final.result.kdj.k <- cbind(result.pure.kdj.k.50,
                      result.zero.diff.kdj.k.50)[, -c(5,12)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "RMSE", "p.v",
                                  "seq2","p2","d2","q2", "RMSE2", "p.v2")

print(final.result.kdj.k)

sum(final.result.kdj.k$RMSE > final.result.kdj.k$RMSE2)

```

```{r}
model.name <- c("pure kdj.k Arima",
                   "zero diff Arima")

average.rmse <- c(mean(final.result.kdj.k$RMSE),
                  mean(final.result.kdj.k$RMSE2))

sd.rmse <- c(sd(final.result.kdj.k$RMSE),
               sd(final.result.kdj.k$RMSE2))


pv.up.0.05 <- c(sum(final.result.kdj.k$p.v >= 0.05),
                sum(final.result.kdj.k$p.v2 >= 0.05))

df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          sd.rmse = sd.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)

mean(final.result.kdj.k$RMSE > final.result.kdj.k$RMSE2) 
```


It can be concluded that pure Arima model with max.order set to 5 and d set to 0 is well for predicting weekly kdj.k.

#### 3.8 Comparison of Zero Difference model of weekly kdj.k with VAR model

```{r appendix 3.8.1, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
weekly.kdj <- cbind(weekly.kdj.k, weekly.kdj.d)

exogen <- cbind(weekly.mlcadd, weekly.mlcdec)

```


```{r appendix 3.8.4, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
source("CompareVARAccuracy.r")

result.var.kdj.k.50 <- CompareVARAccuracy(arg.object = weekly.kdj,
                                       arg.forecast.period = forecast.period,
                                       arg.training.set.endpoint = training.set.endpoint.50,
                                       arg.comparison.period = 50,
                                       arg.comparison.colname = "weekly.kdj.k")
```

```{r appendix 3.8.5, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}
source("CompareVARwithExogen.r")

result.var.exogen.50 <- CompareVARwithExogen(arg.object = weekly.kdj,
                                       arg.forecast.period = forecast.period,
                                       arg.training.set.endpoint = training.set.endpoint.50,
                                       arg.comparison.period = 50,
                                       arg.comparison.colname = "weekly.kdj.k",
                                       arg.exogen = exogen)
```




```{r appendix 3.8.6, fig.height=5, fig.width=7, echo = TRUE, cache=FALSE, eval=TRUE}

final.result <- cbind(result.zero.diff.kdj.k.50,
                      result.var.kdj.k.50,
                      result.var.exogen.50)[,-c(5,11,17,19)]


colnames(final.result) <- c("seq", "p","d","q", "RMSE","p.v", 
                            "seq2","RMSE2", "p.v2", "root","porder",
                            "seq3","RMSE3", "p.v3", "root3")

print(final.result)

model.name <- c("Zero Diff Arima",
                   "VAR",
                   "VAR with exogen")


average.rmse <- c(mean(final.result$RMSE),
                  mean(final.result$RMSE2),
                  mean(final.result$RMSE3))

sd.rmse <- c(sd(final.result$RMSE),
                  sd(final.result$RMSE2),
             sd(final.result$RMSE3))

pv.up.0.05 <- c(sum(final.result$p.v >= 0.05),
                sum(final.result$p.v2 >= 0.05),
                sum(final.result$p.v3 >= 0.05))


df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          sd.rmse = sd.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)


mean(final.result$RMSE > final.result$RMSE2) 
mean(final.result$RMSE > final.result$RMSE3) 
```

### 3.9 Forecast relationship between weekly kdj.k and mlclvtz

#### 3.9.1 Model Selection

```{r appendix 3.9-1, echo = TRUE, cache=TRUE, eval=TRUE}

reg.lagged.df <- cbind(training.weekly.mlcadd,
                       training.weekly.mlcdec,

                c(NA, training.weekly.mlcadd[-length(training.weekly.mlcadd)]),
                c(NA, training.weekly.mlcdec[-length(training.weekly.mlcdec)]),

                c(NA, NA, head(training.weekly.mlcadd, length(training.weekly.mlcadd) - 2)),
                c(NA, NA, head(training.weekly.mlcdec, length(training.weekly.mlcdec) - 2)),

                c(NA, NA, NA, head(training.weekly.mlcadd, length(training.weekly.mlcadd) - 3)),
                c(NA, NA, NA, head(training.weekly.mlcdec, length(training.weekly.mlcdec) - 3)))
```

```{r appendix 3.9-2, echo = TRUE, cache=TRUE, eval=TRUE}
fit.pure.arima <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)])
fit.zerodiff.arima <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)], d = 0)
```

```{r appendix 3.9-3, echo = TRUE, cache=TRUE, eval=TRUE}
fit.1..2 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1:2])

fit.1..4 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1:4])

fit.1..6 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1:6])

fit.1..8 <- auto.arima(training.weekly.kdj.k[4:length(training.weekly.kdj.k)],
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1:8])
```



```{r appendix 3.9-4, echo = TRUE, cache=FALSE, eval=TRUE}

aicc.name <- c("fit.pure.arima$aicc",
               "fit.zerodiff.arima$aicc",
               "fit.1..2$aicc",
               "fit.1..4$aicc",
               "fit.1..6$aicc",
               "fit.1..8$aicc")

aicc.value <- c(fit.pure.arima$aicc,
                fit.zerodiff.arima$aicc,
                fit.1..2$aicc,
                fit.1..4$aicc,
                fit.1..6$aicc,
                fit.1..8$aicc)

aicc.df <- data.frame(name = aicc.name, aicc = aicc.value)

cat("Forecast relationship between weekly kdj.k and mlclvtz:\n")
print(aicc.df[order(aicc.df$aicc),])

```

#### 3.9.2 Model Comparison between zero diff Arima and  Arima with 1-level mlclvtz 

```{r appendix 3.9.5, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}

reg.lagged.df <- cbind(weekly.mlcadd,weekly.mlcdec)

result.actual.xreg.kdj.k.50 <-
        CompareObjectXregAccuracy(arg.object = weekly.kdj.k,
                                  arg.forecast.period = forecast.period,
                                  arg.training.set.endpoint = training.set.endpoint.50,
                                  arg.comparison.period = 50,
                                  arg.maxorder = maxorder,
                                  arg.xreg = reg.lagged.df)

```

```{r appendix 3.9.6, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}

result.actual.xreg.zero.diff.50 <-
        CompareObjectXregAccuracy(arg.d = 0,
                                  arg.object = weekly.kdj.k,
                                  arg.forecast.period = forecast.period,
                                  arg.training.set.endpoint = training.set.endpoint.50,
                                  arg.comparison.period = 50,
                                  arg.maxorder = maxorder,
                                  arg.xreg = reg.lagged.df)

```

```{r appendix 3.9.7, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
final.result.kdj.k <- cbind(result.zero.diff.kdj.k.50,
                      result.actual.xreg.kdj.k.50,
                      result.actual.xreg.zero.diff.50)

final.result.kdj.k <- final.result.kdj.k[, -c(5, 12, 19)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "RMSE", "p.v",
                            "seq2", "p2","d2","q2", "RMSE2", "p.v2",
                            "seq3", "p3","d3","q3", "RMSE3", "p.v3")


print(final.result.kdj.k)
```

```{r appendix 3.9.8, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
model.name <- c("zero diff Arima",
                   "Arima with mlclvtz",
                   "zero diff Arima with  mlclvtz")

average.rmse <- c(mean(final.result.kdj.k$RMSE),
                    mean(final.result.kdj.k$RMSE2),
                    mean(final.result.kdj.k$RMSE3))

sd.rmse <- c(sd(final.result.kdj.k$RMSE),
               sd(final.result.kdj.k$RMSE2),
                 sd(final.result.kdj.k$RMSE3))

pv.up.0.05 <- c(sum(final.result.kdj.k$p.v >= 0.05),
                sum(final.result.kdj.k$p.v2 >= 0.05),
                sum(final.result.kdj.k$p.v3 >= 0.05))


df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          sd.rmse = sd.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)

mean(final.result.kdj.k$RMSE > final.result.kdj.k$RMSE3)

t.test(final.result.kdj.k$RMSE - final.result.kdj.k$RMSE3)

```


#### 3.9.3 Model Comparison between zero diff Arima and  Arima with 2-level mlclvtz 

```{r appendix 3.9.3.1, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}

reg.lagged.df <- cbind(weekly.mlcadd,
                       weekly.mlcdec,

                       c(NA, weekly.mlcadd[-length(weekly.mlcadd)]),
                       c(NA, weekly.mlcdec[-length(weekly.mlcdec)]))


```

```{r appendix 3.9.3.2, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE, eval=TRUE}

result.actual.xreg.zero.diff.50 <-
        CompareObjectXregAccuracy(arg.d = 0,
                                  arg.object = weekly.kdj.k,
                                  arg.forecast.period = forecast.period,
                                  arg.training.set.endpoint = training.set.endpoint.50,
                                  arg.comparison.period = 50,
                                  arg.maxorder = maxorder,
                                  arg.xreg = reg.lagged.df)

```

```{r appendix 3.9.3.3, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
final.result.kdj.k <- cbind(result.zero.diff.kdj.k.50,
                      result.actual.xreg.zero.diff.50)

final.result.kdj.k <- final.result.kdj.k[, -c(5, 12)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "RMSE", "p.v",
                            "seq2", "p2","d2","q2", "RMSE2", "p.v2")


print(final.result.kdj.k)
```

```{r appendix 3.9.3.4, fig.height=12, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
model.name <- c("zero diff Arima",
                   "zero diff Arima with  2 levels mlclvtz")

average.rmse <- c(mean(final.result.kdj.k$RMSE),
                    mean(final.result.kdj.k$RMSE2))

sd.rmse <- c(sd(final.result.kdj.k$RMSE),
               sd(final.result.kdj.k$RMSE2))

pv.up.0.05 <- c(sum(final.result.kdj.k$p.v >= 0.05),
                sum(final.result.kdj.k$p.v2 >= 0.05))


df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          sd.rmse = sd.rmse,
                          pv.up.0.05 = pv.up.0.05)

print(df.accuracy)

mean(final.result.kdj.k$RMSE > final.result.kdj.k$RMSE2)

t.test(final.result.kdj.k$RMSE - final.result.kdj.k$RMSE2)

```

### 3.10 Comparison of Hybrid model with VAR / VAR in difference By root model and Zero Difference model

```{r appendix 3.10.1, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}
source("ResultZeroDiffARIMA.R")

ls.result.zero.diff.kdj.k.50 <- ResultZeroDiffARIMA(arg.object = weekly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint.50,
                                                 arg.comparison.period = 50,
                                                 arg.maxorder = maxorder)
```

```{r appendix 3.10.2, fig.height=5, fig.width=7, echo = TRUE, cache=TRUE, eval=TRUE}
source("ResultVARinDiffByRoot.R")
ls.result.varindiffbyroot.kdj.k.50 <- ResultVARinDiffByRoot(arg.object = weekly.kdj,
                                       arg.forecast.period = forecast.period,
                                       arg.training.set.endpoint = training.set.endpoint.50,
                                       arg.comparison.period = 50,
                                       arg.comparison.colname = "weekly.kdj.k")
```

```{r appendix 3.10.3, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
fc.result.varindiffbyroot <- ls.result.varindiffbyroot.kdj.k.50$fc.result
test.set.result.varindiffbyroot <- ls.result.varindiffbyroot.kdj.k.50$test.set.result

rmse.varindiffbyroot <- sqrt(rowMeans((fc.result.varindiffbyroot - test.set.result.varindiffbyroot)^2))
```

```{r appendix 3.10.4, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
fc.result.zero.diff <- ls.result.zero.diff.kdj.k.50$fc.result
test.set.result.zero.diff <- ls.result.zero.diff.kdj.k.50$test.set.result

rmse.zero.diff <- sqrt(rowMeans((fc.result.zero.diff - test.set.result.zero.diff)^2))
```

```{r appendix 3.10.5, fig.height=5, fig.width=7, echo = TRUE, eval=TRUE}
fc.result.hybrid <- (fc.result.varindiffbyroot + fc.result.zero.diff) / 2
test.set.result.hybrid <- test.set.result.zero.diff

rmse.hybrid <- sqrt(rowMeans((fc.result.hybrid - test.set.result.hybrid)^2))
```

```{r appendix 3.10.6, fig.height=12, fig.width=10, echo = TRUE, eval=TRUE}
model.name <- c("varindiffbyroot",
                   "zero diff Arima",
                "Hybrid")

average.rmse <- c(mean(rmse.varindiffbyroot),
                    mean(rmse.zero.diff),
                    mean(rmse.hybrid))

sd.rmse <- c(sd(rmse.varindiffbyroot),
                    sd(rmse.zero.diff),
                    sd(rmse.hybrid))


df.accuracy <- data.frame(model = model.name,
                          average.rmse = average.rmse,
                          sd.rmse = sd.rmse)

print(df.accuracy)



```



## Check if the last seq number is same for every test? 



