---
title: "ARIMA Prediction Of Gold--Result"
author: "Wu Wei"
date: "2017-4-2"
output: html_document
---

## Synopsis


```{r library, echo = FALSE}
suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
suppressMessages(library(FinTS))
```

### 1. Forecast result of monthly kdj k/d and monthly gold price

```{r main 1.1, echo = TRUE}
rm(list = ls())

setwd("d://MyR//stock//")
monthly.original.data <- read.csv("goldmonthly.csv")

monthly.close.price <- as.ts(monthly.original.data[,5])
monthly.kdj.k <- as.ts(monthly.original.data[,7])
monthly.kdj.d <- as.ts(monthly.original.data[,8])
```



```{r main 1.2, fig.height=6, fig.width=10, echo = TRUE, cache=TRUE}
source("DrawMonthlyKDJDForecastPlot.R")

DrawMonthlyKDJDForecastPlot(monthly.close.price,
                            monthly.kdj.k,
                            monthly.kdj.d,
                            arg.forecast.period = 5,
                            arg.ylabel.offset = 80,
                            arg.xlim.offset = 80,
                            arg.date = monthly.original.data[, 1])
```

```{r main 1.3, fig.height=6, fig.width=10, echo = TRUE, cache=TRUE}
source("DrawMonthlyPriceForecastPlot.R")

DrawMonthlyPriceForecastPlot(monthly.close.price,
                            arg.forecast.period = 5,
                            arg.xlim.offset = 80,
                            arg.date = monthly.original.data[, 1])
```


It can be seen from monthly KDJ.D that the long-term decreasing trend has stopped, which means that the chance of earning money is not decreasing. It is a neutral signal, which can stimulate money come in mildly. 
        
### 2. Forecast result of Weekly kdj k/d and Weekly gold price

```{r main 2.1, echo = TRUE}
rm(list = ls())

setwd("d://MyR//stock//")
weekly.original.data <- read.csv("goldweekly.csv")

weekly.close.price <- as.ts(weekly.original.data[,5])
weekly.kdj.k <- as.ts(weekly.original.data[,7])
weekly.kdj.d <- as.ts(weekly.original.data[,8])
```



```{r main 2.2, fig.height=6, fig.width=10, echo = TRUE, cache=TRUE}
source("DrawWeeklyKDJDForecastPlot.R")
DrawWeeklyKDJDForecastPlot(weekly.close.price,
                           weekly.kdj.k,
                           weekly.kdj.d,
                           arg.forecast.period = 5,
                           arg.ylabel.offset = 80,
                           arg.xlim.offset = 80,
                           arg.regression.offset = 500,
                           arg.date = weekly.original.data[, 1])

```
        
```{r main 2.3, fig.height=6, fig.width=10, echo = TRUE, cache=TRUE}
source("DrawWeeklyPriceForecastPlot.R")

DrawWeeklyPriceForecastPlot(weekly.close.price,
                            weekly.kdj.k,
                            weekly.kdj.d,
                            arg.forecast.period = 5,
                            arg.ylabel.offset = 80,
                            arg.xlim.offset = 80,
                            arg.regression.offset = 500,
                            arg.date = weekly.original.data[, 1])
```


## 3. Verification for Monthly Models 

```{r Monthly Verification--library, echo = TRUE}
rm(list = ls())

setwd("d://MyR//stock//")
monthly.original.data <- read.csv("goldmonthly.csv")

monthly.close.price <- as.ts(monthly.original.data[,5])
monthly.kdj.k <- as.ts(monthly.original.data[,7])
monthly.kdj.d <- as.ts(monthly.original.data[,8])
```


```{r Monthly Verification--Model, cache=FALSE, eval=TRUE}

(fit.arima.kdj.d <- auto.arima(monthly.kdj.d,
                              max.order = 5,
                              stepwise = FALSE,
                              approximation = FALSE))

(fit.arima.kdj.k <- auto.arima(monthly.kdj.k,
                              max.order = 5,
                              d = 0,
                              stepwise = FALSE,
                              approximation = FALSE))

(fit.arima.price <- auto.arima(monthly.close.price, 
                        stepwise = FALSE, 
                        approximation = FALSE,
                        max.order = 9))   ### if p value < 0.05, set to 9

```


### 3.1 White Noise Test


```{r Monthly Verification--White Noise Test, cache=FALSE, eval=TRUE}

Box.test(residuals(fit.arima.kdj.d), lag=10, fitdf=sum(fit.arima.kdj.d$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.kdj.k), lag=10, fitdf=sum(fit.arima.kdj.k$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.price), lag=10, fitdf=sum(fit.arima.price$arma[c(1,2)]), type = "Lj")

```

### 3.2  Relationship Between Residuals And Time

```{r main 3.2, fig.height=6, fig.width=10, cache=FALSE, eval=TRUE}

plot(residuals(fit.arima.kdj.d), axes = TRUE, main = "Arima( Monthly KDJ.D )")
abline(h = 0, col = "red")

plot(residuals(fit.arima.kdj.k), axes = TRUE, main = "Arima( Monthly KDJ.K )")
abline(h = 0, col = "red")

plot(residuals(fit.arima.price), axes = TRUE, main = "Arima( Monthly Price )")
abline(h = 0, col = "red")
```

### 3.3 Relationship Between Residuals And Fitted Value

```{r main 3.3, fig.height=6, fig.width=10, eval=TRUE}

plot(as.numeric(residuals(fit.arima.kdj.d)) ~ as.numeric(fitted(fit.arima.kdj.d)),
     main = "Arima( Monthly KDJ.D )")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.arima.kdj.k)) ~ as.numeric(fitted(fit.arima.kdj.k)),
     main = "Arima( Monthly KDJ.K )")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.arima.price)) ~ as.numeric(fitted(fit.arima.price)),
     main = "Arima( Monthly Price )")
abline(h = 0, col = "red")

```


### 3.4 Normality of Residuals

```{r Monthly Verification--Normality of Residuals, fig.height=6, fig.width=10, eval=TRUE}

qqnorm(residuals(fit.arima.kdj.d), main = "Arima( Monthly KDJ.D )")
qqline(residuals(fit.arima.kdj.d))

qqnorm(residuals(fit.arima.kdj.k), main = "Arima( Monthly KDJ.K )")
qqline(residuals(fit.arima.kdj.k))

qqnorm(residuals(fit.arima.price), main = "Arima( Monthly Price )")
qqline(residuals(fit.arima.price))

```

### 3.5 ARCH Effect Test


```{r Monthly Verification 3.5, eval=TRUE}

Box.test((residuals(fit.arima.kdj.d))^2, lag=10, fitdf=sum(fit.arima.kdj.d$arma[c(1,2)]), type = "Lj")
ArchTest(residuals(fit.arima.kdj.d))

Box.test((residuals(fit.arima.kdj.k))^2, lag=10, fitdf=sum(fit.arima.kdj.k$arma[c(1,2)]), type = "Lj")
ArchTest(residuals(fit.arima.kdj.k))

Box.test((residuals(fit.arima.price))^2, lag=10, fitdf=sum(fit.arima.price$arma[c(1,2)]), type = "Lj")
ArchTest(residuals(fit.arima.price))


```

## 4. Verification for Weekly Models 

```{r Weekly Verification--library, echo = TRUE}
rm(list = ls())

setwd("d://MyR//stock//")
weekly.original.data <- read.csv("goldweekly.csv")

weekly.close.price <- as.ts(weekly.original.data[,5])
weekly.kdj.k <- as.ts(weekly.original.data[,7])
weekly.kdj.d <- as.ts(weekly.original.data[,8])
```


```{r weekly Verification--Model, cache=FALSE, eval=TRUE}

kdj.d.data <- window(weekly.kdj.d, start = length(weekly.kdj.d) - 500)
kdj.k.data <- window(weekly.kdj.k, start = length(weekly.kdj.k) - 500)
close.price.data <- window(weekly.close.price, 
                           start = length(weekly.close.price) - 500)

fit.arima.kdj.d <- auto.arima(kdj.d.data,
                              max.order = 5,
                              d = 0,
                              stepwise = FALSE,
                              approximation = FALSE)

fit.arima.kdj.k <- auto.arima(kdj.k.data,
                              max.order = 5,
                              d = 0,
                              stepwise = FALSE,
                              approximation = FALSE)

fit.arima.price <- auto.arima(close.price.data, 
                        stepwise = FALSE, 
                        approximation = FALSE,
                        max.order = 5)

```


### 4.1 White Noise Test


```{r 4.1, cache=FALSE, eval=TRUE}

Box.test(residuals(fit.arima.kdj.d), lag=10, fitdf=sum(fit.arima.kdj.d$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.kdj.k), lag=10, fitdf=sum(fit.arima.kdj.k$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.price), lag=10, fitdf=sum(fit.arima.price$arma[c(1,2)]), type = "Lj")

```

### 4.2  Relationship Between Residuals And Time

```{r main 4.2, fig.height=6, fig.width=10, cache=FALSE, eval=TRUE}

plot(residuals(fit.arima.kdj.d), axes = TRUE, main = "Arima( Weekly KDJ.D )")
abline(h = 0, col = "red")

plot(residuals(fit.arima.kdj.k), axes = TRUE, main = "Arima( Weekly KDJ.K )")
abline(h = 0, col = "red")

plot(residuals(fit.arima.price), axes = TRUE, main = "Arima( Weekly Price )")
abline(h = 0, col = "red")
```

### 4.3 Relationship Between Residuals And Fitted Value

```{r main 4.3, fig.height=6, fig.width=10, eval=TRUE}

plot(as.numeric(residuals(fit.arima.kdj.d)) ~ as.numeric(fitted(fit.arima.kdj.d)),
     main = "Arima( Weekly KDJ.D )")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.arima.kdj.k)) ~ as.numeric(fitted(fit.arima.kdj.k)),
     main = "Arima( Weekly KDJ.K )")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.arima.price)) ~ as.numeric(fitted(fit.arima.price)),
     main = "Arima( Weekly Price )")
abline(h = 0, col = "red")

```


### 4.4 Normality of Residuals

```{r main 4.4, fig.height=6, fig.width=10, eval=TRUE}

qqnorm(residuals(fit.arima.kdj.d), main = "Arima( Weekly KDJ.D )")
qqline(residuals(fit.arima.kdj.d))

qqnorm(residuals(fit.arima.kdj.k), main = "Arima( Weekly KDJ.K )")
qqline(residuals(fit.arima.kdj.k))

qqnorm(residuals(fit.arima.price), main = "Arima( Weekly Price )")
qqline(residuals(fit.arima.price))

```

### 4.5 ARCH Effect Test


```{r main 4.5, eval=TRUE}

Box.test((residuals(fit.arima.kdj.d))^2, lag=10, fitdf=sum(fit.arima.kdj.d$arma[c(1,2)]), type = "Lj")
ArchTest(residuals(fit.arima.kdj.d))

Box.test((residuals(fit.arima.kdj.k))^2, lag=10, fitdf=sum(fit.arima.kdj.k$arma[c(1,2)]), type = "Lj")
ArchTest(residuals(fit.arima.kdj.k))

Box.test((residuals(fit.arima.price))^2, lag=10, fitdf=sum(fit.arima.price$arma[c(1,2)]), type = "Lj")
ArchTest(residuals(fit.arima.price))


```
