---
title: "ARIMA Prediction Of Gold--Result"
author: "Wu Wei"
date: "2017-2-13"
output: html_document
---

## Synopsis


```{r library, echo = FALSE}
suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
```

### 1. Forecast result of monthly kdj.d and monthly gold price

```{r main 1.1, echo = TRUE}
rm(list = ls())

setwd("d://MyR//stock//")
monthly.original.data <- read.csv("goldmonthly.csv")

monthly.close.price <- as.ts(monthly.original.data[,5])
monthly.kdj.k <- as.ts(monthly.original.data[,7])
monthly.kdj.d <- as.ts(monthly.original.data[,8])
```



```{r main 1.2, fig.height=6, fig.width=10, echo = TRUE, cache=FALSE}
source("DrawMonthlyKDJDForecastPlot.R")

DrawMonthlyKDJDForecastPlot(monthly.close.price,
                            monthly.kdj.k,
                            monthly.kdj.d,
                            arg.forecast.period = 5,
                            arg.ylabel.offset = 80,
                            arg.xlim.offset = 80,
                            arg.date = monthly.original.data[, 1])
```

```{r main 1.3, fig.height=6, fig.width=10, echo = TRUE, cache=TRUE}
source("DrawMonthlyPriceForecastPlot.R")

DrawMonthlyPriceForecastPlot(monthly.close.price,
                            monthly.kdj.k,
                            monthly.kdj.d,
                            arg.forecast.period = 5,
                            arg.ylabel.offset = 80,
                            arg.xlim.offset = 80,
                            arg.date = monthly.original.data[, 1])
```


It can be seen from monthly KDJ.D that the long-term decreasing trend has stopped, which means that the chance of earning money is not decreasing. It is a neutral signal, which can stimulate money come in mildly. 
        
### Forecast result of Weekly kdj.d and Weekly gold price

```{r, echo = TRUE}
rm(list = ls())

setwd("d://MyR//stock//")
weekly.original.data <- read.csv("goldweekly.csv")

weekly.close.price <- as.ts(weekly.original.data[,5])
weekly.kdj.k <- as.ts(weekly.original.data[,7])
weekly.kdj.d <- as.ts(weekly.original.data[,8])
```



```{r, fig.height=12, fig.width=10, echo = TRUE, cache=TRUE}
# source("DrawWeeklyKDJDForecastPlot.R")
# DrawWeeklyKDJDForecastPlot(weekly.close.price,
#                            weekly.kdj.k,
#                            weekly.kdj.d,
#                            arg.forecast.period = 5,
#                            arg.ylabel.offset = 80,
#                            arg.xlim.offset = 80,
#                            arg.regression.offset = 500,
#                            arg.date = weekly.original.data[, 1])

```
        

## 3. Verification for Monthly Models 

```{r Monthly Verification--library, echo = TRUE}
rm(list = ls())

setwd("d://MyR//stock//")
monthly.original.data <- read.csv("goldmonthly.csv")

monthly.close.price <- as.ts(monthly.original.data[,5])
monthly.kdj.k <- as.ts(monthly.original.data[,7])
monthly.kdj.d <- as.ts(monthly.original.data[,8])
```


```{r Monthly Verification--Model, cache=FALSE}

fit.arima.kdj.d <- auto.arima(monthly.kdj.d,
                              max.order = 5,
                              stepwise = FALSE,
                              approximation = FALSE)

fit.arima.kdj.k <- auto.arima(monthly.kdj.k,
                              max.order = 5,
                              d = 0,
                              stepwise = FALSE,
                              approximation = FALSE)

fit.arima.price <- auto.arima(monthly.close.price, 
                        stepwise = FALSE, 
                        approximation = FALSE,
                        max.order = 5)

```


### 3.1 White Noise Test


```{r Monthly Verification--White Noise Test, cache=FALSE}

Box.test(residuals(fit.arima.kdj.d), lag=10, fitdf=sum(fit.arima.kdj.d$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.kdj.k), lag=10, fitdf=sum(fit.arima.kdj.k$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.price), lag=10, fitdf=sum(fit.arima.price$arma[c(1,2)]), type = "Lj")

```

### 3.2  Relationship Between Residuals And Time

```{r Monthly Verification--Relationship Between Residuals And Time, fig.height=6, fig.width=10, cache=FALSE}

plot(residuals(fit.arima.kdj.d), axes = TRUE, main = "Arima( Monthly KDJ.D )")
abline(h = 0, col = "red")

plot(residuals(fit.arima.kdj.k), axes = TRUE, main = "Arima( Monthly KDJ.K )")
abline(h = 0, col = "red")

plot(residuals(fit.arima.price), axes = TRUE, main = "Arima( Monthly Price )")
abline(h = 0, col = "red")
```

### 3.3 Relationship Between Residuals And Fitted Value

```{r Monthly Verification--Relationship Between Residuals And Fitted Value, fig.height=6, fig.width=10}

plot(as.numeric(residuals(fit.arima.kdj.d)) ~ as.numeric(fitted(fit.arima.kdj.d)),
     main = "Arima( Monthly KDJ.D )")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.arima.kdj.k)) ~ as.numeric(fitted(fit.arima.kdj.k)),
     main = "Arima( Monthly KDJ.K )")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.arima.price)) ~ as.numeric(fitted(fit.arima.price)),
     main = "Arima( Monthly Price )")
abline(h = 0, col = "red")

```


### 3.4 Normality of Residuals

```{r Monthly Verification--Normality of Residuals, fig.height=6, fig.width=10}

qqnorm(residuals(fit.arima.kdj.d), main = "Arima( Monthly KDJ.D )")
qqline(residuals(fit.arima.kdj.d))

qqnorm(residuals(fit.arima.kdj.k), main = "Arima( Monthly KDJ.K )")
qqline(residuals(fit.arima.kdj.k))

qqnorm(residuals(fit.arima.price), main = "Arima( Monthly Price )")
qqline(residuals(fit.arima.price))

```

### 3.5 ARCH Effect Test


```{r Monthly Verification 3.5}

Box.test((residuals(fit.arima.kdj.d))^2, lag=10, fitdf=sum(fit.arima.kdj.d$arma[c(1,2)]), type = "Lj")

Box.test((residuals(fit.arima.kdj.k))^2, lag=10, fitdf=sum(fit.arima.kdj.k$arma[c(1,2)]), type = "Lj")

Box.test((residuals(fit.arima.price))^2, lag=10, fitdf=sum(fit.arima.price$arma[c(1,2)]), type = "Lj")

```
