---
title: "ARIMA Prediction Of Stock 999999"
author: "Wu Wei"
date: "2017-1-4"
output: html_document
---

## Synopsis


## Pure Arima Modelling
### Library input & Data Input
```{r}
rm(list = ls())


suppressMessages(library(forecast))
# suppressMessages(library(sandwich))
# suppressMessages(library(lmtest))

setwd("d://MyR//stock//")
original.data <- read.csv("goldweekly.csv")
# (original.data)

close.price <- as.ts(original.data[,5])
# volume <- as.ts(original.data[,6])
kdj.k <- as.ts(original.data[,7])
kdj.d <- as.ts(original.data[,8])

training.set.close.price <- ts(window(close.price, start = 1500, end = 1799), start = 1)
test.set.close.price <- ts(window(close.price, start = 1800, end = 1900), start = 301)


training.set.kdj.k <- ts(window(kdj.k, start = 1500, end = 1799), start = 1)
test.set.kdj.k <- ts(window(kdj.k, start = 1800, end = 1900), start = 301)

training.set.kdj.d <- ts(window(kdj.d, start = 1500, end = 1799), start = 1)
test.set.kdj.d <- ts(window(kdj.d, start = 1800, end = 1900), start = 301)

```


### Exploratory Data Analysis
```{r, fig.height=8, fig.width=10}
# dev.off()
# par(mfrow = c(2,1))

y.lower.limit <- signif(min(training.set.close.price), digits = 2) - 10
y.upper.limit <- signif(max(training.set.close.price), digits = 2) + 10

plot(training.set.close.price, axes = FALSE, main = "gold price", xlab = "",
     ylim = c(y.lower.limit, y.upper.limit))
axis(1, 
     at = seq(tsp(training.set.close.price)[1], tsp(training.set.close.price)[2], 20), 
      labels = FALSE)

text(seq(tsp(training.set.close.price)[1], tsp(training.set.close.price)[2], 20), 
     par("usr")[3] - 40, 
     labels = original.data[seq(tsp(training.set.close.price)[1], 
                                tsp(training.set.close.price)[2], 20), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2, at = seq(y.lower.limit, y.upper.limit, length.out = 5),
    labels = seq(y.lower.limit, y.upper.limit, length.out = 5), las = 1) 
               
box()

abline(v = seq(tsp(training.set.close.price)[1], tsp(training.set.close.price)[2], 20), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(y.lower.limit, y.upper.limit, length.out = 5), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

#########

# y.lower.limit <- signif(min(training.set.volume), digits = 1) - 2000000
# y.upper.limit <- signif(max(training.set.volume), digits = 1) + 2000000
# 
# plot(training.set.volume, axes = FALSE, main = "volume of 999999", ylab = "volume(w)", xlab = "")
# axis(1, 
#      at = seq(tsp(training.set.volume)[1], tsp(training.set.volume)[2], 10), 
#       labels = FALSE)
# 
# text(seq(tsp(training.set.volume)[1], tsp(training.set.volume)[2], 10), 
#      par("usr")[3] - 4000000, 
#      labels = original.data[seq(tsp(training.set.volume)[1], 
#                                 tsp(training.set.volume)[2], 10), 1], 
#      srt = 45, 
#      pos = 1, 
#      xpd = TRUE)
# 
# axis(2, at = seq(y.lower.limit, y.upper.limit, 4000000),
#     labels = seq(y.lower.limit, y.upper.limit, 4000000) / 10000, las = 1)  
#                
# box()
# 
# abline(v = seq(tsp(training.set.volume)[1], tsp(training.set.volume)[2], 10), 
#        col = "springgreen4", 
#        lty = "dashed",
#        lwd = par("lwd"))
# 
# abline(h = seq(y.lower.limit, y.upper.limit, 4000000), 
#        col = "springgreen4", 
#        lty = "dashed",
#        lwd = par("lwd"))


```

```{r, fig.height=9, fig.width=10}

tsdisplay(training.set.close.price)
```

```{r}

ndiffs(training.set.close.price)
nsdiffs(training.set.close.price)
```

```{r}
close.price <- ts(close.price[-length(close.price)])

BoxCox.lambda(close.price)
BoxCox.lambda(close.price, method = "loglik")
par(mfrow=c(1,2))
plot(close.price)
plot(BoxCox(close.price, 0))

hist(close.price)
hist(BoxCox(close.price, 0))

BoxCox.lambda(training.set.close.price)

BoxCox.lambda(training.set.close.price, method = "guerrero")

BoxCox.lambda(training.set.close.price, method = "loglik")

par(mfrow=c(1,3))

plot(training.set.close.price)
plot(BoxCox(training.set.close.price, -0.5))
plot(BoxCox(training.set.close.price, 0))

hist(training.set.close.price)
hist(BoxCox(training.set.close.price, -0.5))
hist(BoxCox(training.set.close.price, 0))


BoxCox.lambda(kdj.d)
par(mfrow=c(2,1))

plot(kdj.d)
plot(BoxCox(kdj.d, 0.9))


BoxCox.lambda(kdj.k)
```

```{r, fig.height=9, fig.width=10}

# tsdisplay(training.set.volume)
```

```{r}

# ndiffs(training.set.volume)

```


### Modelling for close.price


```{r, fig.height=9, fig.width=10}

tsdisplay(diff(training.set.close.price))
```


```{r, fig.height=8, fig.width=10}

(fit.010.close.price <- Arima(training.set.close.price, order = c(1,1,0), include.drift = FALSE))

tsdisplay(residuals(fit.010.close.price))
```

```{r}

Box.test(residuals(fit.010.close.price), lag=10, fitdf=0)
Box.test(residuals(fit.010.close.price), lag=10, fitdf=0, type = "Lj")

```



```{r}
name.aicc <- c("Arima(training.set.close.price, order = c(0,1,0))$aicc",
               "Arima(training.set.close.price, order = c(0,1,1))$aicc",
               "Arima(training.set.close.price, order = c(0,1,2))$aicc",
               "Arima(training.set.close.price, order = c(0,1,3))$aicc",
               
               "Arima(training.set.close.price, order = c(1,1,0))$aicc",
               "Arima(training.set.close.price, order = c(1,1,1))$aicc",
               "Arima(training.set.close.price, order = c(1,1,2))$aicc",
               "Arima(training.set.close.price, order = c(1,1,3))$aicc",
               
               "Arima(training.set.close.price, order = c(2,1,0))$aicc",
               "Arima(training.set.close.price, order = c(2,1,1))$aicc",
               "Arima(training.set.close.price, order = c(2,1,2))$aicc",
               "Arima(training.set.close.price, order = c(2,1,3))$aicc",

               "Arima(training.set.close.price, order = c(3,1,0))$aicc",
               "Arima(training.set.close.price, order = c(3,1,1))$aicc",
               "Arima(training.set.close.price, order = c(3,1,2))$aicc",
               "Arima(training.set.close.price, order = c(3,1,3))$aicc",
               
               "Arima(training.set.close.price, order = c(0,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.close.price, order = c(0,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.close.price, order = c(0,1,2), include.drift = TRUE)$aicc",
               "Arima(training.set.close.price, order = c(0,1,3), include.drift = TRUE)$aicc",
               
               "Arima(training.set.close.price, order = c(1,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.close.price, order = c(1,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.close.price, order = c(1,1,2), include.drift = TRUE)$aicc",
               "Arima(training.set.close.price, order = c(1,1,3), include.drift = TRUE)$aicc",
               
               "Arima(training.set.close.price, order = c(2,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.close.price, order = c(2,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.close.price, order = c(2,1,2), include.drift = TRUE)$aicc",
               "Arima(training.set.close.price, order = c(2,1,3), include.drift = TRUE)$aicc",

               "Arima(training.set.close.price, order = c(3,1,0), include.drift = TRUE)$aicc",
               "Arima(training.set.close.price, order = c(3,1,1), include.drift = TRUE)$aicc",
               "Arima(training.set.close.price, order = c(3,1,2), include.drift = TRUE)$aicc",
               "Arima(training.set.close.price, order = c(3,1,3), include.drift = TRUE)$aicc"
               
             
)

aicc <- unlist(lapply(lapply(name.aicc, parse, file = "", n = NULL), eval))

name <-  substr(name.aicc, 1, nchar(name.aicc) - 5)

df <- data.frame(name = sub("training.set","",name), 
                 aicc = round(aicc, digits = 3))

(df[order(df$aicc),])

```

Arima(2,1,2) is preferred.


```{r}

(fit.close.price <- auto.arima(training.set.close.price, stepwise = FALSE, 
                              approximation = FALSE, max.order = 9))

(fit.kdj.d <- auto.arima(training.set.kdj.d, stepwise = FALSE, 
                              approximation = FALSE, max.order = 9))

(fit.close.price.boxcox <- auto.arima(training.set.close.price, stepwise = FALSE, 
                              approximation = FALSE, lambda = -0.5, max.order = 9))

(fit.close.price.boxcox.0 <- auto.arima(training.set.close.price, stepwise = FALSE, 
                              approximation = FALSE, lambda = 0, max.order = 9))

```

Arima(2,1,2) is also selected by auto method.

```{r, fig.height=8, fig.width=10}

(fit.212.close.price <- Arima(training.set.close.price, order = c(2,1,2)))

tsdisplay(residuals(fit.212.close.price))
```


### White Noise Test


```{r}

Box.test(residuals(fit.212.close.price), lag=10, fitdf=4)
Box.test(residuals(fit.212.close.price), lag=10, fitdf=4, type = "Lj")


Box.test(residuals(fit.close.price), lag=10, fitdf=6)
Box.test(residuals(fit.close.price), lag=10, fitdf=6, type = "Lj")

Box.test(residuals(fit.kdj.d), lag=10, fitdf=4)
Box.test(residuals(fit.kdj.d), lag=10, fitdf=4, type = "Lj")



Box.test(residuals(fit.close.price.boxcox), lag=10, fitdf=6)
Box.test(residuals(fit.close.price.boxcox), lag=10, fitdf=6, type = "Lj")

Box.test(residuals(fit.close.price.boxcox.0), lag=10, fitdf=6)
Box.test(residuals(fit.close.price.boxcox.0), lag=10, fitdf=6, type = "Lj")
```

### Relationship Between Residuals And Time

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,2))

# plot(residuals(fit.212.close.price), axes = TRUE, main = "Arima(2,1,2)")
# abline(h = 0, col = "red")
# axis(1, 
#      at = seq(tsp(training.set.close.price)[1], tsp(training.set.close.price)[2], 5), 
#      labels = original.data[seq(tsp(training.set.close.price)[1], 
#                                 tsp(training.set.close.price)[2], 5), 1])
# axis(2)
# box()

plot(residuals(fit.close.price), axes = TRUE, main = "Arima(no boxcox)")
abline(h = 0, col = "red")

plot(residuals(fit.close.price.boxcox), axes = TRUE, main = "Arima(with boxcox)")
abline(h = 0, col = "red")

```

### Relationship Between Residuals And Fitted Value

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,2))

# plot(as.numeric(residuals(fit.212.close.price)) ~ as.numeric(fitted(fit.212.close.price)), 
#      main = "Arima(2,1,2)")
# abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.close.price)) ~ as.numeric(fitted(fit.close.price)),
     main = "Arima(no boxcox)")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.close.price.boxcox)) ~ as.numeric(fitted(fit.close.price.boxcox)),
     main = "Arima(boxcox)")
abline(h = 0, col = "red")

```

There is no obvious heteroscedasticity.


### Normality of  Residuals

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,2))

# qqnorm(residuals(fit.212.close.price), main = "Arima(2,1,2)")
# qqline(residuals(fit.212.close.price))

qqnorm(residuals(fit.close.price), main = "Arima(no boxcox)")
qqline(residuals(fit.close.price))

qqnorm(residuals(fit.close.price.boxcox), main = "Arima(boxcox)")
qqline(residuals(fit.close.price.boxcox))

```

Residuals conform to normality.

## Comparison of accuracy of 2 Models 

```{r}
fc.close.price <- forecast(fit.close.price, h = 5, #length(test.set.close.price), 
                              level = c(80,95))

fc.close.price.boxcox <- forecast(fit.close.price.boxcox, h = 5, #length(test.set.close.price), 
                              level = c(80,95))

fc.close.price.boxcox.07 <- forecast(fit.close.price.boxcox.07, h = 5, # length(test.set.close.price), 
                              level = c(80,95))

df.test.set <- rbind(accuracy(fc.close.price, head(test.set.close.price,5))[2,],
            accuracy(fc.close.price.boxcox, head(test.set.close.price,5))[2,],
            accuracy(fc.close.price.boxcox.07, head(test.set.close.price,5))[2,])

row.names(df.test.set) <- c("Arima(no boxcox)","Arima(boxcox)","Arima(boxcox.07)")
print(round(df.test.set, 2))



```

## Comparison of PI of 2 Models 
```{r}
arima.pi.no.boxcox <- fc.close.price$upper[,2] - fc.close.price$lower[,2]
arima.pi.boxcox <- fc.close.price.boxcox$upper[,2] - fc.close.price.boxcox$lower[,2]

cbind(arima.pi.no.boxcox, arima.pi.boxcox)

# df.test.set <- rbind(accuracy(fc.arima212.close.price, test.set.close.price)[2,],
#             accuracy(fc.arima.kdj, test.set.close.price)[2,])
# 
# row.names(df.test.set) <- c("Pure Arima","Reg Arima")
# print(round(df.test.set, 3))



```



### Comparison between actual value and forecast result 

```{r, fig.height=9, fig.width=10}
par(mfrow = c(1,1))
fc.arima212.close.price <- forecast(fit.212.close.price, h = length(test.set.close.price), 
                              level = c(80,95))

y.upper.limit <- signif(max(c(test.set.close.price,
                    fc.arima212.close.price$upper, 
                    fc.arima212.close.price$x)), digits = 2) + 100

y.lower.limit <- signif(min(c(test.set.close.price,
                    fc.arima212.close.price$lower, 
                    fc.arima212.close.price$x)), digits = 2) - 100


plot(fc.arima212.close.price, ylim = c(y.lower.limit, y.upper.limit),
     type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
     axes = FALSE, main = "Arima(2,1,2)", xlab = "")
lines(test.set.close.price, type = "o",col = "red")

axis(1, 
     at = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
      labels = FALSE)

text(seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
     par("usr")[3] - 250, 
     labels = original.data[seq(tsp(close.price)[1], 
                                tsp(close.price)[2], 10), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2, at = seq(y.lower.limit, y.upper.limit, 300),
    labels = seq(y.lower.limit, y.upper.limit, 300), las = 1) 
               
box()

abline(v = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(y.lower.limit, y.upper.limit, 300), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))


```

```{r}

upper.bound <- fc.arima212.close.price$upper[,2]

lower.bound <- fc.arima212.close.price$lower[,2]

mean(test.set.close.price > lower.bound & test.set.close.price < upper.bound)

```

## Regression Modelling with Arima Errors

### Exploratory Data Analysis
```{r, fig.height = 14, fig.width=10}
par(mfrow = c(3,1))
plot(training.set.close.price)
plot(training.set.kdj.k)
plot(training.set.kdj.d)
```


```{r, fig.height=8, fig.width=10}

# training.set.close.price <- window(close.price, start = 1, end = 240)
# test.set.close.price <- window(close.price, start = 241)
# 
# training.set.volume <- window(volume, start = 1, end = 240)
# test.set.volume <- window(volume, start = 241)

# plot(training.set.close.price ~ training.set.volume)

pairs(training.set.close.price ~ training.set.kdj.k + training.set.kdj.d)

```

```{r, fig.height=8, fig.width=10}

# plot(diff(training.set.close.price) ~ diff(training.set.volume))

pairs(diff(training.set.close.price) ~ diff(training.set.kdj.k) + diff(training.set.kdj.d))

```

```{r, fig.height=8, fig.width=10}
# par(mfrow = c(2,1))
# plot(log(training.set.close.price))
# plot(log(training.set.volume))
```

```{r, fig.height=8, fig.width=10}
ndiffs(log(training.set.close.price))
ndiffs(log(training.set.kdj.k))
ndiffs(log(training.set.kdj.d))
```

```{r, fig.height=8, fig.width=10}

# plot(log(training.set.close.price) ~ log(training.set.volume))

```

```{r, fig.height=8, fig.width=10}

# plot(diff(log(training.set.close.price)) ~ diff(log(training.set.volume)))

```

```{r, fig.height=8, fig.width=10}
# Y <- ((abs(diff(log(training.set.close.price))))^(-3))
# X <- ((abs(diff(log(training.set.volume))))^(1))
# 
# plot(Y ~ X)

```


### Modelling for close.price and KDJ

```{r}

# reg.df <- cbind(training.set.volume, training.set.kdj.k, training.set.kdj.d)

reg.df <- cbind(training.set.kdj.k, training.set.kdj.d)
(fit.arima.kdj <- auto.arima(training.set.close.price, xreg = reg.df))

# summary(fit.lm <- lm(training.set.close.price ~ training.set.volume))

# (fit <- Arima(training.set.close.price, xreg = training.set.volume, order = c(2,1,0)))

# plot(training.set.close.price ~ training.set.volume)
# abline(fit.lm)

```

### White Noise Test


```{r}

Box.test(residuals(fit.arima.kdj), lag=10, fitdf=1)
Box.test(residuals(fit.arima.kdj), lag=10, fitdf=1, type = "Lj")

```

### Relationship Between Residuals And Time

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.arima.kdj), axes = FALSE, main = "Regression with Arima error")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(training.set.close.price)[1], tsp(training.set.close.price)[2], 5), 
     labels = original.data[seq(tsp(training.set.close.price)[1], 
                                tsp(training.set.close.price)[2], 5), 1])
axis(2)
box()
```

### Relationship Between Residuals And Fitted Value

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.arima.kdj)) ~ as.numeric(fitted(fit.arima.kdj)), 
     main = "Regression with Arima error")
abline(h = 0, col = "red")



```

There is obvious heteroscedasticity.


### Normality of  Residuals

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.arima.kdj), main = "Regression with Arima error")
qqline(residuals(fit.arima.kdj))

```

Residuals conform to normality.


### Comparison between actual value and forecast result 
```{r, fig.height=9, fig.width=10}
# par(mfrow = c(3,1))
fc.arima.kdj <- forecast(fit.arima.kdj, 
                         xreg = cbind(test.set.kdj.k, test.set.kdj.d),
                         h = length(test.set.close.price), 
                              level = c(80,95))

y.upper.limit <- signif(max(c(test.set.close.price,
                    fc.arima.kdj$upper, 
                    fc.arima.kdj$x)), digits = 2) + 100

y.lower.limit <- signif(min(c(test.set.close.price,
                    fc.arima.kdj$lower, 
                    fc.arima.kdj$x)), digits = 2) - 100


plot(fc.arima.kdj, ylim = c(y.lower.limit, y.upper.limit),
     type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
     axes = FALSE, main = "Regression with Arima errors", xlab = "")
lines(test.set.close.price, type = "o",col = "red")

axis(1, 
     at = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
      labels = FALSE)

text(seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
     par("usr")[3] - 250, 
     labels = original.data[seq(tsp(close.price)[1], 
                                tsp(close.price)[2], 10), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2, at = seq(y.lower.limit, y.upper.limit, 300),
    labels = seq(y.lower.limit, y.upper.limit, 300), las = 1) 
               
box()

abline(v = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(y.lower.limit, y.upper.limit, 300), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))


# plot(kdj.k)
# plot(kdj.d)

```

```{r}

upper.bound <- fc.arima.kdj$upper[,2]

lower.bound <- fc.arima.kdj$lower[,2]

mean(test.set.close.price > lower.bound & test.set.close.price < upper.bound)

```

### Modelling for close.price and lagged KDJ

```{r}

reg.lagged.df <- cbind(as.numeric(training.set.kdj.k),
                as.numeric(training.set.kdj.d),       
                ts(c(NA, training.set.kdj.k[-length(training.set.kdj.k)])),
                ts(c(NA, training.set.kdj.d[-length(training.set.kdj.d)])),
                ts(c(NA, NA, head(training.set.kdj.k, length(training.set.kdj.k) - 2))),
                ts(c(NA, NA, head(training.set.kdj.d, length(training.set.kdj.d) - 2))),
                ts(c(NA, NA, NA, head(training.set.kdj.k, length(training.set.kdj.k) - 3))),
                ts(c(NA, NA, NA, head(training.set.kdj.d, length(training.set.kdj.d) - 3))))

fit.pure.arima <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                             stepwise = FALSE, 
                              approximation = FALSE, max.order = 9)
                

fit.12 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1:2],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.14 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1:4],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.16 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1:6],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.18 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1:8],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.34 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 3:4],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.36 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 3:6],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.38 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 3:8],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.2 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 2],
                    max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.2.4 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(2,4)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.2.4.6 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(2,4,6)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.2.4.6.8 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(2,4,6,8)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.1 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1],
                    max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.1.3 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(1,3)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.1.3.5 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(1,3,5)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.1.3.5.7 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
                     xreg = reg.lagged.df[4:nrow(reg.lagged.df), c(1,3,5,7)],
                     max.order = 9, stepwise = FALSE, approximation = FALSE)

fit.pure.arima$aicc

fit.12$aicc
fit.14$aicc
fit.16$aicc
fit.18$aicc
fit.34$aicc
fit.36$aicc
fit.38$aicc

fit.2$aicc
fit.2.4$aicc
fit.2.4.6$aicc
fit.2.4.6.8$aicc

fit.1$aicc
fit.1.3$aicc
fit.1.3.5$aicc
fit.1.3.5.7$aicc
```

```{r}
reg.lagged.df <- cbind(training.set.kdj.k,
                training.set.kdj.d,       
                c(NA, training.set.kdj.k[-length(training.set.kdj.k)]),
                c(NA, training.set.kdj.d[-length(training.set.kdj.d)]),
                c(NA, NA, head(training.set.kdj.k, length(training.set.kdj.k) - 2)),
                c(NA, NA, head(training.set.kdj.d, length(training.set.kdj.d) - 2)),
                c(NA, NA, NA, head(training.set.kdj.k, length(training.set.kdj.k) - 3)),
                c(NA, NA, NA, head(training.set.kdj.d, length(training.set.kdj.d) - 3)))


(fit.lagged.arima <- auto.arima(training.set.close.price, xreg = reg.lagged.df[, 1:4]))
                    
(fit.lagged.arima.2.4.6 <- auto.arima(training.set.close.price,
                                      # allowdrift = FALSE,
                                      xreg = reg.lagged.df[, c(2,4,6)],
                                      # max.p=7, max.q=7,
                                      max.order = 9, stepwise = FALSE, approximation = FALSE)) 

(fit.lagged.arima.2.4.6.8 <- auto.arima(training.set.close.price, 
                                        #allowdrift = FALSE,
                                        xreg = reg.lagged.df[, c(2,4,6,8)])) 

(fit.lagged.arima.1.3 <- auto.arima(training.set.close.price, xreg = reg.lagged.df[, c(1,3)])) 

(fit.lagged.arima.16 <- auto.arima(training.set.close.price, 
                     xreg = reg.lagged.df[, 1:6],
                     stepwise = FALSE, approximation = FALSE))

(fit.lagged.arima.18 <- auto.arima(training.set.close.price, 
                     xreg = reg.lagged.df[, 1:8],
                     max.order = 9, stepwise = FALSE, approximation = FALSE))
```

```{r}

# coeftest(fit.lagged.arima, vcov. = vcovHAC)
                     

```

### White Noise Test


```{r}

Box.test(residuals(fit.lagged.arima), lag=10, fitdf=1)
Box.test(residuals(fit.lagged.arima), lag=10, fitdf=1, type = "Lj")

Box.test(residuals(fit.lagged.arima.2.4.6), lag=10, fitdf=9)
Box.test(residuals(fit.lagged.arima.2.4.6), lag=10, fitdf=9, type = "Lj")

Box.test(residuals(fit.lagged.arima.2.4.6.8), lag=10, fitdf=1)
Box.test(residuals(fit.lagged.arima.2.4.6.8), lag=10, fitdf=1, type = "Lj")

Box.test(residuals(fit.lagged.arima.1.3), lag=10, fitdf=1)
Box.test(residuals(fit.lagged.arima.1.3), lag=10, fitdf=1, type = "Lj")

Box.test(residuals(fit.lagged.arima.1.3), lag=10, fitdf=1)
Box.test(residuals(fit.lagged.arima.1.3), lag=10, fitdf=1, type = "Lj")

Box.test(residuals(fit.lagged.arima.16), lag=10, fitdf=5)
Box.test(residuals(fit.lagged.arima.16), lag=10, fitdf=5, type = "Lj")

Box.test(residuals(fit.lagged.arima.18), lag=10, fitdf=5)
Box.test(residuals(fit.lagged.arima.18), lag=10, fitdf=5, type = "Lj")
```

### Relationship Between Residuals And Time

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.lagged.arima), axes = FALSE, main = "Lagged Regression with Arima error")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(training.set.close.price)[1], tsp(training.set.close.price)[2], 5), 
     labels = original.data[seq(tsp(training.set.close.price)[1], 
                                tsp(training.set.close.price)[2], 5), 1])
axis(2)
box()


plot(residuals(fit.lagged.arima.2.4.6), axes = FALSE, main = "Lagged Regression with Arima error")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(training.set.close.price)[1], tsp(training.set.close.price)[2], 5), 
     labels = original.data[seq(tsp(training.set.close.price)[1], 
                                tsp(training.set.close.price)[2], 5), 1])
axis(2)
box()
```

### Relationship Between Residuals And Fitted Value

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.lagged.arima)) ~ as.numeric(fitted(fit.lagged.arima)), 
     main = "Lagged Regression with Arima error")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.lagged.arima.2.4.6)) ~ as.numeric(fitted(fit.lagged.arima.2.4.6)), 
     main = "Lagged Regression with Arima error")
abline(h = 0, col = "red")

```

There is obvious heteroscedasticity.


### Normality of  Residuals

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.lagged.arima), main = "Lagged Regression with Arima error")
qqline(residuals(fit.lagged.arima))


qqnorm(residuals(fit.lagged.arima.2.4.6), main = "Lagged Regression with Arima error")
qqline(residuals(fit.lagged.arima.2.4.6))
```

Residuals conform to normality.

### Comparison between actual value and forecast result 
```{r, fig.height=9, fig.width=10}
# par(mfrow = c(3,1))
fc.lagged.arima <- forecast(fit.lagged.arima, 
                            xreg = cbind(test.set.kdj.k, 
                                         test.set.kdj.d,
        c(training.set.kdj.k[length(training.set.kdj.k)], test.set.kdj.k[-length(test.set.kdj.k)]),
        c(training.set.kdj.d[length(training.set.kdj.d)], test.set.kdj.d[-length(test.set.kdj.d)])),
                            h = length(test.set.close.price), 
                            level = c(80,95))

y.upper.limit <- signif(max(c(test.set.close.price,
                    fc.lagged.arima$upper, 
                    fc.lagged.arima$x)), digits = 2) + 100

y.lower.limit <- signif(min(c(test.set.close.price,
                    fc.lagged.arima$lower, 
                    fc.lagged.arima$x)), digits = 2) - 100


plot(fc.lagged.arima, ylim = c(y.lower.limit, y.upper.limit),
     type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
     axes = FALSE, main = "Lagged Regression with Arima errors", xlab = "")
lines(test.set.close.price, type = "o",col = "red")

axis(1, 
     at = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
      labels = FALSE)

text(seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
     par("usr")[3] - 250, 
     labels = original.data[seq(tsp(close.price)[1], 
                                tsp(close.price)[2], 10), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2, at = seq(y.lower.limit, y.upper.limit, 300),
    labels = seq(y.lower.limit, y.upper.limit, 300), las = 1) 
               
box()

abline(v = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(y.lower.limit, y.upper.limit, 300), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))
```

```{r}

upper.bound <- fc.lagged.arima$upper[,2]

lower.bound <- fc.lagged.arima$lower[,2]

mean(test.set.close.price > lower.bound & test.set.close.price < upper.bound)

```


## Comparison of accuracy of 3 Models 
```{r}


df.test.set <- rbind(accuracy(fc.arima212.close.price, test.set.close.price)[2,],
            accuracy(fc.arima.kdj, test.set.close.price)[2,],
            accuracy(fc.lagged.arima, test.set.close.price)[2,])

row.names(df.test.set) <- c("Pure Arima","Reg Arima", "Lagged reg")
print(round(df.test.set, 2))



```

## Comparison of PI of 3 Models 
```{r}
arima.pure.pi <- fc.arima212.close.price$upper[,2] - fc.arima212.close.price$lower[,2]

arima.kdj.pi <- fc.arima.kdj$upper[,2] - fc.arima.kdj$lower[,2]

lagged.kdj.pi <- fc.lagged.arima$upper[,2] - fc.lagged.arima$lower[,2]

cbind(arima.pure.pi, arima.kdj.pi, lagged.kdj.pi)

# df.test.set <- rbind(accuracy(fc.arima212.close.price, test.set.close.price)[2,],
#             accuracy(fc.arima.kdj, test.set.close.price)[2,])
# 
# row.names(df.test.set) <- c("Pure Arima","Reg Arima")
# print(round(df.test.set, 3))



```


### Modelling for close.price and volume

```{r}

# reg.lagged.df <- cbind(training.set.volume,
#                 c(NA, training.set.volume[-length(training.set.volume)]),
#                 c(NA, NA, head(training.set.volume, length(training.set.volume) - 2)),
#                 c(NA, NA, NA, head(training.set.volume, length(training.set.volume) - 3)))
#                 
# 
# (fit.1 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
#                      xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1]))
# 
# (fit.12 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
#                      xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1:2]))
# 
# (fit.13 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
#                      xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1:3]))
# 
# (fit.14 <- auto.arima(training.set.close.price[4:length(training.set.close.price)], 
#                      xreg = reg.lagged.df[4:nrow(reg.lagged.df), 1:4]))
# 
# 
# fit.1$aicc
# fit.12$aicc
# fit.13$aicc
# fit.14$aicc

```


## Arima Modelling for kdj.k
```{r}

(fit.arima.kdj.k <- auto.arima(training.set.kdj.k))

```


### White Noise Test


```{r}

Box.test(residuals(fit.arima.kdj.k), lag=10, fitdf=5)
Box.test(residuals(fit.arima.kdj.k), lag=10, fitdf=5, type = "Lj")

```

### Relationship Between Residuals And Time

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.arima.kdj.k), axes = FALSE, main = "Arima model of kdj.k")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(training.set.close.price)[1], tsp(training.set.close.price)[2], 5), 
     labels = original.data[seq(tsp(training.set.close.price)[1], 
                                tsp(training.set.close.price)[2], 5), 1])
axis(2)
box()
```

### Relationship Between Residuals And Fitted Value

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.arima.kdj.k)) ~ as.numeric(fitted(fit.arima.kdj.k)), 
     main = "Arima model of kdj.k")
abline(h = 0, col = "red")



```

There is no obvious heteroscedasticity.


### Normality of  Residuals

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.arima.kdj.k), main = "Arima model of kdj.k")
qqline(residuals(fit.arima.kdj.k))

```

Residuals conform to normality.

### Comparison between actual value and forecast result 
```{r, fig.height=9, fig.width=10}
# par(mfrow = c(3,1))
fc.arima.kdj.k <- forecast(fit.arima.kdj.k, 
                             h = length(test.set.kdj.k), 
                            level = c(80,95))

plot(fc.arima.kdj.k, ylim = c(5, 95),
     type = "o", plot.conf = FALSE, shaded = FALSE, pi.col = "purple",
     axes = FALSE, main = "Arima model of kdj.k", xlab = "")
lines(test.set.kdj.k, type = "o",col = "red")

axis(1, 
     at = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
      labels = FALSE)

text(seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
     par("usr")[3] - 250, 
     labels = original.data[seq(tsp(close.price)[1], 
                                tsp(close.price)[2], 10), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2, at = seq(5, 95, 10),
    labels = seq(5, 95, 10), las = 1) 
               
box()

abline(v = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(5, 95, 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))
```


## ETS Modelling for kdj.k
```{r}

(fit.ets.kdj.k <- ets(training.set.kdj.k))

```


### White Noise Test


```{r}

Box.test(residuals(fit.ets.kdj.k), lag=10, fitdf=3)
Box.test(residuals(fit.ets.kdj.k), lag=10, fitdf=3, type = "Lj")

```

### Relationship Between Residuals And Time

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.ets.kdj.k), axes = FALSE, main = "ets model of kdj.k")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(training.set.close.price)[1], tsp(training.set.close.price)[2], 5), 
     labels = original.data[seq(tsp(training.set.close.price)[1], 
                                tsp(training.set.close.price)[2], 5), 1])
axis(2)
box()
```

### Relationship Between Residuals And Fitted Value

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.ets.kdj.k)) ~ as.numeric(fitted(fit.ets.kdj.k)), 
     main = "ETS model of kdj.k")
abline(h = 0, col = "red")



```

There is no obvious heteroscedasticity.


### Normality of  Residuals

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.ets.kdj.k), main = "ETS model of kdj.k")
qqline(residuals(fit.ets.kdj.k))

```

Residuals conform to normality.

### Comparison between actual value and forecast result 
```{r, fig.height=9, fig.width=10}
# par(mfrow = c(3,1))
fc.ets.kdj.k <- forecast(fit.ets.kdj.k, 
                             h = length(test.set.kdj.k), 
                            level = c(80,95))

plot(fc.ets.kdj.k, ylim = c(5, 95),
     type = "o", plot.conf = FALSE, shaded = FALSE, pi.col = "purple",
     axes = FALSE, main = "ETS model of kdj.k", xlab = "")
lines(test.set.kdj.k, type = "o",col = "red")

axis(1, 
     at = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
      labels = FALSE)

text(seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
     par("usr")[3] - 250, 
     labels = original.data[seq(tsp(close.price)[1], 
                                tsp(close.price)[2], 10), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2, at = seq(5, 95, 10),
    labels = seq(5, 95, 10), las = 1) 
               
box()

abline(v = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(5, 95, 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))
```

## Comparison of accuracy of 2 Models 
```{r}


df.test.set <- rbind(accuracy(fc.arima.kdj.k, test.set.kdj.k)[2,],
            accuracy(fc.ets.kdj.k, test.set.kdj.k)[2,])

row.names(df.test.set) <- c("Arima","ETS")
print(round(df.test.set, 2))



```


## Arima Modelling for kdj.d
```{r}

training.set.kdj.d <- window(kdj.d, start = 1, end = 250)
test.set.kdj.d <- window(kdj.d, start = 251)

(fit.arima.kdj.d <- auto.arima(training.set.kdj.d))

```


### White Noise Test


```{r}

Box.test(residuals(fit.arima.kdj.d), lag=10, fitdf=4)
Box.test(residuals(fit.arima.kdj.d), lag=10, fitdf=4, type = "Lj")

```

### Relationship Between Residuals And Time

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.arima.kdj.d), axes = FALSE, main = "Arima model of kdj.d")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(training.set.close.price)[1], tsp(training.set.close.price)[2], 5), 
     labels = original.data[seq(tsp(training.set.close.price)[1], 
                                tsp(training.set.close.price)[2], 5), 1])
axis(2)
box()
```

### Relationship Between Residuals And Fitted Value

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.arima.kdj.d)) ~ as.numeric(fitted(fit.arima.kdj.d)), 
     main = "Arima model of kdj.d")
abline(h = 0, col = "red")



```

There is no obvious heteroscedasticity.


### Normality of  Residuals

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.arima.kdj.d), main = "Arima model of kdj.d")
qqline(residuals(fit.arima.kdj.d))

```

Residuals conform to normality.

### Comparison between actual value and forecast result 
```{r, fig.height=9, fig.width=10}
# par(mfrow = c(3,1))
fc.arima.kdj.d <- forecast(fit.arima.kdj.d, 
                             h = length(test.set.kdj.d), 
                            level = c(80,95))

plot(fc.arima.kdj.d, ylim = c(5, 95),
     type = "o", plot.conf = FALSE, shaded = FALSE, pi.col = "purple",
     axes = FALSE, main = "Arima model of kdj.d", xlab = "")
lines(test.set.kdj.d, type = "o",col = "red")

axis(1, 
     at = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
      labels = TRUE)

# text(seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
#      par("usr")[3] - 250, 
#      labels = original.data[seq(tsp(close.price)[1], 
#                                 tsp(close.price)[2], 10), 1], 
#      srt = 45, 
#      pos = 1, 
#      xpd = TRUE)

axis(2, at = seq(5, 95, 10),
    labels = seq(5, 95, 10), las = 1) 
               
box()

abline(v = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(5, 95, 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))
```


## ETS Modelling for kdj.d
```{r}

(fit.ets.kdj.d <- ets(training.set.kdj.d))

```


### White Noise Test


```{r}

Box.test(residuals(fit.ets.kdj.d), lag=10, fitdf=3)
Box.test(residuals(fit.ets.kdj.d), lag=10, fitdf=3, type = "Lj")

```

### Relationship Between Residuals And Time

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(residuals(fit.ets.kdj.d), axes = FALSE, main = "ets model of kdj.k")
abline(h = 0, col = "red")
axis(1, 
     at = seq(tsp(training.set.close.price)[1], tsp(training.set.close.price)[2], 5), 
     labels = original.data[seq(tsp(training.set.close.price)[1], 
                                tsp(training.set.close.price)[2], 5), 1])
axis(2)
box()
```

### Relationship Between Residuals And Fitted Value

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

plot(as.numeric(residuals(fit.ets.kdj.d)) ~ as.numeric(fitted(fit.ets.kdj.d)), 
     main = "ETS model of kdj.d")
abline(h = 0, col = "red")



```

There is no obvious heteroscedasticity.


### Normality of  Residuals

```{r, fig.height=9, fig.width=10}
# dev.off()
par(mfrow = c(1,1))

qqnorm(residuals(fit.ets.kdj.d), main = "ETS model of kdj.d")
qqline(residuals(fit.ets.kdj.d))

```

Residuals conform to normality.

### Comparison between actual value and forecast result 
```{r, fig.height=9, fig.width=10}
# par(mfrow = c(3,1))
fc.ets.kdj.d <- forecast(fit.ets.kdj.d, 
                             h = length(test.set.kdj.d), 
                            level = c(80,95))


plot(fc.ets.kdj.d, ylim = c(5, 95),
     type = "o", plot.conf = FALSE, shaded = FALSE, pi.col = "purple",
     axes = FALSE, main = "ETS model of kdj.d", xlab = "")
lines(test.set.kdj.d, type = "o",col = "red")

axis(1, 
     at = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
      labels = FALSE)

text(seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
     par("usr")[3] - 250, 
     labels = original.data[seq(tsp(close.price)[1], 
                                tsp(close.price)[2], 10), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2, at = seq(5, 95, 10),
    labels = seq(5, 95, 10), las = 1) 
               
box()

abline(v = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(5, 95, 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))
```

## Comparison of accuracy of 2 Models 
```{r}


df.test.set <- rbind(accuracy(fc.arima.kdj.d, test.set.kdj.d)[2,],
            accuracy(fc.ets.kdj.d, test.set.kdj.d)[2,])

row.names(df.test.set) <- c("Arima","ETS")
print(round(df.test.set, 2))



```



### Comparison between actual value and forecast result of true kd and estimated kd
```{r, fig.height=9, fig.width=10}
par(mfrow = c(2,1))
fc.lagged.arima <- forecast(fit.lagged.arima, 
                            xreg = cbind(test.set.kdj.k, 
                                         test.set.kdj.d,
        c(training.set.kdj.k[length(training.set.kdj.k)], test.set.kdj.k[-length(test.set.kdj.k)]),
        c(training.set.kdj.d[length(training.set.kdj.d)], test.set.kdj.d[-length(test.set.kdj.d)])),
                            h = length(test.set.close.price), 
                            level = c(80,95))

y.upper.limit <- signif(max(c(test.set.close.price,
                    fc.lagged.arima$upper, 
                    fc.lagged.arima$x)), digits = 2) + 100

y.lower.limit <- signif(min(c(test.set.close.price,
                    fc.lagged.arima$lower, 
                    fc.lagged.arima$x)), digits = 2) - 100


plot(fc.lagged.arima, ylim = c(y.lower.limit, y.upper.limit),
     type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
     axes = FALSE, main = "Lagged Regression with Arima errors", xlab = "")
lines(test.set.close.price, type = "o",col = "red")

axis(1, 
     at = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
      labels = FALSE)

text(seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
     par("usr")[3] - 250, 
     labels = original.data[seq(tsp(close.price)[1], 
                                tsp(close.price)[2], 10), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2, at = seq(y.lower.limit, y.upper.limit, 300),
    labels = seq(y.lower.limit, y.upper.limit, 300), las = 1) 
               
box()

abline(v = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(y.lower.limit, y.upper.limit, 300), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

estimated.kdj.k <- forecast(fit.arima.kdj.k, h = length(test.set.kdj.k))$mean
estimated.kdj.d <- forecast(fit.arima.kdj.d, h = length(test.set.kdj.d))$mean

fc.lagged.arima.estimated <- forecast(fit.lagged.arima, 
                            xreg = cbind(estimated.kdj.k, 
                                         estimated.kdj.d,
        c(training.set.kdj.k[length(training.set.kdj.k)], estimated.kdj.k[-length(estimated.kdj.k)]),
        c(training.set.kdj.d[length(training.set.kdj.d)], estimated.kdj.d[-length(estimated.kdj.d)])),
                            h = length(test.set.close.price), 
                            level = c(80,95))

y.upper.limit <- signif(max(c(test.set.close.price,
                    fc.lagged.arima.estimated$upper, 
                    fc.lagged.arima.estimated$x)), digits = 2) + 100

y.lower.limit <- signif(min(c(test.set.close.price,
                    fc.lagged.arima.estimated$lower, 
                    fc.lagged.arima.estimated$x)), digits = 2) - 100


plot(fc.lagged.arima.estimated, ylim = c(y.lower.limit, y.upper.limit),
     type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
     axes = FALSE, main = "estimated Lagged Regression with Arima errors", xlab = "")
lines(test.set.close.price, type = "o",col = "red")

axis(1, 
     at = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
      labels = FALSE)

text(seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
     par("usr")[3] - 250, 
     labels = original.data[seq(tsp(close.price)[1], 
                                tsp(close.price)[2], 10), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2, at = seq(y.lower.limit, y.upper.limit, 300),
    labels = seq(y.lower.limit, y.upper.limit, 300), las = 1) 
               
box()

abline(v = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(y.lower.limit, y.upper.limit, 300), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))
```

### Comparison between actual value and forecast result of true kd and estimated kd for 5 weeks
```{r, fig.height=9, fig.width=10}

training.set.close.price <- window(close.price, start = 1, end = 240)
test.set.close.price <- window(close.price, start = 241)

training.set.kdj.k <- window(kdj.k, start = 1, end = 240)
test.set.kdj.k <- window(kdj.k, start = 241)

training.set.kdj.d <- window(kdj.d, start = 1, end = 240)
test.set.kdj.d <- window(kdj.d, start = 241)

reg.lagged.df <- cbind(training.set.kdj.k,
                training.set.kdj.d,       
                c(NA, training.set.kdj.k[-length(training.set.kdj.k)]),
                c(NA, training.set.kdj.d[-length(training.set.kdj.d)]),
                c(NA, NA, head(training.set.kdj.k, length(training.set.kdj.k) - 2)),
                c(NA, NA, head(training.set.kdj.d, length(training.set.kdj.d) - 2)),
                c(NA, NA, NA, head(training.set.kdj.k, length(training.set.kdj.k) - 3)),
                c(NA, NA, NA, head(training.set.kdj.d, length(training.set.kdj.d) - 3)))


fit.lagged.arima <- auto.arima(training.set.close.price, xreg = reg.lagged.df[, 1:4])

par(mfrow = c(2,1))
fc.lagged.arima <- forecast(fit.lagged.arima, 
                            xreg = cbind(test.set.kdj.k[1:5], 
                                         test.set.kdj.d[1:5],
                                         c(training.set.kdj.k[length(training.set.kdj.k)], 
                                           test.set.kdj.k[1:4]),
                                         c(training.set.kdj.d[length(training.set.kdj.d)],
                                           as.ts(test.set.kdj.d[1:4]))),
                            h = 5, 
                            level = c(80,95))

y.upper.limit <- signif(max(c(test.set.close.price,
                    fc.lagged.arima$upper, 
                    fc.lagged.arima$x)), digits = 2) + 100

y.lower.limit <- signif(min(c(test.set.close.price,
                    fc.lagged.arima$lower, 
                    fc.lagged.arima$x)), digits = 2) - 100


plot(fc.lagged.arima, ylim = c(y.lower.limit, y.upper.limit),
     type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
     axes = FALSE, main = "Lagged Regression with Arima errors", xlab = "")
lines(window(test.set.close.price, 
             start = tsp(test.set.close.price)[1],
             end = tsp(test.set.close.price)[1] + 4), 
      type = "o",col = "red")

axis(1, 
     at = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
      labels = FALSE)

text(seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
     par("usr")[3] - 250, 
     labels = original.data[seq(tsp(close.price)[1], 
                                tsp(close.price)[2], 10), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2, at = seq(y.lower.limit, y.upper.limit, 300),
    labels = seq(y.lower.limit, y.upper.limit, 300), las = 1) 
               
box()

abline(v = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(y.lower.limit, y.upper.limit, 300), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

fit.arima.kdj.k <- auto.arima(training.set.kdj.k)
fit.arima.kdj.d <- auto.arima(training.set.kdj.d)

estimated.kdj.k <- forecast(fit.arima.kdj.k, h = length(test.set.kdj.k))$mean
estimated.kdj.d <- forecast(fit.arima.kdj.d, h = length(test.set.kdj.d))$mean

fc.lagged.arima.estimated <- forecast(fit.lagged.arima, 
                                      xreg = cbind(estimated.kdj.k[1:5], 
                                                   estimated.kdj.d[1:5],
                                                   c(training.set.kdj.k[length(training.set.kdj.k)], 
                                                     estimated.kdj.k[1:4]),
                                                   c(training.set.kdj.d[length(training.set.kdj.d)], 
                                                     estimated.kdj.d[1:4])),
                                      h = 5, 
                                      level = c(80,95))

y.upper.limit <- signif(max(c(test.set.close.price,
                    fc.lagged.arima.estimated$upper, 
                    fc.lagged.arima.estimated$x)), digits = 2) + 100

y.lower.limit <- signif(min(c(test.set.close.price,
                    fc.lagged.arima.estimated$lower, 
                    fc.lagged.arima.estimated$x)), digits = 2) - 100


plot(fc.lagged.arima.estimated, ylim = c(y.lower.limit, y.upper.limit),
     type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
     axes = FALSE, main = "estimated Lagged Regression with Arima errors", xlab = "")

lines(window(test.set.close.price, 
             start = tsp(test.set.close.price)[1],
             end = tsp(test.set.close.price)[1] + 4), 
      type = "o",col = "red")

axis(1, 
     at = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
      labels = FALSE)

text(seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
     par("usr")[3] - 250, 
     labels = original.data[seq(tsp(close.price)[1], 
                                tsp(close.price)[2], 10), 1], 
     srt = 45, 
     pos = 1, 
     xpd = TRUE)

axis(2, at = seq(y.lower.limit, y.upper.limit, 300),
    labels = seq(y.lower.limit, y.upper.limit, 300), las = 1) 
               
box()

abline(v = seq(tsp(close.price)[1], tsp(close.price)[2], 10), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))

abline(h = seq(y.lower.limit, y.upper.limit, 300), 
       col = "springgreen4", 
       lty = "dashed",
       lwd = par("lwd"))
```


## Comparison of 5 weeks accuracy of 3 Models 
```{r}
fc.arima212.close.price <- forecast(fit.212.close.price, h = 5, 
                              level = c(80,95))

fc.arima.kdj <- forecast(fit.arima.kdj, 
                         xreg = cbind(test.set.kdj.k[1:5], test.set.kdj.d[1:5]),
                         h = 5, 
                              level = c(80,95))

fc.lagged.arima <- forecast(fit.lagged.arima, 
                            xreg = cbind(test.set.kdj.k[1:5], 
                                         test.set.kdj.d[1:5],
                                         c(training.set.kdj.k[length(training.set.kdj.k)], 
                                           test.set.kdj.k[1:4]),
                                         c(training.set.kdj.d[length(training.set.kdj.d)],
                                           as.ts(test.set.kdj.d[1:4]))),
                            h = 5, 
                            level = c(80,95))

fc.lagged.arima.estimated <- forecast(fit.lagged.arima, 
                                      xreg = cbind(estimated.kdj.k[1:5], 
                                                   estimated.kdj.d[1:5],
                                                   c(training.set.kdj.k[length(training.set.kdj.k)], 
                                                     estimated.kdj.k[1:4]),
                                                   c(training.set.kdj.d[length(training.set.kdj.d)], 
                                                     estimated.kdj.d[1:4])),
                                      h = 5, 
                                      level = c(80,95))


df.test.set <- rbind(accuracy(fc.arima212.close.price, test.set.close.price[1:5])[2,],
            accuracy(fc.arima.kdj, test.set.close.price[1:5])[2,],
            accuracy(fc.lagged.arima, test.set.close.price[1:5])[2,],
            accuracy(fc.lagged.arima.estimated, test.set.close.price[1:5])[2,])

row.names(df.test.set) <- c("Pure Arima","Reg Arima", "Lagged reg", "Lagged estimated reg")
print(round(df.test.set, 2))



```


### function of Comparison between actual value and forecast result of true kd and estimated kd for 5 weeks
```{r, fig.height=9, fig.width=10}
DrawForecastPlot <- function(arg.close.price, arg.kdj.k, arg.kdj.d, 
                             arg.training.set.endpoint, arg.forecast.period){
        
        training.set.close.price <- window(arg.close.price, start = 1, end = arg.training.set.endpoint)
        test.set.close.price <- window(arg.close.price, start = arg.training.set.endpoint + 1,
                                       end = arg.training.set.endpoint + arg.forecast.period)
        
        training.set.kdj.k <- window(arg.kdj.k, start = 1, end = arg.training.set.endpoint)
        test.set.kdj.k <- window(arg.kdj.k, start = arg.training.set.endpoint + 1,
                                       end = arg.training.set.endpoint + arg.forecast.period)
        
        training.set.kdj.d <- window(arg.kdj.d, start = 1, end = arg.training.set.endpoint)
        test.set.kdj.d <- window(arg.kdj.d, start = arg.training.set.endpoint + 1,
                                       end = arg.training.set.endpoint + arg.forecast.period)        

        reg.lagged.df <- cbind(training.set.kdj.k,
                               training.set.kdj.d,       
                               c(NA, training.set.kdj.k[-length(training.set.kdj.k)]),
                               c(NA, training.set.kdj.d[-length(training.set.kdj.d)]),
                               c(NA, NA, head(training.set.kdj.k, length(training.set.kdj.k) - 2)),
                               c(NA, NA, head(training.set.kdj.d, length(training.set.kdj.d) - 2)),
                               c(NA, NA, NA, head(training.set.kdj.k, length(training.set.kdj.k) - 3)),
                               c(NA, NA, NA, head(training.set.kdj.d, length(training.set.kdj.d) - 3)))
        
        fit.lagged.arima <- auto.arima(training.set.close.price, xreg = reg.lagged.df[, 1:4])
        
        par(mfrow = c(2,1))
        fc.lagged.arima <- forecast(fit.lagged.arima, 
                                    xreg = cbind(test.set.kdj.k, 
                                                 test.set.kdj.d,
                                                 c(training.set.kdj.k[length(training.set.kdj.k)], 
                                                   test.set.kdj.k[1:(arg.forecast.period - 1)]),
                                                 c(training.set.kdj.d[length(training.set.kdj.d)],
                                                   as.ts(test.set.kdj.d[1:(arg.forecast.period - 1)]))),
                                    h = arg.forecast.period, 
                                    level = c(80,95))


        y.upper.limit <- signif(max(c(test.set.close.price,
                                      fc.lagged.arima$upper, 
                                      fc.lagged.arima$x)), digits = 2) + 100
        
        y.lower.limit <- signif(min(c(test.set.close.price,
                                      fc.lagged.arima$lower, 
                                      fc.lagged.arima$x)), digits = 2) - 100
        
        plot(fc.lagged.arima, ylim = c(y.lower.limit, y.upper.limit),
             type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
             axes = FALSE, main = "Lagged Regression with Arima errors", xlab = "")
        
        lines(test.set.close.price, type = "o",col = "red") 
              
        axis(1, 
             at = seq(tsp(arg.close.price)[1], tsp(arg.close.price)[2], 10), 
             labels = FALSE)
        
        text(seq(tsp(arg.close.price)[1], tsp(arg.close.price)[2], 10), 
             par("usr")[3] - 250, 
             labels = original.data[seq(tsp(arg.close.price)[1], 
                                        tsp(arg.close.price)[2], 10), 1], 
             srt = 45, 
             pos = 1, 
             xpd = TRUE)
        
        axis(2, at = seq(y.lower.limit, y.upper.limit, 300),
             labels = seq(y.lower.limit, y.upper.limit, 300), las = 1) 
        
        box()
        
        abline(v = seq(tsp(arg.close.price)[1], tsp(arg.close.price)[2], 10), 
               col = "springgreen4", 
               lty = "dashed",
               lwd = par("lwd"))
        
        abline(h = seq(y.lower.limit, y.upper.limit, 300), 
               col = "springgreen4", 
               lty = "dashed",
               lwd = par("lwd"))
        
        fit.arima.kdj.k <- auto.arima(training.set.kdj.k)
        fit.arima.kdj.d <- auto.arima(training.set.kdj.d)
        
        estimated.kdj.k <- forecast(fit.arima.kdj.k, h = length(test.set.kdj.k))$mean
        estimated.kdj.d <- forecast(fit.arima.kdj.d, h = length(test.set.kdj.d))$mean        

        fc.lagged.arima.estimated <- forecast(fit.lagged.arima, 
                                      xreg = cbind(estimated.kdj.k, 
                                                   estimated.kdj.d,
                                                   c(training.set.kdj.k[length(training.set.kdj.k)], 
                                                     estimated.kdj.k[1:(arg.forecast.period - 1)]),
                                                   c(training.set.kdj.d[length(training.set.kdj.d)], 
                                                     estimated.kdj.d[1:(arg.forecast.period - 1)])),
                                      h = arg.forecast.period, 
                                      level = c(80,95))


        y.upper.limit <- signif(max(c(test.set.close.price,
                                      fc.lagged.arima.estimated$upper, 
                                      fc.lagged.arima.estimated$x)), digits = 2) + 100
        
        y.lower.limit <- signif(min(c(test.set.close.price,
                                      fc.lagged.arima.estimated$lower, 
                                      fc.lagged.arima.estimated$x)), digits = 2) - 100

        plot(fc.lagged.arima.estimated, ylim = c(y.lower.limit, y.upper.limit),
             type = "o", plot.conf = TRUE, shaded = TRUE, pi.col = "purple",
             axes = FALSE, main = "estimated Lagged Regression with Arima errors", xlab = "")
        
        lines(test.set.close.price, type = "o",col = "red")

        axis(1, 
             at = seq(tsp(arg.close.price)[1], tsp(arg.close.price)[2], 10), 
             labels = FALSE)
        
        text(seq(tsp(arg.close.price)[1], tsp(arg.close.price)[2], 10), 
             par("usr")[3] - 250, 
             labels = original.data[seq(tsp(arg.close.price)[1], 
                                        tsp(arg.close.price)[2], 10), 1], 
             srt = 45, 
             pos = 1, 
             xpd = TRUE)
        
        axis(2, at = seq(y.lower.limit, y.upper.limit, 300),
             labels = seq(y.lower.limit, y.upper.limit, 300), las = 1) 
        
        box()
        
        abline(v = seq(tsp(arg.close.price)[1], tsp(arg.close.price)[2], 10), 
               col = "springgreen4", 
               lty = "dashed",
               lwd = par("lwd"))
        
        abline(h = seq(y.lower.limit, y.upper.limit, 300), 
               col = "springgreen4", 
               lty = "dashed",
               lwd = par("lwd"))        
}


```


```{r, fig.height=9, fig.width=10}
DrawForecastPlot(close.price, kdj.k, kdj.d, 
                             arg.training.set.endpoint = 252, arg.forecast.period = 2)

```
        

```{r, fig.height=9, fig.width=10}
DrawKDJPlot <- function(arg.kdj.k, arg.kdj.d, 
                             arg.training.set.endpoint, arg.forecast.period){
        

        training.set.kdj.k <- window(arg.kdj.k, start = 1, end = arg.training.set.endpoint)
        test.set.kdj.k <- window(arg.kdj.k, start = arg.training.set.endpoint + 1,
                                       end = arg.training.set.endpoint + arg.forecast.period)
        
        training.set.kdj.d <- window(arg.kdj.d, start = 1, end = arg.training.set.endpoint)
        test.set.kdj.d <- window(arg.kdj.d, start = arg.training.set.endpoint + 1,
                                       end = arg.training.set.endpoint + arg.forecast.period)        


        par(mfrow = c(2,1))


        fit.arima.kdj.k <- auto.arima(training.set.kdj.k)
        fit.arima.kdj.d <- auto.arima(training.set.kdj.d)
        
        estimated.kdj.k <- forecast(fit.arima.kdj.k, h = length(test.set.kdj.k))
        estimated.kdj.d <- forecast(fit.arima.kdj.d, h = length(test.set.kdj.d))        

        plot(estimated.kdj.k, type = "o")
        lines(test.set.kdj.k, col = "red", type = "o")
        
        plot(estimated.kdj.d, type = "o")
        lines(test.set.kdj.d, col = "red", type = "o")
        
}


```

```{r, fig.height=9, fig.width=10}
DrawKDJPlot(kdj.k, kdj.d, arg.training.set.endpoint = 203, arg.forecast.period = 3)

```
