---
title: "ARIMA Prediction Of Gold--Result"
author: "Wu Wei"
date: "2017-9-20"
output: html_document
---

## Synopsis


```{r library, echo = FALSE}
rm(list = ls())

suppressMessages(library(forecast))
suppressMessages(library(grid))
suppressMessages(library(gridExtra))
suppressMessages(library(ggplot2))
suppressMessages(library(FinTS))
suppressMessages(library(rugarch))
suppressMessages(library(fNonlinear))
suppressMessages(library(vars))
```

```{r source files, echo = FALSE}
setwd("d://MyR//stock//")

source("DrawMonthlyKDJDForecastPlot.R")
source("DrawWeeklyKDJDForecastPlot.R")
source("ReturnArimaRollingForecast.r")
```


### 1. Forecast result of monthly kdj k/d and monthly compound return

```{r main 1.1, echo = FALSE}


monthly.original.data <- read.csv("goldmonthly.csv")

monthly.close.price <- monthly.original.data[,5]

## The last month has not passed completely. So it is cancelled.
monthly.close.price <- monthly.close.price[-length(monthly.close.price)]

## start time: 1990.01.01
monthly.close.price <- ts(monthly.close.price, start = c(1990, 1), frequency = 12)
monthly.compound.return <- diff(log(monthly.close.price)) * 100

## when the last kdj is added manually and not real, it is removed
monthly.kdj.k <- monthly.original.data[,7]
monthly.kdj.d <- monthly.original.data[,8]
if(length(unique(tail(monthly.kdj.k,2))) == 1){
        monthly.kdj.k <- monthly.kdj.k[-length(monthly.kdj.k)]
        monthly.kdj.d <- monthly.kdj.d[-length(monthly.kdj.d)]
}

monthly.kdj.k <- ts(monthly.kdj.k, start = c(1990, 1), frequency = 12)
monthly.kdj.d <- ts(monthly.kdj.d, start = c(1990, 1), frequency = 12)
```

#### 1.1 Forecast result of monthly kdj k/d 

```{r main 1.2, fig.height=6, fig.width=10, echo = FALSE, cache=FALSE}

DrawMonthlyKDJDForecastPlot(monthly.close.price,
                            monthly.kdj.k,
                            monthly.kdj.d,
                            arg.forecast.period = 5,
                            arg.ylabel.offset = 80,
                            arg.xlim.offset = 80,
                            arg.date = monthly.original.data[, 1])
```

#### 1.2 Monthly Price Forecast 

```{r main 1.3, fig.height=6, fig.width=10, echo = FALSE, cache=TRUE}

## It is found that there is no significant difference between setting stepwise and approximation to true and false
## For the sake of simplicity, use default setting values (set to true)

fit.arima.monthly.return <- auto.arima(monthly.compound.return, seasonal = FALSE)


fc.arima.monthly.return <- forecast(fit.arima.monthly.return, h = 1, 
                              level = c(80,95))

```


```{r main 1.6, echo=FALSE}
### 2 sigma upper level
monthly.price.2.upper.level <- as.numeric(tail(monthly.close.price,1)) * exp((fc.arima.monthly.return$mean  + sqrt(fc.arima.monthly.return$model$sigma2) * 2) / 100)

### 1 sigma upper level
monthly.price.1.upper.level <- as.numeric(tail(monthly.close.price,1)) * exp((fc.arima.monthly.return$mean  + sqrt(fc.arima.monthly.return$model$sigma2)) / 100)

### close price last month
monthly.price.last.month <- as.numeric(tail(monthly.close.price,1))

### 1 sigma lower level
monthly.price.1.lower.level <- as.numeric(tail(monthly.close.price,1)) * exp((fc.arima.monthly.return$mean  - sqrt(fc.arima.monthly.return$model$sigma2)) / 100)

### 2 sigma lower level
monthly.price.2.lower.level <- as.numeric(tail(monthly.close.price,1)) * exp((fc.arima.monthly.return$mean  - sqrt(fc.arima.monthly.return$model$sigma2) * 2) / 100)


### the possibility that the price will descend next month

possibility.descend.next.month <- pnorm(0, mean = fc.arima.monthly.return$mean, 
      sd = sqrt(fc.arima.monthly.return$model$sigma2))

### the possibility that the price will ascend next month

possibility.ascend.next.month <- pnorm(0, mean = fc.arima.monthly.return$mean, 
      sd = sqrt(fc.arima.monthly.return$model$sigma2),
      lower.tail = FALSE)

```



```{r main 1.7,  fig.height=3, fig.width=4, echo=FALSE}
d <- data.frame(monthly.price.2.upper.level = round(monthly.price.2.upper.level,digits = 2),
                monthly.price.1.upper.level = round(monthly.price.1.upper.level,digits = 2),
                monthly.price.last.month = round(monthly.price.last.month,digits = 2),
                monthly.price.1.lower.level = round(monthly.price.1.lower.level,digits = 2),
                monthly.price.2.lower.level = round(monthly.price.2.lower.level,digits = 2),
                monthly.return.mean.forecast = paste0(round(fc.arima.monthly.return$mean,digits = 2),"%"),
                monthly.return.sigma.forecast = 
                        paste0(round(sqrt(fc.arima.monthly.return$model$sigma2),digits = 1),"%"),
                possibility.descend.next.month = 
                        paste0(round(possibility.descend.next.month * 100, digits = 1),"%"),
                possibility.ascend.next.month = 
                        paste0(round(possibility.ascend.next.month * 100,digits = 1),"%"))


g <- tableGrob(t(d))
grid.newpage()
grid.draw(g)
```

#### 1.3 Predictation of Recent months 


```{r appendix 1.3.2, fig.height=2, fig.width=9, echo = FALSE, cache=FALSE, eval=TRUE}

recent.month.count <- 5

recent.monthly.return <- round(tail(monthly.compound.return, recent.month.count),digits = 2)

## fit arima model using rolling data
recent.mean.sigma <- ReturnArimaRollingForecast(arg.object = monthly.compound.return, 
                           arg.rolling.period = recent.month.count)


month.flag.return.larger.than.sigma <- ((recent.monthly.return > recent.mean.sigma$mean + recent.mean.sigma$sigma) |
                          (recent.monthly.return < recent.mean.sigma$mean - recent.mean.sigma$sigma) )


d <- data.frame(recent.monthly.return = paste0(recent.monthly.return,"%"),
                mean.forecast = paste0(recent.mean.sigma$mean,"%"),
                sigma.forecast = paste0(recent.mean.sigma$sigma,"%"),
                absolute.return.larger.than.1.sigma = month.flag.return.larger.than.sigma)


start.year <- trunc(tsp(recent.monthly.return)[1])
start.month <- round((tsp(recent.monthly.return)[1] - start.year) / 0.0833333) + 1

row.names(d) <- paste0(start.year,"-",seq(from = start.month, length=recent.month.count))

g <- tableGrob(d)
grid.newpage()
grid.draw(g)
```

### 2. Forecast result of Weekly kdj k/d and Weekly compound return

```{r main 2.1, echo = FALSE}

weekly.original.data <- read.csv("goldweekly.csv")

weekly.close.price <- as.ts(weekly.original.data[,5])
weekly.kdj.k <- as.ts(weekly.original.data[,7])
weekly.kdj.d <- as.ts(weekly.original.data[,8])

names(weekly.close.price) <- weekly.original.data$Time
names(weekly.kdj.k) <- weekly.original.data$Time
names(weekly.kdj.d) <- weekly.original.data$Time

weekly.compound.return <- diff(log(weekly.close.price)) * 100

names(weekly.compound.return) <- weekly.original.data$Time[-1]
```

#### 2.1 Forecast result of weekly kdj k/d 

```{r main 2.2, fig.height=6, fig.width=10, echo = FALSE, cache=TRUE}

DrawWeeklyKDJDForecastPlot(weekly.close.price,
                           weekly.kdj.k,
                           weekly.kdj.d,
                           arg.forecast.period = 5,
                           arg.ylabel.offset = 80,
                           arg.xlim.offset = 80,
                           arg.regression.offset = 400,
                           arg.date = weekly.original.data[, 1])

```
        
#### 2.2 Weekly Price Forecast 

```{r main 2.3, fig.height=6, fig.width=10, echo = TRUE, cache=TRUE}
fit.arima.object <- auto.arima(weekly.compound.return[1:469], seasonal = FALSE) 

myspec.aparch.std.52.ver1 <- ugarchspec(variance.model = list(model = "apARCH",garchOrder = c(5,2)),
                                mean.model = list(armaOrder = c(fit.arima.object$arma[1],
                                                                fit.arima.object$arma[2])),
                                distribution.model = "std",
                                fixed.pars=list(beta1 = 0))

myfit.aparch.std.52.ver1 <- ugarchfit(myspec.aparch.std.52.ver1, data = weekly.compound.return[1:469], solver = "hybrid")


setfixed(myspec.aparch.std.52.ver1) <- as.list(coef(myfit.aparch.std.52.ver1))

suppressWarnings(fc.aparch.std.52.ver1 <- ugarchforecast(myspec.aparch.std.52.ver1,data = weekly.compound.return, n.ahead = 1))

```

```{r main 2.3(2), fig.height=6, fig.width=10, echo = TRUE, cache=TRUE}
## if the length is larger than 479, it is needed to select garch model again

## n.old in 5.1 section should also be modified in the above section
## fit.arima.object should also be modified in the above section 

length(weekly.compound.return)

```


```{r main 2.4, echo=FALSE}
### 2 sigma upper level
weekly.price.2.upper.level <- as.numeric(tail(weekly.close.price,1) * exp((fc.aparch.std.52.ver1@forecast$seriesFor  + 2 * fc.aparch.std.52.ver1@forecast$sigmaFor) / 100))

### 1 sigma upper level
weekly.price.1.upper.level <- as.numeric(tail(weekly.close.price,1) * exp((fc.aparch.std.52.ver1@forecast$seriesFor  + fc.aparch.std.52.ver1@forecast$sigmaFor) / 100))

### close price last week
weekly.price.last.week <- as.numeric(tail(weekly.close.price,1))

### 1 sigma lower level
weekly.price.1.lower.level <- as.numeric(tail(weekly.close.price,1) * exp((fc.aparch.std.52.ver1@forecast$seriesFor  - fc.aparch.std.52.ver1@forecast$sigmaFor) / 100))

### 2 sigma lower level
weekly.price.2.lower.level <- as.numeric(tail(weekly.close.price,1) * exp((fc.aparch.std.52.ver1@forecast$seriesFor  - 2 * fc.aparch.std.52.ver1@forecast$sigmaFor) / 100))


### the possibility that the price will descend next week

possibility.descend.next.week <- pnorm(0, mean = fc.aparch.std.52.ver1@forecast$seriesFor, 
      sd = fc.aparch.std.52.ver1@forecast$sigmaFor)

### the possibility that the price will ascend next week

possibility.ascend.next.week <- pnorm(0, mean = fc.aparch.std.52.ver1@forecast$seriesFor, 
      sd = fc.aparch.std.52.ver1@forecast$sigmaFor,
      lower.tail = FALSE)

```



```{r main 2.5,  fig.height=3, fig.width=4, echo=FALSE}
d <- data.frame(weekly.price.2.upper.level = round(weekly.price.2.upper.level,digits = 2),
                weekly.price.1.upper.level = round(weekly.price.1.upper.level,digits = 2),
                weekly.price.last.week = round(weekly.price.last.week,digits = 2),
                weekly.price.1.lower.level = round(weekly.price.1.lower.level,digits = 2),
                weekly.price.2.lower.level = round(weekly.price.2.lower.level,digits = 2),
                weekly.return.mean.forecast = 
                        paste0(round(fc.aparch.std.52.ver1@forecast$seriesFor,digits = 2),"%"),
                weekly.return.sigma.forecast = 
                        paste0(round(fc.aparch.std.52.ver1@forecast$sigmaFor,digits = 2),"%"),
                possibility.descend.next.week = 
                        paste0(round(possibility.descend.next.week * 100, digits = 2),"%"),
                possibility.ascend.next.week = 
                        paste0(round(possibility.ascend.next.week * 100,digits = 2),"%"))


g <- tableGrob(t(d))
grid.newpage()
grid.draw(g)
```

#### 2.3 Data of Recent weeks 
```{r main 2.3.1,  fig.height=3, fig.width=4, echo=FALSE}
## parameters in myspec.aparch.std.52.ver1 have been set fixed in the 2.3 section
## n.old should be same as the above setting for myfit.aparch.std.52.ver1

myfilter.aparch.std.52.ver1 <- ugarchfilter(myspec.aparch.std.52.ver1, weekly.compound.return, n.old = 469)
```


```{r appendix 2.3.2, fig.height=2, fig.width=9, echo = FALSE, cache=FALSE, eval=TRUE}
recent.week.count <- 5

recent.weekly.return <- round(tail(weekly.compound.return, recent.week.count),digits = 2)

## Since parameters in garch model are fixed, it is no need to fit garch model again
mean.forecast <- as.numeric(round(tail(fitted(myfilter.aparch.std.52.ver1),
                            recent.week.count),
                       digits = 2))

sigma.forecast <- as.numeric(round(tail(myfilter.aparch.std.52.ver1@filter$sigma,
                             recent.week.count),
                        digits = 2))


week.flag.return.larger.than.sigma <- ((recent.weekly.return > mean.forecast + sigma.forecast) |
                          (recent.weekly.return < mean.forecast - sigma.forecast) )


d <- data.frame(recent.weekly.return = paste0(recent.weekly.return,"%"),
                mean.forecast = paste0(mean.forecast,"%"),
                sigma.forecast = paste0(sigma.forecast,"%"),
                absolute.return.larger.than.1.sigma = week.flag.return.larger.than.sigma)

row.names(d) <- names(recent.weekly.return)

g <- tableGrob(d)
grid.newpage()
grid.draw(g)
```

## 3. Verification for Monthly Models 



```{r 3.0.1, cache=FALSE, eval=TRUE}

fit.arima.monthly.kdj.d <- auto.arima(monthly.kdj.d,
                              max.order = 5,
                              seasonal = FALSE,
                              stepwise = FALSE,
                              approximation = FALSE)

fit.arima.monthly.kdj.k <- auto.arima(monthly.kdj.k,
                              max.order = 5,
                              seasonal = FALSE,
                              d = 0,
                              stepwise = FALSE,
                              approximation = FALSE)

```

```{r 3.0.2, cache=FALSE, eval=TRUE}

monthly.kdj <- cbind(monthly.kdj.k, monthly.kdj.d)

var <- VAR(monthly.kdj, p=1, type="const", lag.max = 5, ic = "SC" )

## if max mod of roots is larger than 1, auto.arima is enabled
max(Mod(roots(var)))

var$p

```


### 3.1 White Noise Test


```{r 3.1.1, cache=FALSE, eval=TRUE}

Box.test(residuals(fit.arima.monthly.kdj.d), lag=10, fitdf=sum(fit.arima.monthly.kdj.d$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.monthly.kdj.k), lag=10, fitdf=sum(fit.arima.monthly.kdj.k$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.monthly.return), lag=10, fitdf=sum(fit.arima.monthly.return$arma[c(1,2)]), type = "Lj")

```

```{r 3.1.2, cache=FALSE, eval=TRUE}

serial.test(var, lags.pt=10, type="PT.asymptotic")
```


### 3.2  Relationship Between Residuals And Time

```{r main 3.2.1, fig.height=6, fig.width=10, cache=FALSE, eval=TRUE}
plot(residuals(fit.arima.monthly.kdj.d), axes = TRUE, main = "Arima( Monthly KDJ.D )")
abline(h = 0, col = "red")

plot(residuals(fit.arima.monthly.kdj.k), axes = TRUE, main = "Arima( Monthly KDJ.K )")
abline(h = 0, col = "red")

plot(residuals(fit.arima.monthly.return), axes = TRUE, main = "Arima( Monthly Return )")
abline(h = 0, col = "red")
```

```{r main 3.2.2, fig.height=6, fig.width=10, cache=FALSE, eval=TRUE}
plot(residuals(var)[,"monthly.kdj.k"], main = "VAR( monthly.kdj.k )")
abline(h = 0, col = "red")

```


### 3.3 Relationship Between Residuals And Fitted Value

```{r main 3.3.1, fig.height=6, fig.width=10, eval=TRUE}

plot(as.numeric(residuals(fit.arima.monthly.kdj.d)) ~ as.numeric(fitted(fit.arima.monthly.kdj.d)),
     main = "Arima( Monthly KDJ.D )")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.arima.monthly.kdj.k)) ~ as.numeric(fitted(fit.arima.monthly.kdj.k)),
     main = "Arima( Monthly KDJ.K )")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.arima.monthly.return)) ~ as.numeric(fitted(fit.arima.monthly.return)),
     main = "Arima( Monthly Price )")
abline(h = 0, col = "red")

```

```{r main 3.3.2, fig.height=6, fig.width=10, eval=TRUE}
plot(as.numeric(residuals(var)[,"monthly.kdj.k"]) ~ as.numeric(fitted(var)[,"monthly.kdj.k"]),
     main = "VAR( Monthly KDJ.K )")
abline(h = 0, col = "red")

```


### 3.4 Normality of Residuals

```{r 3.4.1, fig.height=6, fig.width=10, eval=TRUE}

qqnorm(residuals(fit.arima.monthly.kdj.d), main = "Arima( Monthly KDJ.D )")
qqline(residuals(fit.arima.monthly.kdj.d))

qqnorm(residuals(fit.arima.monthly.kdj.k), main = "Arima( Monthly KDJ.K )")
qqline(residuals(fit.arima.monthly.kdj.k))

qqnorm(residuals(fit.arima.monthly.return), main = "Arima( Monthly Return )")
qqline(residuals(fit.arima.monthly.return))

```

```{r 3.4.2, fig.height=6, fig.width=10, eval=TRUE}
qqnorm(residuals(var)[,"monthly.kdj.k"], main = "VAR( Monthly KDJ.K )")
qqline(residuals(var)[,"monthly.kdj.k"])


```

### 3.5 ARCH Effect Test


```{r 3.5.1, eval=TRUE}

Box.test((residuals(fit.arima.monthly.kdj.d))^2, lag=10, fitdf=sum(fit.arima.monthly.kdj.d$arma[c(1,2)]), type = "Lj")
ArchTest(residuals(fit.arima.monthly.kdj.d))

Box.test((residuals(fit.arima.monthly.kdj.k))^2, lag=10, fitdf=sum(fit.arima.monthly.kdj.k$arma[c(1,2)]), type = "Lj")
ArchTest(residuals(fit.arima.monthly.kdj.k))

Box.test((residuals(fit.arima.monthly.return))^2, lag=10, fitdf=sum(fit.arima.monthly.return$arma[c(1,2)]), type = "Lj")
ArchTest(residuals(fit.arima.monthly.return))


```

```{r 3.5.2, eval=TRUE}
ArchTest(residuals(var)[,"monthly.kdj.k"])
```


### 3.6 Non-Linear Test

#### 3.6.1  BDS Test

```{r Monthly Verification 3.6.1, eval=TRUE}
# iid test

bdsTest(residuals(fit.arima.monthly.kdj.d), m = 3)
bdsTest(residuals(fit.arima.monthly.kdj.k), m = 3)
bdsTest(residuals(fit.arima.monthly.return), m = 3)

```

#### 3.6.2  Runs Test

```{r Monthly Verification 3.6.2, eval=TRUE}
# random process test

runsTest(residuals(fit.arima.monthly.kdj.d))
runsTest(residuals(fit.arima.monthly.kdj.k))
runsTest(residuals(fit.arima.monthly.return))
```

#### 3.6.3  Teraesvirta Neural Network Test
```{r Monthly Verification 3.6.3, eval=TRUE}
# mean linearity test

tnnTest(monthly.kdj.d)
tnnTest(monthly.kdj.k)
tnnTest(monthly.compound.return)

```

#### 3.6.4  White Neural Network Test
```{r Monthly Verification 3.6.4, eval=TRUE}
# mean linearity test

wnnTest(monthly.kdj.d)
wnnTest(monthly.kdj.k)
wnnTest(monthly.compound.return)

```


## 4. Verification for Weekly Kdj Models 

```{r weekly Verification--Model, cache=FALSE, eval=TRUE}

weekly.kdj.d.data <- window(weekly.kdj.d, start = length(weekly.kdj.d) - 400)
weekly.kdj.k.data <- window(weekly.kdj.k, start = length(weekly.kdj.k) - 400)


fit.arima.weekly.kdj.d <- auto.arima(weekly.kdj.d.data,
                              max.order = 5,
                              d = 0,
                              stepwise = FALSE,
                              approximation = FALSE)

fit.arima.weekly.kdj.k <- auto.arima(weekly.kdj.k.data,
                              max.order = 5,
                              d = 0,
                              stepwise = FALSE,
                              approximation = FALSE)



```


### 4.1 White Noise Test


```{r 4.1, cache=FALSE, eval=TRUE}

Box.test(residuals(fit.arima.weekly.kdj.d), lag=10, fitdf=sum(fit.arima.weekly.kdj.d$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.weekly.kdj.k), lag=10, fitdf=sum(fit.arima.weekly.kdj.k$arma[c(1,2)]), type = "Lj")

```

### 4.2  Relationship Between Residuals And Time

```{r main 4.2, fig.height=6, fig.width=10, cache=FALSE, eval=TRUE}

plot(residuals(fit.arima.weekly.kdj.d), axes = TRUE, main = "Arima( Weekly KDJ.D )")
abline(h = 0, col = "red")

plot(residuals(fit.arima.weekly.kdj.k), axes = TRUE, main = "Arima( Weekly KDJ.K )")
abline(h = 0, col = "red")

```

### 4.3 Relationship Between Residuals And Fitted Value

```{r main 4.3, fig.height=6, fig.width=10, eval=TRUE}

plot(as.numeric(residuals(fit.arima.weekly.kdj.d)) ~ as.numeric(fitted(fit.arima.weekly.kdj.d)),
     main = "Arima( Weekly KDJ.D )")
abline(h = 0, col = "red")

plot(as.numeric(residuals(fit.arima.weekly.kdj.k)) ~ as.numeric(fitted(fit.arima.weekly.kdj.k)),
     main = "Arima( Weekly KDJ.K )")
abline(h = 0, col = "red")

```


### 4.4 Normality of Residuals

```{r main 4.4, fig.height=6, fig.width=10, eval=TRUE}

qqnorm(residuals(fit.arima.weekly.kdj.d), main = "Arima( Weekly KDJ.D )")
qqline(residuals(fit.arima.weekly.kdj.d))

qqnorm(residuals(fit.arima.weekly.kdj.k), main = "Arima( Weekly KDJ.K )")
qqline(residuals(fit.arima.weekly.kdj.k))

```

### 4.5 ARCH Effect Test


```{r main 4.5, eval=TRUE}

Box.test((residuals(fit.arima.weekly.kdj.d))^2, lag=10, fitdf=sum(fit.arima.weekly.kdj.d$arma[c(1,2)]), type = "Lj")
ArchTest(residuals(fit.arima.weekly.kdj.d))

Box.test((residuals(fit.arima.weekly.kdj.k))^2, lag=10, fitdf=sum(fit.arima.weekly.kdj.k$arma[c(1,2)]), type = "Lj")
ArchTest(residuals(fit.arima.weekly.kdj.k))

```

### 4.6 Non-Linear Test

#### 4.6.1 BDS Test

```{r Weekly Verification 4.6.1, eval=TRUE}
# iid test 

bdsTest(residuals(fit.arima.weekly.kdj.d), m = 3)
bdsTest(residuals(fit.arima.weekly.kdj.k), m = 3)

```

#### 4.6.2 Runs Test

```{r Weekly Verification 4.6.2, eval=TRUE}
# random process test

runsTest(residuals(fit.arima.weekly.kdj.d))
runsTest(residuals(fit.arima.weekly.kdj.k))

```

#### 4.6.3  Teraesvirta Neural Network Test
```{r Weekly Verification 4.6.3, eval=TRUE}
# mean linearity test

tnnTest(weekly.kdj.d.data)
tnnTest(weekly.kdj.k.data)

```

#### 4.6.4  White Neural Network Test
```{r Weekly Verification 4.6.4, eval=TRUE}
# mean linearity test

wnnTest(weekly.kdj.d.data)
wnnTest(weekly.kdj.k.data)

```



## 5. Verification for Weekly Compound Return Model 

```{r 5.1, cache=FALSE, eval=TRUE}



show(myfilter.aparch.std.52.ver1)

```


```{r appendix 5.2, fig.height=8, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
plot(myfilter.aparch.std.52.ver1, which = 1)
```

```{r appendix 5.3, fig.height=8, fig.width=10, echo = FALSE, cache=FALSE, eval=FALSE}
# plot(myfilter.aparch.std.52.ver1, which = 2)
```

```{r appendix 5.4, fig.height=8, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
plot(myfilter.aparch.std.52.ver1, which = 3)
```


```{r appendix 5.5, fig.height=8, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
plot(myfilter.aparch.std.52.ver1, which = 9)
```

```{r appendix 5.6, fig.height=8, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
plot(myfilter.aparch.std.52.ver1, which = 10)
```

```{r appendix 5.7, fig.height=8, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
plot(myfilter.aparch.std.52.ver1, which = 11)
```

```{r appendix 5.8, fig.height=8, fig.width=10, echo = TRUE, cache=FALSE, eval=TRUE}
plot(myfilter.aparch.std.52.ver1, which = 12)
```

### 5.1 Non-Linear Test

#### 5.1.1 BDS Test

```{r Weekly Verification 5.1.1, eval=TRUE}
# iid test

bdsTest(as.ts(residuals(myfilter.aparch.std.52.ver1, standard = TRUE)), m = 3)

```

#### 5.1.2 Runs Test

```{r Weekly Verification 5.1.2, eval=TRUE}
# random process test

runsTest(as.ts(residuals(myfilter.aparch.std.52.ver1, standard = TRUE)))

```


#### 5.1.3  Teraesvirta Neural Network Test
```{r Monthly Verification 5.1.3, eval=TRUE}
# mean linearity test

tnnTest(weekly.compound.return)

```

#### 5.1.4  White Neural Network Test
```{r Monthly Verification 5.1.4, eval=TRUE}
# mean linearity test

wnnTest(weekly.compound.return)

```
