---
title: "ARIMA+Garch Prediction Of monthly Gold close.price----Appendix D"
author: "Wu Wei"
date: "2017-4-6"
output: html_document
---

## 1. Preparation


```{r Appendix 1.1, echo = FALSE}
suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
suppressMessages(library(rugarch))
suppressMessages(library(tseries))
suppressMessages(library(fBasics))

```



```{r Appendix 1.2, fig.height=8, fig.width=10}
rm(list = ls())

setwd("d://MyR//stock//")
monthly.original.data <- read.csv("goldmonthly.csv")

monthly.close.price <- monthly.original.data[,5]

training.set <- head(monthly.close.price, length(monthly.close.price) - 20)

# tsdisplay(training.set)
```

```{r Appendix 1.3}
mean(training.set)
sd(training.set)
skewness(training.set)
kurtosis(training.set)
jarqueberaTest(training.set)

```

## 2 Comparison of monthly Models 

```{r Appendix 2.1, echo = TRUE, cache=TRUE}
source("CompareGarchAic.r")

CompareGarchAic(training.set, arg.difference = 1)

```

```{r appendix 2.2, echo = TRUE, cache=FALSE, eval=TRUE}
source("CompareObjectAccuracy.R")

comparison.period <- 20

forecast.period <- 5

training.set.endpoint <- length(monthly.close.price) - comparison.period - forecast.period

maxorder <- 5
```

```{r appendix 2.2(2), echo = TRUE, cache=TRUE, eval=TRUE}


result.arima.close.price <- CompareObjectAccuracy(arg.object = monthly.close.price,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```


```{r Appendix 2.2(3), echo = TRUE, cache=TRUE, eval=TRUE}
source("CompareGarchsignbias.r")

signbias.sGarchnorm <- CompareGarchsignbias(arg.object = diff(monthly.close.price),
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "norm")
print(signbias.sGarchnorm)

```

The leverage effect of the standardized residuals is not significant. So gjrGARCH/eGARCH/apGARCH are not used for modelling.

```{r Appendix 2.2(4), echo = TRUE, cache=TRUE, eval=FALSE}
source("CompareGarchgof.r")

gof.sGarchnorm <- CompareGarchgof(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "norm")
print(gof.sGarchnorm)

```

So, norm distribution assumption can be accepted.

```{r Appendix 2.2(5), echo = TRUE, cache=TRUE, eval=FALSE}
source("CompareGarchgof.r")

gof.sGarchsnorm <- CompareGarchgof(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "snorm")
print(gof.sGarchsnorm)

```

So, snorm distribution assumption can be accepted.

```{r Appendix 2.2(6), echo = TRUE, cache=TRUE, eval=FALSE}
source("CompareGarchgof.r")

gof.sGarchstd <- CompareGarchgof(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "std")
print(gof.sGarchstd)

```

So, std distribution assumption can be accepted.

```{r Appendix 2.2(7), echo = TRUE, cache=TRUE, eval=FALSE}
source("CompareGarchgof.r")

gof.sGarchsstd <- CompareGarchgof(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "sstd")
print(gof.sGarchsstd)

```

So, sstd distribution assumption can be accepted.

```{r Appendix 2.2(8), echo = TRUE, cache=TRUE, eval=FALSE}
source("CompareGarchgof.r")

gof.sGarchged <- CompareGarchgof(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "ged")
print(gof.sGarchged)

```

So, ged distribution assumption can be accepted.

```{r Appendix 2.2(9), echo = TRUE, cache=TRUE, eval=FALSE}
source("CompareGarchgof.r")

gof.sGarchsged <- CompareGarchgof(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "sged")
print(gof.sGarchsged)

```

So, sged distribution assumption can be accepted.

## 3 Back test of monthly Models 

```{r appendix 3.1, echo = TRUE, cache=FALSE, eval=FALSE}
source("CompareGarchAccuracy.R")


```


```{r appendix 3.2, echo = TRUE, cache=TRUE, eval=FALSE}


result.iGarchsged.close.price <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "sged")
```

```{r appendix 3.2(1), echo = TRUE, cache=TRUE, eval=FALSE}


result.sGarchsged.close.price <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "sged")
```


```{r appendix 3.2(2), echo = TRUE, cache=TRUE, eval=FALSE}


result.iGarchged.close.price <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "ged")
```

```{r appendix 3.2(3), echo = TRUE, cache=TRUE, eval=FALSE}


result.sGarchged.close.price <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "ged")
```


```{r appendix 3.3, echo = TRUE, cache=TRUE, eval=FALSE}


result.iGarchnorm.close.price <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "norm")
```

```{r appendix 3.3(1), echo = TRUE, cache=TRUE, eval=FALSE}


result.sGarchnorm.close.price <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "norm")
```


```{r appendix 3.3(2), echo = TRUE, cache=TRUE, eval=FALSE}


result.iGarchsnorm.close.price <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "snorm")
```

```{r appendix 3.3(22), echo = TRUE, cache=TRUE, eval=FALSE}


result.sGarchsnorm.close.price <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "snorm")
```


```{r appendix 3.3(3), echo = TRUE, cache=TRUE, eval=FALSE}


result.iGarchstd.close.price <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "std")
```

```{r appendix 3.3(32), echo = TRUE, cache=TRUE, eval=FALSE}


result.sGarchstd.close.price <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "std")
```


```{r appendix 3.3(4), echo = TRUE, cache=TRUE, eval=FALSE}


result.iGarchsstd.close.price <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "sstd")
```

```{r appendix 3.3(42), echo = TRUE, cache=TRUE, eval=FALSE}


result.sGarchsstd.close.price <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "sstd")
```


```{r appendix 3.3(5), echo = TRUE, cache=FALSE, eval=FALSE}

rmse.name <- c("iGarchsged",
               "iGarchged",
               "iGarchnorm",
               "iGarchsnorm",
               "iGarchstd",
               "iGarchsstd",
               "sGarchsged",
               "sGarchged",
               "sGarchnorm",
               "sGarchsnorm",
               "sGarchstd",
               "sGarchsstd")

rmseBT.count <- c(sum(result.iGarchsged.close.price$RMSE > result.arima.close.price$RMSE),
                sum(result.iGarchged.close.price$RMSE > result.arima.close.price$RMSE),
                sum(result.iGarchnorm.close.price$RMSE > result.arima.close.price$RMSE),
                sum(result.iGarchsnorm.close.price$RMSE > result.arima.close.price$RMSE),
                sum(result.iGarchstd.close.price$RMSE > result.arima.close.price$RMSE),
                sum(result.iGarchsstd.close.price$RMSE > result.arima.close.price$RMSE),
                
                sum(result.sGarchsged.close.price$RMSE > result.arima.close.price$RMSE),
                sum(result.sGarchged.close.price$RMSE > result.arima.close.price$RMSE),
                sum(result.sGarchnorm.close.price$RMSE > result.arima.close.price$RMSE),
                sum(result.sGarchsnorm.close.price$RMSE > result.arima.close.price$RMSE),
                sum(result.sGarchstd.close.price$RMSE > result.arima.close.price$RMSE),
                sum(result.sGarchsstd.close.price$RMSE > result.arima.close.price$RMSE))

rmse.meanvalue <- c(mean(result.iGarchsged.close.price$RMSE),
                mean(result.iGarchged.close.price$RMSE),
                mean(result.iGarchnorm.close.price$RMSE),
                mean(result.iGarchsnorm.close.price$RMSE),
                mean(result.iGarchstd.close.price$RMSE),
                mean(result.iGarchsstd.close.price$RMSE),
                
                mean(result.sGarchsged.close.price$RMSE),
                mean(result.sGarchged.close.price$RMSE),
                mean(result.sGarchnorm.close.price$RMSE),
                mean(result.sGarchsnorm.close.price$RMSE),
                mean(result.sGarchstd.close.price$RMSE),
                mean(result.sGarchsstd.close.price$RMSE))

rmse.df <- data.frame(name = rmse.name, CountrmseBTarima = rmseBT.count, meanvalue = rmse.meanvalue)


print(rmse.df[order(rmse.df$CountrmseBTarima),])


```

#### 4 Final comparison of pure Arima model with Garch models

```{r appendix 4.1, echo = TRUE, cache=TRUE, eval=FALSE}

comparison.period <- 50
training.set.endpoint <- length(monthly.close.price) - comparison.period - forecast.period

result.arima.close.price.50 <- CompareObjectZeroDiffAccuracy(arg.object = monthly.close.price,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 4.1(2), echo = TRUE, cache=TRUE, eval=FALSE}


result.iGarchsstd.close.price.50 <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price.50,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "sstd")
```

```{r appendix 4.1(3), echo = TRUE, cache=TRUE, eval=FALSE}


result.sGarchsstd.close.price.50 <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price.50,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "sstd")
```

```{r appendix 4.1(4), echo = TRUE, cache=TRUE, eval=FALSE}


result.iGarchsged.close.price.50 <- CompareGarchAccuracy(arg.object = monthly.close.price,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima.close.price = result.arima.close.price.50,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "sged")
```


```{r appendix 4.2, echo = TRUE, cache=FALSE, eval=FALSE}
t.test(result.iGarchsstd.close.price.50$RMSE - result.arima.close.price.50$RMSE)

summary(result.iGarchsstd.close.price.50$RMSE)

summary(result.arima.close.price.50$RMSE)

final.result.close.price <- cbind(result.arima.close.price.50, result.iGarchsstd.close.price.50)


final.result.close.price <- final.result.close.price[, -c(8)]

colnames(final.result.close.price) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                            "p","q", "RMSE.iGarchsstd")

print(final.result.close.price)

sum(final.result.close.price$RMSE.arima > final.result.close.price$RMSE.iGarchsstd)

sum(final.result.close.price$p.v >= 0.05)


```

```{r appendix 4.2(2), echo = TRUE, cache=FALSE, eval=FALSE}
t.test(result.sGarchsstd.close.price.50$RMSE - result.arima.close.price.50$RMSE)

summary(result.sGarchsstd.close.price.50$RMSE)

summary(result.arima.close.price.50$RMSE)

final.result.close.price <- cbind(result.arima.close.price.50, result.sGarchsstd.close.price.50)


final.result.close.price <- final.result.close.price[, -c(8)]

colnames(final.result.close.price) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                            "p","q", "RMSE.sGarchsstd")

print(final.result.close.price)

sum(final.result.close.price$RMSE.arima > final.result.close.price$RMSE.sGarchsstd)

sum(final.result.close.price$p.v >= 0.05)


```

```{r appendix 4.2(3), echo = TRUE, cache=FALSE, eval=FALSE}
t.test(result.iGarchsged.close.price.50$RMSE - result.arima.close.price.50$RMSE)

summary(result.iGarchsged.close.price.50$RMSE)

summary(result.arima.close.price.50$RMSE)

final.result.close.price <- cbind(result.arima.close.price.50, result.iGarchsged.close.price.50)


final.result.close.price <- final.result.close.price[, -c(8)]

colnames(final.result.close.price) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                            "p","q", "RMSE.iGarchsged")

print(final.result.close.price)

sum(final.result.close.price$RMSE.arima > final.result.close.price$RMSE.iGarchsged)

sum(final.result.close.price$p.v >= 0.05)


```

There is no obvious advantage to use Garch model for predicting monthly close.price.
