---
title: "ARIMA+Garch Prediction Of weekly Gold kdjk----Appendix C"
author: "Wu Wei"
date: "2017-4-1"
output: html_document
---

## 0. Preparation


```{r Appendix 0.1, echo = FALSE}
suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
suppressMessages(library(rugarch))
suppressMessages(library(tseries))
suppressMessages(library(fBasics))
suppressMessages(library(FinTS))

```



```{r Appendix 0.2, fig.height=8, fig.width=10}
rm(list = ls())

setwd("d://MyR//stock//")
weekly.original.data <- read.csv("goldweekly.csv")

weekly.kdj.k <- as.ts(tail(weekly.original.data[,7], 500))

training.set <- head(weekly.kdj.k, 480)

# tsdisplay(training.set)
```

```{r Appendix 0.3}
mean(training.set)
sd(training.set)
skewness(training.set)
kurtosis(training.set)
jarqueberaTest(training.set)

```

## 1 Enfluence on Models of different training set 

```{r Appendix 1.1}
source("CompareGarchAic.r")
```

```{r Appendix 1.2, echo = TRUE, cache=TRUE}
training.set.450 <- head(weekly.kdj.k, 450)
CompareGarchAic(training.set.450, arg.difference = 0)

```


```{r Appendix 1.3, echo = TRUE, cache=TRUE, eval=TRUE}
training.set.460 <- head(weekly.kdj.k, 460)
CompareGarchAic(training.set.460, arg.difference = 0)

```


```{r Appendix 1.4, echo = TRUE, cache=TRUE, eval=TRUE}
training.set.470 <- head(weekly.kdj.k, 470)
CompareGarchAic(training.set.470, arg.difference = 0)

```


```{r Appendix 1.5, echo = TRUE, cache=TRUE, eval=TRUE}
training.set.480 <- head(weekly.kdj.k, 480)
CompareGarchAic(training.set.480, arg.difference = 0)

```

gjrgarch.norm and gjrgarch.sstd should be noticed.

```{r Appendix 1.6, echo = TRUE, cache=TRUE, eval=TRUE}
training.set.490 <- head(weekly.kdj.k, 490)
CompareGarchAic(training.set.490, arg.difference = 0)

```


## 2 Comparison of Weekly Models 
```{r appendix 2.2}
source("CompareObjectZeroDiffAccuracy.R")

comparison.period <- 20

forecast.period <- 5

training.set.endpoint <- length(weekly.kdj.k) - comparison.period - forecast.period

maxorder <- 5
```

```{r appendix 2.2(2), echo = TRUE, cache=TRUE, eval=TRUE}


result.arima.kdj.k <- CompareObjectZeroDiffAccuracy(arg.object = weekly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```



```{r Appendix 2.2(3)}
source("CompareGarchsignbias.r")
```

```{r Appendix 2.2(31), echo = TRUE, cache=TRUE, eval=TRUE}
signbias.sGarchnorm <- CompareGarchsignbias(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "norm")
print(signbias.sGarchnorm)

```

The leverage effect of the standardized residuals is not significant. So eGARCH/apGARCH are not used for modelling.

```{r Appendix 2.2(32)}
source("CompareGarchnyblom.r")
```

```{r Appendix 2.2(321), echo = TRUE, cache=TRUE, eval=TRUE}
nyblom.sGarchnorm <- CompareGarchnyblom(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "norm")

nyblom.sGarchnorm <- round(nyblom.sGarchnorm, digits = 2)
print(nyblom.sGarchnorm)

```


```{r Appendix 2.2(331), echo = TRUE, cache=TRUE, eval=TRUE}
nyblom.sGarchstd <- CompareGarchnyblom(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "std")

nyblom.sGarchstd <- round(nyblom.sGarchstd, digits = 2)
print(nyblom.sGarchstd)

```

```{r Appendix 2.2(34), echo = TRUE, cache=TRUE, eval=TRUE}

nyblom.sGarchged <- CompareGarchnyblom(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "ged")

nyblom.sGarchged <- round(nyblom.sGarchged, digits = 2)
print(nyblom.sGarchged)

```


```{r Appendix 2.2(4)}
source("CompareGarchgof.r")

```


```{r Appendix 2.2(41), echo = TRUE, cache=TRUE, eval=TRUE}

gof.sGarchnorm <- CompareGarchgof(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "norm")
print(gof.sGarchnorm)

```

So, norm distribution assumption can be accepted.


```{r Appendix 2.2(5), echo = TRUE, cache=TRUE, eval=TRUE}
gof.sGarchsnorm <- CompareGarchgof(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "snorm")
print(gof.sGarchsnorm)

```

So, snorm distribution assumption can be accepted.

```{r Appendix 2.2(6), echo = TRUE, cache=TRUE, eval=TRUE}

gof.sGarchstd <- CompareGarchgof(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "std")
print(gof.sGarchstd)

```

So, std distribution assumption can be accepted.

```{r Appendix 2.2(7), echo = TRUE, cache=TRUE, eval=TRUE}

gof.sGarchsstd <- CompareGarchgof(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "sstd")
print(gof.sGarchsstd)

```

So, sstd distribution assumption can be accepted.

```{r Appendix 2.2(8), echo = TRUE, cache=TRUE, eval=TRUE}

gof.sGarchged <- CompareGarchgof(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "ged")
print(gof.sGarchged)

```

So, ged distribution assumption can be accepted.

```{r Appendix 2.2(9), echo = TRUE, cache=TRUE, eval=TRUE}

gof.sGarchsged <- CompareGarchgof(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "sged")
print(gof.sGarchsged)

```

So, sged distribution assumption can be accepted.

## 3 Back test of Weekly Models 

```{r appendix 3.1}
source("CompareGarchAccuracy.R")


```


```{r appendix 3.2, echo = TRUE, cache=TRUE, eval=TRUE}


result.iGarchsged.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "sged")
```

```{r appendix 3.2(1), echo = TRUE, cache=TRUE, eval=TRUE}


result.sGarchsged.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "sged")
```


```{r appendix 3.2(2), echo = TRUE, cache=TRUE, eval=TRUE}


result.iGarchged.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "ged")
```

```{r appendix 3.2(3), echo = TRUE, cache=TRUE, eval=TRUE}


result.sGarchged.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "ged")
```


```{r appendix 3.3, echo = TRUE, cache=TRUE, eval=TRUE}


result.iGarchnorm.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "norm")
```

```{r appendix 3.3(1), echo = TRUE, cache=TRUE, eval=TRUE}


result.sGarchnorm.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "norm")
```

```{r appendix 3.3(11), echo = TRUE, cache=TRUE, eval=TRUE}


result.gjrGarchnorm.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "gjrGARCH",
                                                  arg.dist.model = "norm")
```


```{r appendix 3.3(2), echo = TRUE, cache=TRUE, eval=TRUE}


result.iGarchsnorm.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "snorm")
```

```{r appendix 3.3(22), echo = TRUE, cache=TRUE, eval=TRUE}


result.sGarchsnorm.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "snorm")
```


```{r appendix 3.3(3), echo = TRUE, cache=TRUE, eval=TRUE}


result.iGarchstd.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "std")
```

```{r appendix 3.3(32), echo = TRUE, cache=TRUE, eval=TRUE}


result.sGarchstd.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "std")
```


```{r appendix 3.3(4), echo = TRUE, cache=TRUE, eval=TRUE}


result.iGarchsstd.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "sstd")
```

```{r appendix 3.3(42), echo = TRUE, cache=TRUE, eval=TRUE}


result.sGarchsstd.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "sstd")
```

```{r appendix 3.3(41), echo = TRUE, cache=TRUE, eval=TRUE}


result.gjrGarchsstd.kdj.k <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k,
                                                  arg.var.model = "gjrGARCH",
                                                  arg.dist.model = "sstd")
```


```{r appendix 3.3(5)}

rmse.name <- c("iGarchsged",
               "iGarchged",
               "iGarchnorm",
               "iGarchsnorm",
               "iGarchstd",
               "iGarchsstd",
               "sGarchsged",
               "sGarchged",
               "sGarchnorm",
               "sGarchsnorm",
               "sGarchstd",
               "sGarchsstd",
               "gjrGarchnorm",
               "gjrGarchsstd")

rmseBT.count <- c(sum(result.iGarchsged.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                sum(result.iGarchged.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                sum(result.iGarchnorm.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                sum(result.iGarchsnorm.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                sum(result.iGarchstd.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                sum(result.iGarchsstd.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                
                sum(result.sGarchsged.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                sum(result.sGarchged.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                sum(result.sGarchnorm.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                sum(result.sGarchsnorm.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                sum(result.sGarchstd.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                sum(result.sGarchsstd.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                
                sum(result.gjrGarchnorm.kdj.k$RMSE > result.arima.kdj.k$RMSE),
                sum(result.gjrGarchsstd.kdj.k$RMSE > result.arima.kdj.k$RMSE))

rmse.meanvalue <- c(mean(result.iGarchsged.kdj.k$RMSE),
                mean(result.iGarchged.kdj.k$RMSE),
                mean(result.iGarchnorm.kdj.k$RMSE),
                mean(result.iGarchsnorm.kdj.k$RMSE),
                mean(result.iGarchstd.kdj.k$RMSE),
                mean(result.iGarchsstd.kdj.k$RMSE),
                
                mean(result.sGarchsged.kdj.k$RMSE),
                mean(result.sGarchged.kdj.k$RMSE),
                mean(result.sGarchnorm.kdj.k$RMSE),
                mean(result.sGarchsnorm.kdj.k$RMSE),
                mean(result.sGarchstd.kdj.k$RMSE),
                mean(result.sGarchsstd.kdj.k$RMSE),
                
                mean(result.gjrGarchnorm.kdj.k$RMSE),
                mean(result.gjrGarchsstd.kdj.k$RMSE))

rmse.df <- data.frame(name = rmse.name, CountrmseBTarima = rmseBT.count, meanvalue = round(rmse.meanvalue,digits = 2))


print(rmse.df[order(rmse.df$CountrmseBTarima, rmse.df$meanvalue),])

round(mean(result.arima.kdj.k$RMSE), digits = 2)

```

#### 4 Final comparison of pure Arima model with Garch models for 50 steps

```{r appendix 4.1, echo = TRUE, cache=TRUE, eval=TRUE}

comparison.period <- 50
training.set.endpoint <- length(weekly.kdj.k) - comparison.period - forecast.period

result.arima.kdj.k.50 <- CompareObjectZeroDiffAccuracy(arg.object = weekly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 4.1(2), echo = TRUE, cache=TRUE, eval=TRUE}


result.iGarchged.kdj.k.50 <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k.50,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "ged")
```

```{r appendix 4.1(3), echo = TRUE, cache=TRUE, eval=TRUE}


result.sGarchged.kdj.k.50 <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k.50,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "ged")
```

```{r appendix 4.1(4), echo = TRUE, cache=TRUE, eval=TRUE}


result.iGarchsged.kdj.k.50 <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k.50,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "sged")
```

```{r appendix 4.1(g), echo = TRUE, cache=TRUE, eval=TRUE}


result.gjrGarchnorm.kdj.k.50 <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k.50,
                                                  arg.var.model = "gjrGARCH",
                                                  arg.dist.model = "norm")
```

```{r appendix 4.1(6)}

rmse.name <- c("iGarchsged",
               "iGarchged",
               "sGarchged",
               "gjrGarchnorm")

rmseBT.count <- c(sum(result.iGarchsged.kdj.k.50$RMSE > result.arima.kdj.k.50$RMSE),
                  sum(result.iGarchged.kdj.k.50$RMSE > result.arima.kdj.k.50$RMSE),
                  sum(result.sGarchged.kdj.k.50$RMSE > result.arima.kdj.k.50$RMSE),
                  sum(result.gjrGarchnorm.kdj.k.50$RMSE > result.arima.kdj.k.50$RMSE))

rmse.meanvalue <- c(mean(result.iGarchsged.kdj.k.50$RMSE),
                    mean(result.iGarchged.kdj.k.50$RMSE),
                    mean(result.sGarchged.kdj.k.50$RMSE),
                    mean(result.gjrGarchnorm.kdj.k.50$RMSE))

rmse.df <- data.frame(name = rmse.name, CountrmseBTarima = rmseBT.count, meanvalue = round(rmse.meanvalue,digits = 2))


print(rmse.df[order(rmse.df$CountrmseBTarima, rmse.df$meanvalue),])

round(mean(result.arima.kdj.k.50$RMSE), digits = 2)

```



```{r appendix 4.2, echo = TRUE, cache=FALSE, eval=TRUE}
t.test(result.iGarchged.kdj.k.50$RMSE - result.arima.kdj.k.50$RMSE)

summary(result.iGarchged.kdj.k.50$RMSE)

summary(result.arima.kdj.k.50$RMSE)

final.result.kdj.k <- cbind(result.arima.kdj.k.50, result.iGarchged.kdj.k.50)


final.result.kdj.k <- final.result.kdj.k[, -c(8)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                             "RMSE.iGarchsstd", "Q.p","Q.p^2","LM.p")

print(final.result.kdj.k)

sum(final.result.kdj.k$RMSE.arima > final.result.kdj.k$RMSE.iGarchsstd)

sum(final.result.kdj.k$p.v >= 0.05)


```

```{r appendix 4.2(2), echo = TRUE, cache=FALSE, eval=TRUE}
t.test(result.sGarchged.kdj.k.50$RMSE - result.arima.kdj.k.50$RMSE)

summary(result.sGarchged.kdj.k.50$RMSE)

summary(result.arima.kdj.k.50$RMSE)

final.result.kdj.k <- cbind(result.arima.kdj.k.50, result.sGarchged.kdj.k.50)


final.result.kdj.k <- final.result.kdj.k[, -c(8)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                            "RMSE.sGarchsstd", "Q.p","Q.p^2","LM.p")

print(final.result.kdj.k)

sum(final.result.kdj.k$RMSE.arima > final.result.kdj.k$RMSE.sGarchsstd)

sum(final.result.kdj.k$p.v >= 0.05)


```

```{r appendix 4.2(3), echo = TRUE, cache=FALSE, eval=TRUE}
t.test(result.iGarchsged.kdj.k.50$RMSE - result.arima.kdj.k.50$RMSE)

summary(result.iGarchsged.kdj.k.50$RMSE)

summary(result.arima.kdj.k.50$RMSE)

final.result.kdj.k <- cbind(result.arima.kdj.k.50, result.iGarchsged.kdj.k.50)


final.result.kdj.k <- final.result.kdj.k[, -c(8)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                            "RMSE.iGarchsged", "Q.p","Q.p^2","LM.p")

print(final.result.kdj.k)

sum(final.result.kdj.k$RMSE.arima > final.result.kdj.k$RMSE.iGarchsged)

sum(final.result.kdj.k$p.v >= 0.05)


```

```{r appendix 4.2(4), echo = TRUE, cache=FALSE, eval=TRUE}
result.gjrGarchnorm.kdj.k.50

t.test(result.gjrGarchnorm.kdj.k.50$RMSE - result.arima.kdj.k.50$RMSE)

summary(result.gjrGarchnorm.kdj.k.50$RMSE)

summary(result.arima.kdj.k.50$RMSE)

final.result.kdj.k <- cbind(result.arima.kdj.k.50, result.gjrGarchnorm.kdj.k.50)


final.result.kdj.k <- final.result.kdj.k[, -c(8)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                            "RMSE.gjrGarchnorm", "Q.p","Q.p^2","LM.p")

print(final.result.kdj.k)

sum(final.result.kdj.k$RMSE.arima > final.result.kdj.k$RMSE.gjrGarchnorm)

sum(final.result.kdj.k$p.v >= 0.05)


```

There is no obvious advantage to use Garch model for predicting weekly kdj.k.


#### 5 Final comparison of pure Arima model with Garch models for 40 steps

```{r appendix 5.1, echo = TRUE, cache=TRUE, eval=TRUE}

comparison.period <- 40
training.set.endpoint <- length(weekly.kdj.k) - comparison.period - forecast.period

result.arima.kdj.k.40 <- CompareObjectZeroDiffAccuracy(arg.object = weekly.kdj.k,
                                                 arg.forecast.period = forecast.period,
                                                 arg.training.set.endpoint = training.set.endpoint,
                                                 arg.comparison.period = comparison.period,
                                                 arg.maxorder = maxorder)
```

```{r appendix 5.2, echo = TRUE, cache=TRUE, eval=TRUE}


result.gjrGarchnorm.kdj.k.40 <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k.40,
                                                  arg.var.model = "gjrGARCH",
                                                  arg.dist.model = "norm")
```

```{r appendix 5.3, echo = TRUE, cache=TRUE, eval=TRUE}


result.iGarchged.kdj.k.40 <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k.40,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "ged")
```

```{r appendix 5.4, echo = TRUE, cache=TRUE, eval=TRUE}


result.sGarchged.kdj.k.40 <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k.40,
                                                  arg.var.model = "sGARCH",
                                                  arg.dist.model = "ged")
```

```{r appendix 5.5, echo = TRUE, cache=TRUE, eval=TRUE}


result.iGarchsged.kdj.k.40 <- CompareGarchAccuracy(arg.object = weekly.kdj.k,
                                                  arg.forecast.period = forecast.period,
                                                  arg.training.set.endpoint = training.set.endpoint,
                                                  arg.comparison.period = comparison.period,
                                                  arg.result.arima = result.arima.kdj.k.40,
                                                  arg.var.model = "iGARCH",
                                                  arg.dist.model = "sged")
```

```{r appendix 5.6}

rmse.name <- c("iGarchsged",
               "iGarchged",
               "sGarchged",
               "gjrGarchnorm")

rmseBT.count <- c(sum(result.iGarchsged.kdj.k.40$RMSE > result.arima.kdj.k.40$RMSE),
                  sum(result.iGarchged.kdj.k.40$RMSE > result.arima.kdj.k.40$RMSE),
                  sum(result.sGarchged.kdj.k.40$RMSE > result.arima.kdj.k.40$RMSE),
                  sum(result.gjrGarchnorm.kdj.k.40$RMSE > result.arima.kdj.k.40$RMSE))

rmse.meanvalue <- c(mean(result.iGarchsged.kdj.k.40$RMSE),
                    mean(result.iGarchged.kdj.k.40$RMSE),
                    mean(result.sGarchged.kdj.k.40$RMSE),
                    mean(result.gjrGarchnorm.kdj.k.40$RMSE))

rmse.df <- data.frame(name = rmse.name, CountrmseBTarima = rmseBT.count, meanvalue = round(rmse.meanvalue,digits = 2))


print(rmse.df[order(rmse.df$CountrmseBTarima, rmse.df$meanvalue),])

round(mean(result.arima.kdj.k.40$RMSE), digits = 2)

```


```{r appendix 5.7, echo = TRUE, cache=FALSE, eval=TRUE}
result.gjrGarchnorm.kdj.k.40

t.test(result.gjrGarchnorm.kdj.k.40$RMSE - result.arima.kdj.k.40$RMSE)

summary(result.gjrGarchnorm.kdj.k.40$RMSE)

summary(result.arima.kdj.k.40$RMSE)

final.result.kdj.k <- cbind(result.arima.kdj.k.40, result.gjrGarchnorm.kdj.k.40)


final.result.kdj.k <- final.result.kdj.k[, -c(8)]

colnames(final.result.kdj.k) <- c("seq", "p","d","q", "dr","RMSE.arima", "p.v",
                            "RMSE.gjrGarchnorm", "Q.p","Q.p^2","LM.p")

print(final.result.kdj.k)

sum(final.result.kdj.k$RMSE.arima > final.result.kdj.k$RMSE.gjrGarchnorm)

sum(final.result.kdj.k$p.v >= 0.05)


```
