---
title: "VAR Prediction for Gold & dollar"
author: "Wu Wei"
date: "2017-8-18"
output: html_document
---



```{r library, echo = FALSE}
suppressMessages(library(forecast))
suppressMessages(library(ggplot2))
suppressMessages(library(vars))
suppressMessages(library(tseries))
suppressMessages(library(fBasics))
suppressMessages(library(FinTS))
```


## 1.Analyse for monthly gold compound return


```{r appendix 1-1, echo = TRUE}
rm(list = ls())

setwd("d://MyR//stock//")
monthly.original.data <- read.csv("goldmonthly.csv")
# View(monthly.original.data)


monthly.close.price <- monthly.original.data$Close
monthly.dollar.index <- monthly.original.data$dollarindex

## The last month has not passed completely. So it is cancelled.
monthly.close.price <- monthly.close.price[-length(monthly.close.price)]
monthly.dollar.index <- monthly.dollar.index[-length(monthly.dollar.index)]

## 19900101 ~ 20170630
# monthly.close.price <- ts(monthly.close.price, start = c(1990, 1), frequency = 12)

monthly.gold.compound.return <- diff(log(monthly.close.price)) * 100

names(monthly.gold.compound.return) <- monthly.original.data$Time[-c(1,length(monthly.original.data$Time))]


monthly.dollar.compound.return <- diff(log(monthly.dollar.index)) * 100

names(monthly.dollar.compound.return) <- monthly.original.data$Time[-c(1,length(monthly.original.data$Time))]


cor(monthly.gold.compound.return, monthly.dollar.compound.return)

cor(monthly.gold.compound.return[-length(monthly.gold.compound.return)], monthly.dollar.compound.return[-1])
```


```{r appendix 1-2, fig.height=8, fig.width=10}

tsdisplay(monthly.gold.compound.return)
```

```{r appendix 1-2(2), fig.height=8, fig.width=10}

tsdisplay(monthly.dollar.compound.return)
```

```{r appendix 1-3, eval=TRUE}

ndiffs(monthly.gold.compound.return)

```

```{r appendix 1-3(2), eval=TRUE}

ndiffs(monthly.dollar.compound.return)

```

```{r Appendix 1-4}
summary(monthly.gold.compound.return)

monthly.gold.compound.return[monthly.gold.compound.return == max(monthly.gold.compound.return)]

monthly.gold.compound.return[monthly.gold.compound.return == min(monthly.gold.compound.return)]
```




```{r appendix 1-5}
mean(monthly.gold.compound.return)
sd(monthly.gold.compound.return)
skewness(monthly.gold.compound.return)
kurtosis(monthly.gold.compound.return)
jarqueberaTest(monthly.gold.compound.return)

```


```{r appendix 1-6, cache=TRUE, eval=TRUE}
(fit.arima.gold.monthly.return <- auto.arima(monthly.gold.compound.return, seasonal = FALSE,
                                                  stepwise = FALSE, approximation = FALSE))

```

### 1.1 White Noise Test


```{r  appendix 1.1-1, cache=FALSE, eval=TRUE}


Box.test(residuals(fit.arima.gold.monthly.return), 
         lag=10, 
         fitdf=sum(fit.arima.gold.monthly.return$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.gold.monthly.return), 
         lag=20, 
         fitdf=sum(fit.arima.gold.monthly.return$arma[c(1,2)]), type = "Lj")

```

### 1.2  Relationship Between Residuals And Time

```{r appendix 1.2-1, fig.height=6, fig.width=10, cache=FALSE, eval=TRUE}

plot(residuals(fit.arima.gold.monthly.return), axes = TRUE)
abline(h = 0, col = "red")

```

### 1.3 Relationship Between Residuals And Fitted Value

```{r appendix 1.3-1, fig.height=6, fig.width=10, eval=TRUE}

plot(as.numeric(residuals(fit.arima.gold.monthly.return)) ~ as.numeric(fitted(fit.arima.gold.monthly.return)))
abline(h = 0, col = "red")


```


### 1.4 Normality of Residuals

```{r appendix 1.4-1, fig.height=6, fig.width=10, eval=TRUE}

qqnorm(residuals(fit.arima.gold.monthly.return))
qqline(residuals(fit.arima.gold.monthly.return))


```

### 1.5 ARCH Effect Test


```{r appendix 1.5-1, eval=TRUE}

Box.test((residuals(fit.arima.gold.monthly.return))^2, 
         lag=10, 
         fitdf=sum(fit.arima.gold.monthly.return$arma[c(1,2)]), type = "Lj")

Box.test((residuals(fit.arima.gold.monthly.return))^2, 
         lag=20, 
         fitdf=sum(fit.arima.gold.monthly.return$arma[c(1,2)]), type = "Lj")

ArchTest(residuals(fit.arima.gold.monthly.return))



```

## 2.Analyse for monthly dollar index compound return

```{r Appendix 2.0.1}
summary(monthly.dollar.compound.return)

monthly.dollar.compound.return[monthly.dollar.compound.return == max(monthly.dollar.compound.return)]

monthly.dollar.compound.return[monthly.dollar.compound.return == min(monthly.dollar.compound.return)]
```


```{r appendix 2.0.2}
mean(monthly.dollar.compound.return)
sd(monthly.dollar.compound.return)
skewness(monthly.dollar.compound.return)
kurtosis(monthly.dollar.compound.return)
jarqueberaTest(monthly.dollar.compound.return)

```

```{r appendix 2.0.3, cache=TRUE, eval=TRUE}
(fit.arima.dollar.monthly.return <- auto.arima(monthly.dollar.compound.return, seasonal = FALSE,
                                                  stepwise = FALSE, approximation = FALSE))


```


### 2.1 White Noise Test


```{r  appendix 2.1-1, cache=FALSE, eval=TRUE}


Box.test(residuals(fit.arima.dollar.monthly.return), 
         lag=10, 
         fitdf=sum(fit.arima.dollar.monthly.return$arma[c(1,2)]), type = "Lj")

Box.test(residuals(fit.arima.dollar.monthly.return), 
         lag=20, 
         fitdf=sum(fit.arima.dollar.monthly.return$arma[c(1,2)]), type = "Lj")

```

### 2.2  Relationship Between Residuals And Time

```{r appendix 2.2-1, fig.height=6, fig.width=10, cache=FALSE, eval=TRUE}

plot(residuals(fit.arima.dollar.monthly.return), axes = TRUE)
abline(h = 0, col = "red")

```

### 2.3 Relationship Between Residuals And Fitted Value

```{r appendix 2.3-1, fig.height=6, fig.width=10, eval=TRUE}

plot(as.numeric(residuals(fit.arima.dollar.monthly.return)) ~ as.numeric(fitted(fit.arima.dollar.monthly.return)))
abline(h = 0, col = "red")


```


### 2.4 Normality of Residuals

```{r appendix 2.4-1, fig.height=6, fig.width=10, eval=TRUE}

qqnorm(residuals(fit.arima.dollar.monthly.return))
qqline(residuals(fit.arima.dollar.monthly.return))


```

### 2.5 ARCH Effect Test


```{r appendix 2.5-1, eval=TRUE}

Box.test((residuals(fit.arima.dollar.monthly.return))^2, 
         lag=10, 
         fitdf=sum(fit.arima.dollar.monthly.return$arma[c(1,2)]), type = "Lj")

Box.test((residuals(fit.arima.dollar.monthly.return))^2, 
         lag=20, 
         fitdf=sum(fit.arima.dollar.monthly.return$arma[c(1,2)]), type = "Lj")

ArchTest(residuals(fit.arima.dollar.monthly.return))



```

## 3.VAR Analyse for Gold & dollar index compound return

```{r Appendix 3.1}
gold.dollar <- data.frame(monthly.gold.compound.return, monthly.dollar.compound.return)
str(gold.dollar)
```

```{r Appendix 3.1(2)}
gold.dollar.250 <- ts(gold.dollar[1:250,], start = c(1990, 2), frequency = 12)
VARselect(gold.dollar.250, lag.max=8, type="const")
```

```{r Appendix 3.1(3)}
gold.dollar.270 <- ts(gold.dollar[1:270,], start = c(1990, 2), frequency = 12)
VARselect(gold.dollar.270, lag.max=8, type="const")
```

```{r Appendix 3.1(4)}
gold.dollar.290 <- ts(gold.dollar[1:290,], start = c(1990, 2), frequency = 12)
VARselect(gold.dollar.290, lag.max=8, type="const")
```

```{r Appendix 3.1(5)}
gold.dollar.310 <- ts(gold.dollar[1:310,], start = c(1990, 2), frequency = 12)
VARselect(gold.dollar.310, lag.max=8, type="const")
```

```{r Appendix 3.1(6)}
gold.dollar <- ts(gold.dollar, start = c(1990, 2), frequency = 12)
VARselect(gold.dollar, lag.max=8, type="const")
```

```{r Appendix 3.2}
var <- VAR(gold.dollar, p=1, type="const")
serial.test(var, lags.pt=10, type="PT.asymptotic")
```

```{r Appendix 3.3}
summary(var)
```

```{r Appendix 3.4}

fcst <- forecast(var,h = 2)

fcst
```

```{r appendix 3.5, fig.height=8, fig.width=10, eval=TRUE}
plot(fcst, xlab="Year")

```
